### 2020-09-05 Triangulation_2020_7_9.tex
first commit

\documentclass{beamer}

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subfigure,pgf,tikz}
\usetikzlibrary{arrows}
\usepackage[misc]{ifsym}
\usepackage{mathrsfs}
\usepackage{epstopdf}

\usepackage{graphicx,xcolor,subfigure}

\usepackage{xeCJK}

\setCJKmainfont{微軟正黑體}

\XeTeXlinebreaklocale "zh"

\XeTeXlinebreakskip = 0pt plus 1pt

\usetheme{Boadilla}

\setbeamertemplate{footlines}[page number]{}
\setbeamertemplate{navigation symbols}

\title[]{}

\author[]{ }

\date[]{}

\setbeamertemplate{theorems}[numbered]

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}

\theoremstyle{definition}
\newtheorem{ex}[thm]{Exercise}
\newtheorem{defn}[thm]{Definition}
\newtheorem{prob}[thm]{Problem}
\newtheorem{exam}[thm]{Example}
\newtheorem{rem}[thm]{Remark}
\newtheorem{ques}[thm]{Question}
\newtheorem{conj}[thm]{Conjecture}

\begin{document}

\begin{frame}{\bf Definitions}

\begin{enumerate}
\item A \textcolor{red}{\bf triangulated graph} is a planar graph such that any edge is in a face and any face is a triangle. 
\item A \textcolor{red}{\bf chordal graph} is a graph such that every cycle of length at least $4$ contains a \textcolor{red}{\bf chord}, i.e., an edge connecting two nonadjacent vertices of the cycle. 
\item Is a triangulated graph a chordal graph? 
\item A \textcolor{red}{\bf weakly  pancyclic graph} is a graph which contains cycles of every length between the girth and the circumference. 
\item A graph is \textcolor{red}{\bf $t$-tough}  if for every integer $k>1$, the graph cannot be split into $k$ components by removal of fewer than $tk$ vertices 
\item Hence a $t$-tough graph with $t>0$ is connected.  
\end{enumerate}

\end{frame}

\begin{frame}{\bf Conjectures}

\begin{enumerate}
\item A triangulated graph is weakly  pancyclic.
\item A chordal graph is weakly  pancyclic.
\item There is a  $9$-tough triangulated non-Hamiltonian graph. 
\item A $9.1$-tough triangulated graph is Hamiltonian. 
\end{enumerate}
\bigskip

[1] Adam Kabela, Tom\'{a}\v{s} Kaiser, $10$-tough chordal graphs are Hamiltonian, Journal of Combinatorial Theory, Series B, Volume 122, January 2017, Pages 417-427.
\end{frame}

\begin{frame}{\bf Locally property $P$}

Let $P$ be a property on graphs. 
A graph $G$ has \textcolor{red}{\bf local $P$} if $G_1(v)$ has property $P$ for every vertex $v$ in $G$. 
\bigskip

Hence a triangulated graph is locally connected.
\end{frame}

\begin{frame}{\bf Lemma}
If $G$ is $1$-tough and locally $1$-tough then $G-u$ is $1$-tough for every vertex $u$ in $G$.

\begin{proof} 
Assume that $G-u$ is split into $k$ components by removal fewer than $k$ vertices, and $t$ of these components intersect $G_1(u)$. 
Then among the $k$ removal vertices there are at least $t$ from $G_1(u)$ and the remaining at most $k-t$ from $G-u-G_1(u)$ since $G_1(u)$ is $1$-tough.
Then $G$ is split into $1+(k-t)$ components by  by removal fewer than $1+k-t$ vertices in $G-G_1(u)$, a contradiction to the $1$-tough assumption of $G$. 
\end{proof}
\end{frame}

\begin{frame}{\bf More conjectures}
\begin{enumerate}
\item If $G$ is $1$-tough and locally $1$-tough then $G-u$ is locally $1$-tough for every vertex $u$ in $G$. 
\item  A $1$-tough and locally $1$-tough graph is weakly pancyclic. 
\item  A $1$-tough and locally $1$-tough graph is Hamiltonian. 
\end{enumerate}

\end{frame}
\end{document}

### 2020-09-05 spectral radius of matrix new method/paper/article_struc1112.tex
first commit

\documentclass[12pt]{article}
%\usetheme{Warsaw}
\usepackage{times}  % fonts are up to you
\usepackage{amssymb, amsmath, mathrsfs,amsthm}
\usepackage{multicol}
\usepackage{bm}
\usepackage{ulem}

\usepackage{fontspec}
\usepackage{xeCJK}
%\setCJKmainfont{微軟正黑體}
\setCJKmainfont{simsun.ttf}
\setCJKsansfont{simhei.ttf}
\setCJKmonofont{simfang.ttf}
\XeTeXlinebreaklocale "zh"
\XeTeXlinebreakskip = 0pt plus 1pt

\begin{document}

% THEOREMS ---------------------------------------------------------------
\theoremstyle{plain}
% block中的字會變成數學體, 斜體字
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{remark}[thm]{Remark}
\newtheorem{pf}[thm]{Proof}

\newtheorem{eg}[thm]{Example}
\newtheorem{conj}[thm]{Conjecture}

\theoremstyle{definition}
% block中的字是正常字體
\newtheorem{ex}[thm]{Exercise}
\newtheorem{defn}[thm]{Definition}
\newtheorem{prob}[thm]{Problem}
\newtheorem{exam}[thm]{Example}
\newtheorem{rem}[thm]{Remark}

\newtheorem{algo}[thm]{Algorithm}

\title{TBA}
\author{Ke-Han Chen\\} % 作者
%\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
\date{October 18th, 2018}
\date{\today} % 日期

\maketitle
\begin{abstract}
    This is my abstract.
\end{abstract}

\section{Preliminaries}

\begin{defn}
Spectral radius of a matrix $C$ is the largest absolute value of real eigenvalue of $C$. And here we are interested in spectral radius of the adjacency matrix for some simple graph.
\end{defn}
\begin{defn}
    Eigenvalue of a matrix $C$ corresponds to an eigenvector $u$, where $u$ and its eigenvalue $\lambda $  satisfies $Cu = \lambda u$. 
\end{defn}
    We introduce a notation of sub-matrix, which is taken from some columns and some rows of a matrix. 
    \begin{defn}We use $C[\alpha|\beta]$ to denote the sub-matrix of rows $\alpha$ of $C$ and columns $\beta$ of $C$ and $C(\alpha|\beta)$ is the sub-matrix of rows $[n]$ - $\alpha$ of $C$ and columns $[n] - \beta$ of $C$.
    The bracket [] and parentheses () can be used together is the notation of sub-matrix, such as $C[k|e)$ or $C(k|e]$. 
\end{defn}

\thm
        If $C$ is nonnegative square matrix, then the following holds. \\
        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.

The following theorem is from [].

\begin{thm}
 Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]    $PCQ\leq PC'Q$;
\item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
\item[(iii)] there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector $v^TP$; and
\item[(iv)] $v^TPQu>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
    Moreover, $\lambda=\lambda'$ 
if and only if
    \begin{equation*}
        \label{e3}
(PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
\end{equation*}
\end{thm}

\begin{pf}
            Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
        \begin{equation}
            \label{e1}
            PCQu\leq PC'Qu=\lambda'PQu.
        \end{equation}
        Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
        \begin{equation}
            \label{e2}
            \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
        \end{equation}
        Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.

        Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.  Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
            $\lambda=\lambda'$ by (\ref{e2}). \qed

 \end{pf}

 Throughout fix $k\in [n-1]$. Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the  position $k,n$ of $E_{kn}$. We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
1 &  & & &  & 0 \\
 & 1 &  &      &  &  \\
 &  & \ddots & &  & 1 \\
 &  &        & &  &  \\
  &  & & & 1 &  \\
0 &  & & &  & 1 \\
\end{pmatrix}.$$
\begin{defn}\label{v_rooted}
 ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

The following Lemma is immediate from the above definition.
\bigskip

\begin{lem}
If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}
\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
\qed
\end{lem}

\section{Our first result}

\begin{thm} \label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[-|n)\leq C'[-|n)$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
\item[(a)] $c_{ik}+c_{in}=c'_{ik}+c'_{in}$\qquad for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
\item[(b)]
$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
\end{enumerate} \qed
\end{thm}

{\bf $k$-rooted matrix}

\begin{defn}[(k,n)-sum]
For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
\end{defn}

\begin{defn}[k-rooted matrix]\label{m_rooted}
A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-sum vector are all $k$-rooted except the last column of $C'$.
\end{defn}

\begin{thm}
Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
    \begin{enumerate}
        \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
        \item[(ii)]$C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$ as an eigenvalue. $u$ is a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$.
        \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
    \end{enumerate}

\begin{pf}
\subsection{}
(i) is immediate from Definition~\ref{m_rooted} and the observation that 
$$Q^{-1}=I-E_{kn}=\begin{pmatrix}
1 &  & & &  & 0 \\
 & 1 &  &      &  &  \\
 &  & \ddots & &  & -1 \\
 &  &        & &  &  \\
  &  & & & 1 &  \\
0 &  & & &  & 1 \\
\end{pmatrix},$$
and $Q^{-1}C'Q$ is 
$$\begin{pmatrix}
c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
\vdots \\
c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
\vdots              & \vdots & \ddots              & \vdots & \vdots \\
c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
\end{pmatrix}.
$$

\subsection{(ii)}

By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted. 
Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have 
$C'Qu=\rho(C')Qu$.

\subsection{(iii)}

Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.

\end{pf}
\end{thm}

\begin{lem}\label{l_diag}
If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
\end{lem}

\section{Conclusion}

\begin{thm}
Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
such that $c'_{ij}\geq c_{ij}$, and then choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$ and $c'_{kj}\geq c'_{nj}>0$, and 
let $c'_{in}:=r'_i-c'_{ik}$ with $r'_k \geq r'_n$. Whereas $c'_{kk}\geq c'_{nk}$ is not necessary. Then the $n\times n$ matrix $C'=(c'_{ij})$ has a positive $k$-rooted eigenvector for $\rho(C')$ and $\rho(C)\leq \rho(C')$. 
\end{thm}

{\bf Proof}

The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by \ref{l_diag}, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$. So C'+d*I and C+d*I meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed

{Example}
For the following $4\times 4$ matrix
$$C=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 0 & 1\\
1 & 1 & 0 & 1\\
1 & 1 & 1 & 0
\end{pmatrix},$$
we choose
$$C'=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 1 &  0\\
1 & 1 & 0 & 1\\
1 & 1 & 1 & 0
\end{pmatrix}.$$
Then
$\rho(C)\leq \rho(C')$ by previous theorem.

{\bf Counterexample}
For the following two $4\times 4$ matrices
$$C=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 0 & 1\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 0
\end{pmatrix},\quad C'=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 1 &  0\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 0
\end{pmatrix},$$ 
we have $CQ\leq C'Q$, but 
$\rho(C)=2.234\not\leq 2.148= \rho(C')$. 
This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.

\end{document}

### 2020-09-05 spectral radius of matrix new method/paper/conclusion/root.tex
first commit

--- 2020-09-05 spectral radius of matrix new method/paper/article_struc1112.tex
@@
-\documentclass[12pt]{article}
+\documentclass{article}
+
 %\usetheme{Warsaw}
@@
 \newtheorem{algo}[thm]{Algorithm}
-
-\title{TBA}
-\author{Ke-Han Chen\\} % 作者
-%\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
-\date{October 18th, 2018}
-\date{\today} % 日期
-
-\maketitle
-\begin{abstract}
-    This is my abstract.
-\end{abstract}
-
-\section{Preliminaries}
-
-\begin{defn}
-Spectral radius of a matrix $C$ is the largest absolute value of real eigenvalue of $C$. And here we are interested in spectral radius of the adjacency matrix for some simple graph.
-\end{defn}
-\begin{defn}
-    Eigenvalue of a matrix $C$ corresponds to an eigenvector $u$, where $u$ and its eigenvalue $\lambda $  satisfies $Cu = \lambda u$. 
-\end{defn}
-    We introduce a notation of sub-matrix, which is taken from some columns and some rows of a matrix. 
-    \begin{defn}We use $C[\alpha|\beta]$ to denote the sub-matrix of rows $\alpha$ of $C$ and columns $\beta$ of $C$ and $C(\alpha|\beta)$ is the sub-matrix of rows $[n]$ - $\alpha$ of $C$ and columns $[n] - \beta$ of $C$.
-    The bracket [] and parentheses () can be used together is the notation of sub-matrix, such as $C[k|e)$ or $C(k|e]$. 
-\end{defn}
-
-\thm
-        If $C$ is nonnegative square matrix, then the following holds. \\
-        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
-
-The following theorem is from [].
-
-\begin{thm}
- Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
-Assume that
-\begin{enumerate}
-\item[(i)]    $PCQ\leq PC'Q$;
-\item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
-\item[(iii)] there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
-such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector $v^TP$; and
-\item[(iv)] $v^TPQu>0.$
-\end{enumerate}
- Then $\lambda\leq \lambda'$.
-    Moreover, $\lambda=\lambda'$ 
-if and only if
-    \begin{equation*}
-        \label{e3}
-(PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
-\end{equation*}
-\end{thm}
-
-\begin{pf}
-            Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
-        \begin{equation}
-            \label{e1}
-            PCQu\leq PC'Qu=\lambda'PQu.
-        \end{equation}
-        Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
-        \begin{equation}
-            \label{e2}
-            \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
-        \end{equation}
-        Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
-
-        Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.
-Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
-         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
-            $\lambda=\lambda'$ by (\ref{e2}). \qed
-
- \end{pf}
-
- Throughout fix $k\in [n-1]$.
-Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the  position $k,n$ of $E_{kn}$.
-We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
-1 &  & & &  & 0 \\
- & 1 &  &      &  &  \\
- &  & \ddots & &  & 1 \\
- &  &        & &  &  \\
-  &  & & & 1 &  \\
-0 &  & & &  & 1 \\
-\end{pmatrix}.$$
-\begin{defn}\label{v_rooted}
- ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
-\end{defn}
-\bigskip
-
-The following Lemma is immediate from the above definition.
-\bigskip
-
-\begin{lem}
-If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
-\begin{enumerate}
-\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
-\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
-\end{enumerate}
-\qed
-\end{lem}
-
-\section{Our first result}
-
-\begin{thm} \label{thm_main}
-    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
-Assume that
-\begin{enumerate}
-\item[(i)]   $C[-|n)\leq C'[-|n)$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-\item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
-such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
-\item[(iv)] $v^Tv'>0.$
-\end{enumerate}
- Then $\lambda\leq \lambda'$.
-Moreover, $\lambda=\lambda'$
-if and only if
-\begin{enumerate}
-\item[(a)] $c_{ik}+c_{in}=c'_{ik}+c'_{in}$\qquad for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
-\item[(b)]
-$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
-\end{enumerate} \qed
-\end{thm}
-
-{\bf $k$-rooted matrix}
-
-\begin{defn}[(k,n)-sum]
-For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
-\end{defn}
-
-\begin{defn}[k-rooted matrix]\label{m_rooted}
-A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-sum vector are all $k$-rooted except the last column of $C'$.
-\end{defn}
-
-\begin{thm}
-Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-    \begin{enumerate}
-        \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-        \item[(ii)]$C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$ as an eigenvalue. $u$ is a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$.
-        \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
-    \end{enumerate}
-
-\begin{pf}
-\subsection{}
-(i) is immediate from Definition~\ref{m_rooted} and the observation that 
-$$Q^{-1}=I-E_{kn}=\begin{pmatrix}
-1 &  & & &  & 0 \\
- & 1 &  &      &  &  \\
- &  & \ddots & &  & -1 \\
- &  &        & &  &  \\
-  &  & & & 1 &  \\
-0 &  & & &  & 1 \\
-\end{pmatrix},$$
-and $Q^{-1}C'Q$ is 
-$$\begin{pmatrix}
-c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
-\vdots \\
-c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
-c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
-c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
-\vdots              & \vdots & \ddots              & \vdots & \vdots \\
-c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
-\end{pmatrix}.
-$$
-
-\subsection{(ii)}
-
-By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted. 
-Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have 
-$C'Qu=\rho(C')Qu$.
-
-\subsection{(iii)}
-
-Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.
-
-\end{pf}
-\end{thm}
-
-\begin{lem}\label{l_diag}
-If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
-the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
-\end{lem}
 

### 2020-09-05 spectral radius of matrix new method/ref/els_matrix_realization_Cheng.tex
first commit

\documentclass[final,3p, times, 12pt]{elsarticle}
\usepackage[centertags]{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[misc]{ifsym}
\usepackage{mathrsfs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}
\usepackage{lineno}
%\usepackage[authoryear]{natbib}

% THEOREMS ---------------------------------------------------------------
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{pron}[thm]{Proposition}
\newtheorem{remark}[thm]{Remark}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{prob}[thm]{Problem}
%
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{exam}[thm]{Example}
\newtheorem{rem}[thm]{Remark}
%
\theoremstyle{remark}
\numberwithin{equation}{section}
\renewcommand{\theequation}{\thesection.\arabic{equation}}

\newcommand{\beast}{\begin{eqnarray*}}
\newcommand{\eeast}{\end{eqnarray*}}
\begin{document}

\begin{frontmatter}

\title{A matrix realization of spectral bounds \\ of the spectral radius of a nonnegative matrix}

\author[NCTU]{Yen-Jen Cheng\corref{cor}}\ead{yjc7755.am01g@nctu.edu.tw}
\author[NCTU]{Chih-wen Weng}\ead{weng@math.nctu.edu.tw}

\cortext[cor]{Corresponding author}
%\date{\currenttime \today}

\address[NCTU]{Department of Applied Mathematics, National Chiao Tung University, 1001 Ta Hsueh Road, Hsinchu, Taiwan.}

\begin{abstract}
We  realize many sharp spectral bounds of the spectral radius of a nonnegative square matrix $C$ by using the largest real eigenvalues of  suitable matrices of smaller sizes related to $C$ that are very easy to find.
As applications, we give a sharp upper bound of the spectral radius of $C$ expressed by the sum of entries, the largest off-diagonal entry $f$ and the largest diagonal entry $d$ in $C$.
We also give a new class of sharp lower bounds of the spectral radius of $C$ expressed
 by the above $d$ and $f$, the least row-sum $r_n$ and the $t$-th largest row-sum $r_t$ in $C$ satisfying
 $0<r_n-(n-t-1)f-d\leq r_t-(n-t)f$, where $n$ is the size of $C$.
\end{abstract}

\begin{keyword}
nonnegative matrices, spectral radius, spectral bounds

\MSC[2010]05C50 \sep 15A42
\end{keyword}
\bigskip

\end{frontmatter}

%%%%%%%%%%%%%%%%   1.Introduction  %%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{s1}

For real matrices $C=(c_{ij})$, $C'=(c'_{ij})$ of the same size, $C'$ {\it majorizes} $C$, in the notation  $C\leq C'$, if $c_{ij}\leq c'_{ij}$ for all $i$,$j$. When $C$ is a square matrix, the spectral radius $\rho(C)$ of $C$ is defined by
$$\rho(C):=\max\{~|\lambda|~\ |~\lambda\hbox{ is an eigenvalue of $C$}\},$$
where $|\lambda|$ is the magnitude of complex number $\lambda.$
This paper is motivated by the following theorem of   Xing Duan and Bo Zhou in 2013 \cite[Theorem 2.1]{dz}.

\begin{thm}\label{dz2013}
Let $C=(c_{ij})$ be a nonnegative $n\times n$ matrix with  row-sums $r_1\geq r_2\geq \cdots \geq r_n$,  $f:=\max_{1\leq i\not=j\leq n} c_{ij}$ and $d:=\max_{1\leq i\leq n} c_{ii}$. Then
\begin{equation}\label{mo}\rho(C) \leq \frac{r_{\ell}+d-f+\sqrt{(r_{\ell}-d+f)^{2}+4f\sum_{i=1}^{\ell-1}(r_i-r_\ell)}}{2}\end{equation}
for $1 \leq \ell \leq n.$
Moreover, if $C$ is irreducible, then the equality holds in (\ref{mo}) if and only if $r_1=r_n$ or for  $1\leq t\leq \ell$ with $r_{t-1}\not=r_t=r_\ell$, we have $r_t=r_n$ and
$$c_{ij}=\left\{
           \begin{array}{ll}
             d, & \hbox{if $i=j\leq t-1$;} \\
             f, & \hbox{if $i\not=j$ and $1\leq i\leq n$, $1\leq j\leq t-1.$}
           \end{array}
         \right.$$
\end{thm}

Theorem~\ref{dz2013} generalizes the results in \cite{bh:85, cls:13, h:98, hsf:01, lw13, s87, sw:04} and
relates to the  results in \cite{hw:13, Liu, s87}, while the upper bound of $\rho(C)$ expressed in (\ref{mo}) is somewhat complicate and deserves an intuitive realization.

The values on the right hand side of (\ref{mo}) is realized as the largest real eigenvalue $\rho_r(C')$ of the $n\times n$ matrix
\begin{equation}\label{ne1.0}C'=\left(\begin{array}{cccc|ccccc}
d     &f      &\cdots &f      &f      & f        &\cdots &f       &r_1-d-(n-2)f\\
f     &d      &       &f      &f      & f        &\cdots &f       &r_2-d-(n-2)f\\
\vdots&       &\ddots &\vdots &\vdots &\vdots    &       &\vdots  &\vdots      \\
f     &f      &\cdots &d      & f     & f        &\cdots &f       &r_{\ell-1}-d-(n-2)f\\ \hline
f     &f      &\cdots &f      & d     & f        &\cdots &f       &r_{\ell}-d-(n-2)f\\
f     &f      &\cdots &f      & f     & d        &       &f       &r_{\ell}-d-(n-2)f\\
\vdots&\vdots &       &\vdots &\vdots &          &\ddots &\vdots  &\vdots\\
f     &f      &\cdots &f      & f     & f        &       &d       &r_{\ell}-d-(n-2)f\\
f     &f      &\cdots &f      & f     & f        &\cdots &f       &r_{\ell}-(n-1)f\\
\end{array}\right)\end{equation}
which has the following three properties:
\begin{enumerate}
\item[(i)]  The row-sum vector $(r_1, r_2, \ldots, r_\ell, \ldots,  r_\ell)^T$ of $C'$ majorizes the row-sum vector  $(r_1,$ $r_2,$ $\ldots,$ $r_n)^T$ of $C$,
\item[(ii)] $C'$ majorizes $C$ except the last column, and
\item[(iii)] $C'$ has a positive eigenvector $(v'_1, v'_2, \ldots, v'_n)^T$ for $\rho_r(C')$ with $v'_i\geq v'_n$ for $1\leq i\leq n.$
\end{enumerate}
Property (iii) will be checked by Lemma~\ref{l4.4}. Since the above matrix $C'$ is not necessary to be nonnegative, the spectra radius $\rho(C')$ of $C'$ is replaced by the largest real eigenvalue $\rho_r(C')$ in the property (iii).
 Our main result in Theorem~\ref{t3.1} is in a more general form that will imply for any matrices $C'$ that satisfy the properties (i)-(iii) above, we have $\rho(C)\leq \rho_r(C').$
Moreover, when the matrix $C'$ and so the value $\rho_r(C')$ are fixed, the matrices $C$ with $\rho(C)=\rho_r(C')$ are completely determined.
We apply Theorem~\ref{t3.1} to find a sharp upper bound of $\rho(C)$ expressed by the sum of entries in $C$, the largest off-diagonal entry $f$ and the largest diagonal entry $d$ in Theorem~\ref{tt6.1}.

 Note that $\rho_r(C')=\rho_r(C'')$ for the largest real eigenvalues of $C'$ and $C''$ respectively, where  $C'$ is as in (\ref{ne1.0}) and
\begin{equation}\label{ne1.2}C''=\left(\begin{array}{cccc|c}
d     &f&\cdots&f     &r_1-d-(\ell-2)f\\
f     &d&      &f     &r_2-d-(\ell-2)f\\
\vdots& &\ddots&\vdots &\vdots \\
f     &f&\cdots&d        &r_{\ell-1}-d-(\ell-2)f\\ \hline
f     &f&\cdots&f     &r_{\ell}-(\ell-1)f
\end{array}\right)
\end{equation}
 is the equitable quotient matrix of $C'$ with respect to the partition $\{\{1\}$, $\{2\}$, $\ldots$, $\{\ell-1\}$, $\{\ell, \ell+1, \ldots, n\}\}$ of $\{1, 2, \ldots, n\}$.
 Moreover  $\rho_r(C'')=\rho_r(C''')$, where
\begin{equation}\label{n31.3}C'''=\begin{pmatrix}(\ell-2)f+d & f\\
\sum_{i=1}^{\ell-1} r_i-(\ell-1)((\ell-2)f+d)    & r_\ell-(\ell-1)f
\end{pmatrix},\end{equation}
is the equitable quotient of the transpose $C''^T$ of $C''$ with respect to the partition $\{\{1, 2, \ldots, \ell-1\}, \{\ell\}\}$ of $\{1, 2, \ldots, \ell\}$.
Motivated by these observations, Theorem~\ref{main3} will provide an upper bound $\rho_r(C'')$ of $\rho(C)$, where $C''$ is a matrix of size smaller than that of $C$ obtained by applying equitable quotient to suitable matrix $C'$  that satisfies properties (i)-(iii) described above.

Every our theorem of upper bounds of $\rho(C)$ has a dual version that deals with lower bounds. We provide a new class of sharp lower bounds of $\rho(C)$  in Theorem~\ref{main5}. Applying  Theorem~\ref{main5} to a binary matrix $C$, we improve the well known inequality  $\rho(C)\geq r_n$ as stated in Corollary~\ref{cor10.2}.
We believe that many new spectral bounds of the spectral radius of a nonnegative matrix will be easily obtained by our matrix realization in this paper.

In addition to the above results, Lemma~\ref{nt3.1}, Lemma~\ref{nt3.1'} and Lemma~\ref{lem2.2'} are of independent interest in matrix theory.

\section{Preliminaries}\label{s1.5}

Our study is based on the famous Perron-Frobenius Theorem, hence we shall review the necessary parts of the theorem in this section.

\begin{thm}[{\cite[Theorem 2.2.1]{Brou}, \cite[Corollary 8.1.29, Theorem 8.3.2]{Horn}}]\label{PF}
If $C$ is a nonnegative square matrix, then the following (i)-(iii) hold.
\begin{enumerate}
\item[(i)] The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
\item[(ii)] If there exists a column vector $v> 0$ and a nonnegative number $\lambda$ such that $Cv\leq \lambda v$, then $\rho(C)\leq\lambda$.
\item[(iii)] If there exists a column vector $v\geq 0$, $v\not=0$  and a nonnegative number $\lambda$ such that  $Cv\geq \lambda v$, then  $\rho(C)\geq\lambda$.
\end{enumerate}
Moreover, if in addition  $C$ is irreducible, then
 the eigenvalue $\rho(C)$ in (i) has multiplicity $1$ and its corresponding left eigenvector and right eigenvector can be chosen to be positive, and any nonnegative left or right eigenvector of $C$ is only corresponding to the eigenvalue $\rho(C)$.
 \qed
\end{thm}

Without further mention, an eigenvector is always a right eigenvector.
The following two lemmas are  well-known consequences of Theorem~\ref{PF}. We shall provide their proofs since they motivate our  proofs of results.

\begin{lem}[{\cite[Theorem 2.2.1]{Brou}}]\label{lem1.2}
If $0\leq C\leq C'$ are square matrices, then $\rho(C)\leq\rho(C')$. Moreover, if $C'$ is irreducible,
then $\rho(C')=\rho(C)$  if and only if $C'=C$.
\end{lem}
\begin{proof}
 Let $v$ be  a nonnegative eigenvector of $C$ for $\rho(C)$. From the assumption,  $C'v\geq Cv=\rho(C)v$.
 By Theorem~\ref{PF}(iii) with $(C, \lambda)=(C', \rho(C))$, we have  $\rho(C')\geq \rho(C).$
   Clearly $C'=C$ implies $\rho(C')=\rho(C)$.
 If $\rho(C')=\rho(C)$ and $C'$ is irreducible, then
 $\rho(C)v'^Tv=\rho(C') v'^Tv=v'^TC'v\geq v'^TCv= \rho(C)v'^Tv,$
 where $v'^T$ is a positive left eigenvector of $C'$ for $\rho(C').$
 Hence the above inequality is the equality $v'^TC'v=v'^TCv$.  As $v'^T$ positive,
  $C'v=Cv=\rho(C)v=\rho(C')v,$ so $v$ is a positive eigenvector of $C'$ for $\rho(C')$ and $C'=C.$
 \end{proof}

The matrix $C'$ in Lemma~\ref{lem1.2} is a {\it matrix realization} of the upper bound $\rho(C')$ of $\rho(C)$. We shall provide other matrix realizations as stated in the title.

\begin{lem}[{\cite[Theorem 8.1.22]{Horn}}]\label{lem1.1}
If an $n\times n$ matrix $C=(c_{ij})$ is nonnegative with row-sum vector $(r_1,r_2,\ldots,r_n)^T$, where $r_i=\sum_{1\leq j\leq n}c_{ij}$ and $r_1\geq r_i\geq r_n$ for $1\leq i\leq n$,
then
$$r_n \leq \rho(C) \leq r_1.$$
Moreover, if $C$ is irreducible, then $\rho(C)=r_1$ (resp.  $\rho(C)=r_n$) if and only if $C$ has constant row-sum.
\end{lem}

We provide a proof of the following generalized version of Lemma~\ref{lem1.1}, which is due to  M. N. Ellingham and Xiaoya Zha \cite{ez}.

\begin{lem}[\cite{ez}]\label{lem1.1'}
If an $n\times n$ matrix $C$ with row-sum vector $(r_1,r_2,\ldots,r_n)^T$, where $r_1\geq r_i\geq r_n$ for $1\leq i\leq n$, has a nonnegative left eigenvector $v^T=(v_1,v_2,\ldots,v_n)$ for $\theta$, then
$$r_n \leq \theta \leq r_1.$$
Moreover, $\theta=r_1$ (resp. $\theta=r_n$) if and only if $r_i=r_1$ (resp. $r_i=r_n$) for the indices $i$ with $v_i\ne 0$.
In particular, if $v^T$ is positive, $\theta=r_1$ (resp. $\theta=r_n$) if and only if $C$ has constant row-sum.
\end{lem}
\begin{proof}
Without loss of generality, let $\sum_{i=1}^{n}v_i=1$ and $u$ be the all-one column vector. Then
$$\theta=\theta v^Tu=v^TCu=\sum_{i=1}^nv_ir_i.$$
So $\theta$ is a convex combination of those $r_i$ with indices $i$ satisfying $1\leq i\leq n$ and $v_i> 0$, and the lemma follows.
\end{proof}

In the sequels, we shall call two statements  that resemble each other by switching $\leq$ and $\geq$ and corresponding variables, like
$\theta\geq r_n$ and $\theta\leq r_1$, as {\it dual statements}, and  their proofs are called {\it dual proofs} if one proof is obtained from the other  by simply switching one of $\leq$ and $\geq$ to the other.

\section{A generalization of Lemma~~\ref{lem1.2}}\label{s2.2}

We generalize Lemma~\ref{lem1.2} in the sense of Lemma~\ref{lem1.1'} that the matrices considered are not necessary to be nonnegative.
\begin{lem}\label{nt3.1}
 Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]    $PCQ\leq PC'Q$;
\item[(ii)]  $C'$ has an eigenvector $Qu$ for $\lambda'$ for some nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and $\lambda'\in \mathbb{R}$;
\item[(iii)] $C$ has a left eigenvector $v^TP$ for $\lambda$ for some nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and  $\lambda\in \mathbb{R}$; and
\item[(iv)] $v^TPQu>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{equation}\label{ne4.1}
(PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
\end{equation}
\end{lem}

\begin{proof}
Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
\begin{equation}\label{e4.3}
PCQu\leq PC'Qu=\lambda'PQu.
\end{equation}
Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e4.3}), we have
\begin{equation}\label{e4.4}\lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.\end{equation}
Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.

 Assume that $\lambda=\lambda'$, so the inequality in (\ref{e4.4}) is an equality.  Especially $(PCQu)_i=(PC'Qu)_i$
for any $i$ with $v_i\not=0.$ Hence $(PCQ)_{ij}=(PC'Q)_{ij}$ for  any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$

Conversely, (\ref{ne4.1}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
$\lambda=\lambda'$ by (\ref{e4.4}).
\end{proof}

If $C$ is nonnegative and $P=Q=I$, where $I$ is  the $n\times n$ identity matrix, then Lemma~\ref{nt3.1} becomes Lemma~\ref{lem1.2}
with an additional assumption $v^Tu>0$ which immediately holds if $C$ or $C'$ is irreducible by Theorem~\ref{PF}.
The following is a dual version of lemma~\ref{nt3.1} and its proof is by dual proof.

\begin{lem}\label{nt3.1'}
 Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]    $PCQ\geq PC'Q$;
\item[(ii)]  $C'$ has an eigenvector $Qu$ for $\lambda'$ for some nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and $\lambda'\in \mathbb{R}$;
\item[(iii)] $C$ has a left eigenvector $v^TP$ for $\lambda$ for some nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and  $\lambda\in \mathbb{R}$; and
\item[(iv)] $v^TPQu>0.$
\end{enumerate}
 Then $\lambda\geq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{equation}\label{ne4.1'}
(PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n~ \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
\end{equation}\qed
\end{lem}

\section{The special case $P=I$ and a particular $Q$}\label{s2.5}

We shall applying Lemma~\ref{nt3.1} and Lemma~\ref{nt3.1'} by using $P=I$ and
\begin{equation}\label{defnq}
Q=\begin{pmatrix}
1 & 0 & \cdots & 0 & 1 \\
0 & 1 & \cdots & 0 & 1 \\
\vdots & \vdots & \ddots & \vdots & \vdots \\
0 & 0 & \cdots & 1 & 1 \\
0 & 0 & \cdots & 0 & 1 \\
\end{pmatrix}.
\end{equation}
Hence for $n\times n$ matrix $C'=(c'_{ij}),$ the matrix $PC'Q$ in Lemma~\ref{nt3.1}(i) is
\begin{equation}\label{C'Q}C'Q=\begin{pmatrix}
c'_{11} & c'_{12} & \cdots & c'_{1\ n-1} & r'_1\\
c'_{21} & c'_{22} & \cdots & c'_{2\ n-1} & r'_2\\
\vdots & \vdots & \ddots & \vdots & \vdots \\
c'_{n-1\ 1} & c'_{n-1\ 2} & \cdots & c'_{n-1\ n-1} & r'_{n-1}\\
c'_{n1} & c'_{n2} & \cdots & c'_{n\ n-1} & r'_n\\
\end{pmatrix},
\end{equation}
where $(r'_1, r'_2, \ldots, r'_n)^T$ is the row-sum column vector of $C'.$

\begin{defn}\label{d3.1}
 A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it rooted}  if $v'_j\geq v'_n\geq 0$  for $1\leq j\leq n-1$.
\end{defn}

The following Lemma is immediate from the above definition.
\begin{lem}\label{l3.15}
If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1+u_n, u_2+u_n, \ldots, u_{n-1}+u_n, u_n)^T$, then
\begin{enumerate}
\item[(i)] $v'$ is rooted  if and only if  $u$ is nonnegative;
\item[(ii)] $u_j>0$ if and only if $v'_j>v'_n$ for $1\leq j\leq n-1$.
\end{enumerate}\qed
\end{lem}

The following matrix notation will be adopted in the paper. For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column indices respectively, we use $C[\alpha|\beta]$ to denote the submatrix
of $C$ with size $|\alpha|\times |\beta|$ that has entries $c_{ij}$ for $i\in \alpha$ and $j\in\beta$,
$C[\alpha|\beta):=C[\alpha|\overline{\beta}],$ where $\overline{\beta}$ is the complement of $\beta$ in the set of column indices, and
similarly, for the definitions of $C(\alpha|\beta]$ and $C(\alpha|\beta).$
 For $\ell\in \mathbb{N},$ $[\ell]:=\{1, 2, \ldots, \ell\},$ symbol $-$ is the complete set of indices, and we use  $i$ to denote the singleton subset $\{i\}$ to reduce the double use of parentheses. For example of the $n\times n$ matrix $C$,
 $C[-|n)=C[[n]|[n-1]]$ is the $n\times (n-1)$ submatrix of $C$ obtained by deleting the last column of $C$.
The following theorem is immediate from Lemma~\ref{nt3.1} by applying $P=I$, the $Q$ in (\ref{defnq}), $v'=Qu$ and referring to (\ref{C'Q}) and Lemma~\ref{l3.15}.

\begin{thm}\label{t3.1}
 Let $C=(c_{ij})$, $C'=(c_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[-|n)\leq C'[-|n)$ and the row-sum vector $(r'_1, r'_2, \ldots, r'_n)^T$ of $C'$ majorizes the row-sum vector  $(r_1, r_2, \ldots, r_n)^T$ of $C$;
\item[(ii)]  $C'$ has a rooted eigenvector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ for $\lambda'$ for some  $\lambda'\in \mathbb{R}$;
\item[(iii)] $C$ has a nonnegative left eigenvector $v^T=(v_1, v_2, \ldots, v_n)$ for $\lambda\in \mathbb{R}$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
\item[(a)] $r_i=r'_i$\qquad for $1\leq i\leq n$ with $v_i\not=0$ when $v'_n\not=0;$
\item[(b)]
$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
\end{enumerate} \qed
\end{thm}

Note that the cases (a)-(b) in Theorem~\ref{t3.1} is from the line (\ref{ne4.1}) in Theorem~\ref{nt3.1}.
The first part of assumption (i) in Theorem~\ref{t3.1}  says that last column is {\it irrelevant} in the comparison of $C$ and $C'$. The following theorem is a dual version of Theorem~\ref{t3.1}.

\begin{thm}\label{t3.1'}
 Let $C=(c_{ij})$, $C'=(c_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[-|n)\geq C'[-|n)$ and the row-sum vector $(r_1, r_2, \ldots, r_n)^T$  of $C$ majorizes the row-sum vector $(r'_1, r'_2, \ldots, r'_n)^T$ of $C'$;
\item[(ii)]  $C'$ has a rooted eigenvector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ for $\lambda'$ for some  $\lambda'\in \mathbb{R}$;
\item[(iii)] $C$ has a nonnegative left eigenvector $v^T=(v_1, v_2, \ldots, v_n)$ for $\lambda\in \mathbb{R}$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\geq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
\item[(a)] $r_i=r'_i$\qquad for $1\leq i\leq n$ with $v_i\not=0$ when $v'_n\not=0;$
\item[(b)]
$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
\end{enumerate}  \qed
\end{thm}

\begin{exam}\label{exam2}
Consider the following three matrices
$$C'_\ell= \begin{pmatrix}
3 & 1 & 1\\ 0 & 0 & 3 \\ 0 & 1 & 2
\end{pmatrix}, \quad  C=\begin{pmatrix}
3 & 1 & 1\\ 1 & 0 & 2 \\ 1 & 1 & 1
\end{pmatrix}, \quad C'_u=\begin{pmatrix}
3 & 2 & 0\\ 1 & 2 & 0 \\ 1 & 2 & 0
\end{pmatrix}$$
with $C'_\ell[-|3)\leq C[-|3) \leq C'_u[-|3),$ and the same row-sum vector $(5, 3, 3)^T$.
Note that $C'_\ell$ has a rooted eigenvector $v'^\ell=(1, 0, 0)^T$ for $\lambda'^\ell=3$
and $C'_u$ has a rooted eigenvector $v'^u=(2, 1, 1)^T$ for $\lambda'^r=4$.
Since $C$ is irreducible, it has a left positive eigenvector $(v_1,v_2,v_3)>0$.
Hence assumptions (i)-(iv) in Theorem~\ref{t3.1} and Theorem~\ref{t3.1'} hold, and
we conclude that $\lambda'^\ell\leq \rho(C)\leq \lambda'^r$.
Since $[3]\times [1]$ is the set of the pairs $(i,j)$ described in Theorem~\ref{t3.1}(b) and Theorem~\ref{t3.1'}(b),
from simple comparison of
the first columns $C'_\ell[-|~1]< C[-|~1] = C'_u[-|~1]$ of these three matrices,
we easily conclude that $3=\lambda'^\ell< \rho(C)= \lambda'^r=4$ by the second part of Theorem~\ref{t3.1} and that of Theorem~\ref{t3.1'}.
\end{exam}

\section{Matrices with a rooted eigenvector}\label{ns4}

Before giving applications of Theorem~\ref{t3.1} and Theorem \ref{t3.1'}, we need to construct $C'$ which possesses a rooted eigenvector for some $\lambda'$. The following lemma comes immediately.

\begin{lem}\label{l4.1}
If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$. \qed
\end{lem}

 A rooted column vector defined in Definition~\ref{d3.1} is generalized to a rooted matrix as follows.
\begin{defn}\label{def4.1}
A  matrix $C'=(c'_{ij})$ is called {\it rooted}  if its  columns and its row-sum vector are all rooted except the last column of $C'$.
\end{defn}

The vertex $Q$ in (\ref{defnq}) is invertible with
$$Q^{-1}=\begin{pmatrix}
1 & 0 & \cdots & 0 & -1 \\
0 & 1 & \cdots & 0 & -1 \\
\vdots & \vdots & \ddots & \vdots & \vdots \\
0 & 0 & \cdots & 1 & -1 \\
0 & 0 & \cdots & 0 & 1 \\
\end{pmatrix}.$$ Multiplying $Q^{-1}$ to $C'Q$ in (\ref{C'Q}),   $Q^{-1}C'Q$ is
\begin{equation}\label{e3.1}\begin{pmatrix}
c'_{11}-c'_{n1}     & c'_{12}-c'_{n2} & \cdots     & c'_{1\ n-1}-c'_{n\ n-1} & r'_1-r'_n \\
c'_{21}-c'_{n1}     & c'_{22}-c'_{n2} & \cdots     & c'_{2\ n-1}-c'_{n\ n-1} & r'_2-r'_n \\
\vdots              & \vdots & \ddots              & \vdots & \vdots \\
c'_{n-1\ 1}-c'_{n1} & c'_{n-1\ 2}-c'_{n2} & \cdots & c'_{n-1\ n-1}-c'_{n\ n-1} & r'_{n-1}-r'_{n} \\
c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & r'_n \\
\end{pmatrix}.
\end{equation}

The matrices $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues. Moreover, $v'$ is an eigenvector of $C'$ for $\lambda'$ if and only if $u=Q^{-1}v'$ is an eigenvector of $Q^{-1}C'Q$ for $\lambda'$. From (\ref{e3.1}),
  $C'$ is rooted if and only if $Q^{-1}C'Q$ is nonnegative.
The first part of the following lemma follows immediately from the above discussion and Theorem~\ref{PF} by choosing $\lambda'=\rho(C')$.

\begin{lem}\label{l5.3}
If $C'$ is a rooted matrix, then $Q^{-1}C'Q$ is nonnegative, $\rho(C')$ is an eigenvalue of $C'$,
and $C'$ has a rooted eigenvector $v'=Qu$ for $\rho(C')$,
where $u$ is a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$.
Moreover, with $v'=(v'_1, v'_2, \ldots, v'_n)^T$,  the following (i)-(ii) hold.
\begin{enumerate}
\item[(i)] If $C' [n|n)$ is positive, then $v'$ is positive.
\item[(ii)] If  $C' [n|n)$ is positive and  $r'_i> r'_n$ for all $1\leq i\leq n-1$, then $v'_j>v'_n$ for all $1\leq j\leq n-1.$
\end{enumerate}
\end{lem}
\begin{proof}
It remains to prove the second part.

(i) suppose that $C' [n|n)$ is positive and $v'_n=0$. Then
$$\sum_{j=1}^{n-1}c'_{nj}v'_j=\sum_{j=1}^nc'_{nj}v'_j=(C'v')_n=\rho(C')v'_n=0.$$
Hence $v'$ is a zero vector since $c'_{nj}>0$ for $j\leq n-1$, a contradiction. So $v'_n>0$ and $v'>0$ since $v'$ is rooted.

(ii) The assumptions imply that the matrix $Q^{-1}C'Q$ in (\ref{e3.1}) is irreducible.
Hence $u$ is positive. By Lemma~\ref{l3.15}(ii), $v'_j>v'_n$ for $1\leq j<n.$
\end{proof}

The largest real eigenvalue of the following matrix will be used to obtain  bounds of the spectral radius of a nonnegative matrix.

Fix  $d,f,r_1,r_2,\ldots,r_n\geq 0$ such that $r_j\geq r_n$ for $1\leq j\leq n-1$, and let
\begin{equation}\label{ee5.2}
M_n(d, f, r_1, r_2, \ldots, r_n)=
\begin{pmatrix}
d & f &  \cdots & f & r_{1}-(d+(n-2)f) \\
f & d &   & f & r_{2}-(d+(n-2)f) \\
\vdots &  & \ddots & \vdots & \vdots \\
f & f & \cdots  & d & r_{n-1}-(d+(n-2)f)\\
f & f & \cdots & f & r_{n}-(n-1)f
\end{pmatrix}
\end{equation} be an $n\times n$ matrix with row-sum vector $(r_1, r_2, \ldots, r_n)^T$.

Note that for any square matrix $C'$, it might be $\rho(C'+dI)\not=\rho(C')+d$, but $\rho_r(C'+dI)=\rho_r(C')+d$ always holds, where $\rho_r(C'+dI)$ and $\rho_r(C')$ are the largest real eigenvalues of $C'+dI$ and $C'$ respectively.
Also $\rho(C')=\rho_r(C')$ if $C'$ is nonnegative.

\begin{lem}\label{l4.4} The following (i)-(ii) hold.
\begin{enumerate}
\item[(i)] The matrix $M_n(d, f, r_1, r_2, \ldots, r_n)$ has a rooted eigenvector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ for the largest real eigenvalue $\rho_r(M_n(d, f, r_1, r_2, \ldots, r_n))$ of $M_n(d, f, r_1, r_2, \ldots, r_n)$.
\item[(ii)] If $f>0$, then $v'>0$.
\end{enumerate}
\end{lem}
\begin{proof} Let $M_n:=M_n(d, f, r_1, r_2, \ldots, r_n)$.
First assume $d\geq f$. Then $M_n$ is rooted. (i)-(ii) follows from (i)-(ii) of Lemma~\ref{l5.3},  in particular $\rho(M_n)=\rho_r(M_n)$.
If  $d<f$, then  the matrix $(f-d)I+M_n$  is a rooted matrix.
As in the first part, let $v'$ be a rooted eigenvector of $(f-d)I+M_n$ for $\rho((f-d)I+M_n).$ Note that $v'$ is also a rooted eigenvector of $M_n$ for $\rho_r(M_n)=\rho((f-d)I+M_n)-(f-d).$ This proves (i), and (ii) follows similarly  from (ii) of Lemma~\ref{l5.3}.
\end{proof}

\section{Equitable partition}\label{s3}

Pattern in $C'$ will make it easier to compute its eigenvalue and to find the bound $\lambda'$ obtained in Theorem~\ref{t3.1} and Theorem~\ref{t3.1'}.
For a partition $\Pi=\{\pi_1, \pi_2, \ldots, \pi_\ell\}$ of $[n]$,
 the $\ell\times \ell$ matrix $\Pi(C'):=(\pi'_{ab})$, where
$$\pi'_{ab}:= \frac{1}{|\pi_a|}\sum_{i\in \pi_a, j\in \pi_b} c'_{ij},$$
is called the {\it quotient matrix} of $C'$ with respect to $\Pi$. In matrix notation,
\begin{equation}\label{e5.1}
\Pi(C')=(S^TS)^{-1}S^TC'S,
\end{equation}
where $S=(s_{jb})$ is the $n\times \ell$ {\it characteristic matrix} of $\Pi$, i.e.,
$$s_{jb}=
\left\{
\begin{array}{ll}
1, & \hbox{if $j\in \pi_b$;} \\
0, & \hbox{otherwise.} \\
\end{array}
\right.$$
for $1\leq j\leq n,$ and $1\leq b\leq \ell.$
If
$$\pi'_{ab}=\sum_{j\in \pi_b} c'_{ij}\qquad (1\leq a, b\leq \ell)$$
for all $i\in \pi_a,$ then  $\Pi(C')=(\pi'_{ab})$ is called
the {\it equitable quotient matrix} of $C'$ with respect to $\Pi.$
Note that $\Pi(C')$ is an equitable quotient matrix if and only if  \begin{equation}\label{e5.2}S\Pi(C')=C'S.\end{equation}

\begin{lem}[{\cite[Lemma 2.3.1]{Brou}}]\label{q1}
If an $n\times n$ matrix $C'$ has an equitable quotient matrix $\Pi(C')$ with respect to partition $\Pi=\{\pi_1, \pi_2, \ldots, \pi_\ell\}$ of $[n]$ with characteristic matrix $S$,  and $\lambda'$ is an eigenvalue of  $\Pi(C')$ with eigenvector $u'$,   then   $\lambda'$ is an  eigenvalue of $C'$ with eigenvector  $Su'$. Moreover, if $u'$ is rooted and $n\in \pi_\ell$, then $Su'$ is rooted.
\end{lem}
\begin{proof} From (\ref{e5.2}),
$C'Su'=S\Pi(C')u'=\lambda' Su'.$ The second statement is clear.
\end{proof}

Under some conditions, the spectral radius is preserved by equitable quotient operation.

\begin{lem}\label{lem2.2'} If $\Pi=\{\pi_1,\ldots, \pi_\ell\}$ is a partition of $[n]$ and
  $C'=(c'_{ij})$ is an $n\times n$ matrix satisfying
 $c'_{ij}=c'_{kj}$ for all $i, k$ in the same part $\pi_a$ of $\Pi$ and $j\in [n],$
 then $C'$ and its quotient matrix $\Pi(C')$ with respect to $\Pi$ have the same set of nonzero eigenvalues.
 In particular, $\rho(C')=\rho(\Pi(C'))$.
\end{lem}
\begin{proof} From the construction of $C'$, $\Pi(C')$ is clear to be an equitable quotient matrix of $C'$.
Let $\lambda'$ be a nonzero eigenvalue of $C'$ with eigenvector $v'=(v'_1,\ldots,v'_n)^T$.
Then $v'_i=(Cv')_i/\lambda'=(Cv')_{k}/\lambda'=v'_{k}$ for all $i, k$  in the same part $\pi_a$ of $\Pi.$
Let $u'_a=v'_i$ with any choice of  $i\in \pi_a.$
Then $u':=(u'_1,\ldots,u'_\ell)\ne 0$, and  $\Pi(C')u'=\lambda' u'$.
 From this and Lemma~\ref{q1}, we know that $C'$ and $\Pi(C')$ have the same set of nonzero eigenvalues, and thus $\rho(C')=\rho(\Pi(C')).$
\end{proof}

\begin{lem}\label{l7.1} For $M_n=M_n(d, f, r_1, r_2, \ldots, r_n)$ defined in \eqref{ee5.2}, where  $d, f\geq 0$ and $r_1\geq r_2\geq \cdots\geq r_n\geq 0$, we have  the following (i)-(iii).
\begin{enumerate}
\item [(i)] The largest real eigenvalue $\rho_r(M_n)$ of $M_n$ satisfies \begin{align*}
    \rho_r(M_n):=&\frac{r_n+d-f+\sqrt{(r_n-d+f)^2+4f\sum_{i=1}^{n-1}(r_i-r_n)}}{2}\\
    \geq& \max(d-f, r_n).\end{align*}
\item[(ii)] If $r_n=0$, then $$\rho_r(M_n)=\frac{d-f+\sqrt{(d-f)^2+4f m}}{2},$$
where $m:=\sum_{i=1}^{n-1} r_i$ is the sum of all entries of $M_n$.
\item [(iii)]  If $r_t=r_n$ for $t\leq n$, then $\rho_r(M_t)=\rho_r(M_n).$
\end{enumerate}
\end{lem}
\begin{proof}
(i)  We consider the matrix $M_n+(f-d)I$. Note that $(M_n+(f-d)I)^T$ has equitable quotient matrix
$$\Pi((M_n+(f-d)I)^T)=\begin{pmatrix} (n-1)f & f \\  \sum_{i=1}^{n-1} (r_i-(d+(n-2)f))  & r_n-(d+(n-2)f) \end{pmatrix}$$
with respect to the  partition $\Pi=\{\{1, 2, \ldots, n-1\}, \{n\} \}$ of $[n]$,
which has two eigenvalues $$\frac{r_n-d+f\pm\sqrt{(r_n-d+f)^2+4f\sum_{i=1}^{n-1}(r_i-r_n)}}{2}.$$
Since $((M_n+(f-d)I)^T)_{ij}=((M_n+(f-d)I)^T)_{kj}$ all $i,k\in [n-1]$ and $j\in [n]$ and by  Lemma~\ref{lem2.2'}, $(M_n+(f-d)I)^T$ has eigenvalues
$$0^{n-2},\frac{r_n-d+f\pm\sqrt{(r_n-d+f)^2+4f\sum_{i=1}^{n-1}(r_i-r_n)}}{2},$$
and $M_n$ has eigenvalues
$$(d-f)^{n-2},\frac{r_n+d-f\pm\sqrt{(r_n-d+f)^2+4f\sum_{i=1}^{n-1}(r_i-r_n)}}{2}.$$
Note that
$$\frac{r_n+d-f+\sqrt{(r_n-d+f)^2+4f\sum_{i=1}^{n-1}(r_i-r_n)}}{2}\geq \max(d-f, r_n).$$
So the proof of (i) is complete.

(ii) and (iii)  follow from (i) immediately.
\end{proof}

\section{Spectral upper bounds with prescribed sum of entries}

Let $J_k$, $I_k$ and $O_{k}$ be the $k\times k$ all-one matrix, the $k\times k$ identity matrix and the $k\times k$ zero matrix respectively. We recall an old  result of Richard Stanley \cite{s87}.

\begin{thm}[\cite{s87}]\label{t6.1s}
Let $C=(c_{ij})$ be an $n\times n$ symmetric (0,1) matrix with zero trace. Let the number of 1's of $C$ be $2e$. Then
$$\rho(C)\leq \frac{-1+\sqrt{1+8e}}{2}.$$
Equality holds if and only if
$$e=\binom{k}{2}$$
and $PCP^T$ has the form
$$
\left(
\begin{matrix}
J_k-I_k & 0 \\
0   & O_{n-k}
\end{matrix}
\right)=(J_k-I_k)\oplus O_{n-k}
$$
for some permutation matrix $P$ and positive integer $k$.
\end{thm}

The following theorem generalizes Theorem~\ref{t6.1s} to nonnegative matrices, not necessary symmetric.
\begin{thm}\label{tt6.1}
Let $C=(c_{ij})$ be an $n\times n$ nonnegative matrix. Let $m$ be the sum of entries
and $d$ (resp. $f$) be any number which is larger than or equal to the largest diagonal element (resp. the largest off-diagonal element) of $M$.
Then
 \begin{equation}\label{e7.1}
\rho(C)\leq \frac{d-f+\sqrt{(d-f)^2+4mf}}{2}.
\end{equation}
Moreover, if $mf>0$ then the equality in (\ref{e7.1}) holds
 if and only if
 $m=k(k-1)f+kd$ and
 $PCP^T$ has the form
 $$\begin{pmatrix}
 fJ_k+(d-f)I_k & 0\\
 0   & O_{n-k}
 \end{pmatrix}=
 (fJ_k+(d-f)I_k)\oplus O_{n-k}$$   for some permutation matrix $P$ and some  nonnegative integer $k$.
\end{thm}

\begin{proof} If $f=0$ then the nonzero entries only appear in the diagonal of $C$, so $\rho(C)\leq d$ and
(\ref{e7.1}) holds. Assume $f>0$ for the remaining.
Consider the $(n+1)\times (n+1)$ nonnegative matrix $M=C\oplus O_1$ which  has row-sum vector $(r_1,r_2,\ldots,r_n,r_{n+1})^T$ with $r_{n+1}=0$ and  a nonnegative left eigenvector $v^T$ for $\rho(M)=\rho(C)$.
Let $C'=M_{n+1}(d, f, r_1, r_2, \ldots, r_{n+1})$ as defined in (\ref{ee5.2}) which has the same row-sum vector of $M$, and has a positive rooted eigenvector $v'=(v'_1, v'_2, \ldots, v'_{n+1})^T$ for $\rho_r(C')$ by Lemma~\ref{l4.4}(i).
Clearly $M[-|n+1)\leq C'[-|n+1)$ and $v^Tv'>0.$ Hence the assumptions (i)-(iv) in Theorem~\ref{t3.1}
hold with $(C, \lambda, \lambda')=(M, \rho(M), \rho_r(C'))$.
 Now by Theorem~\ref{t3.1} and Lemma~\ref{l7.1}(ii), we have
$$\rho(C)=\rho(M)\leq \rho_r(C')=\frac{d-f+\sqrt{(d-f)^2+4mf}}{2},$$
finishing the proof of the first part.

To prove the second part, assume $m=k(k-1)f+kd$ and $PCP^T=(fJ_k+(d-f)I_k)\oplus O_{n-k}$ for one direction.
Using $\rho(C)=\rho(PCP^T)=\rho(fJ_k+(d-f)I_k),$ we have
$$\rho(C)=(k-1)f+d=\frac{d-f+\sqrt{(d-f)^2+4mf}}{2}.$$

For the other direction, assume $\rho(C)=\rho_r(C')$ and $mf>0$. In particular $C\not=0$ and $M\not=0$.
Let $(v_1, v_2, \ldots, v_{n+1})$ be a nonnegative left eigenvector of $M$. Then $v_{n+1}=0$.
 Write $\tilde{v}^T=(v_1, v_2, \ldots,v_n)$.
We first assume that $C$ has no zero row. Then $r_i>r_{n+1}=0$ for $1\leq i\leq n$. By Lemma~\ref{l5.3}(ii) with
$(C', n)=(M, n+1)$,  we have $v'_j>v'_{n+1}$. Then
$c_{ij}=m_{ij}=c'_{ij}$ for the indices $1\leq i\leq n$ with $v_i\not=0$ and any $1\leq j\leq n$ by Theorem \ref{t3.1}(b).
Hence
\begin{equation}\label{ee6.2}\rho(C)\tilde{v}^T=\tilde{v}^TC=\tilde{v}^TC'(n+1|n+1)=\tilde{v}^T(fJ+(d-f)I).\end{equation}
 Since $\tilde{v}^T$ is a nonnegative left eigenvalue of the irreducible nonnegative matrix $fJ+(d-f)I$ for $\rho(C)$, we have  $\tilde{v}>0$. This together with $fJ+(d-f)I\geq C$ and (\ref{ee6.2}) will imply
$C=fJ+(d-f)I$, finishing the proof for the case under the assumption that $C$ has no zero row.
Assume that $C$ has $n-k$ zero rows for some $1\leq k\leq n-1$. Then there is a permutation matrix $P$ such that all zero rows of $PCP^T$ appear in the end, so the $(n-k)\times n$ submatrix  $PCP^T([k]|-]$ of $PCP^T$ is $0$ and the $k\times n$ submatrix $PCP^T[[k]|-]$ of $PCP^T$  has no zero row. Let $C_1=PCP^T[[k]|[k]]$
and $m'$ be the sum of entries in $C_1$. Notice that $\rho(C_1)=\rho(C)$ and  $m'\leq m$.
Applying the first part of the theorem to $C_1$, we have
$$\rho(C_1)\leq \frac{d-f+\sqrt{(d-f)^2+4m'f}}{2}\leq \frac{d-f+\sqrt{(d-f)^2+4mf}}{2}=\rho(C)=\rho(C_1),$$
forcing $m'=m$, $C_1$ has no zero row and $C_1=fJ_k+(d-f)I_k$.  Hence $PCP^T[[k]|[k])=0$ and this implies  $PCP^T=(fJ_k+(d-f)I_k)\oplus O_{n-k}$ and  $m=k(k-1)f+kd$.
\end{proof}

\section{$C'$ admitting an equitable quotient}\label{s3.5}

From now on the square matrix $C$ is nonnegative, and the eigenvalue $\rho(C)$ of $C$ is corresponding to a nonnegative left eigenvector $v^T$ by Theorem~\ref{PF}(i). Hence the assumption (iii) in Theorem~\ref{t3.1} and Theorem~\ref{t3.1'} immediately holds. In Lemma~\ref{l4.1} and Lemma~\ref{l5.3}, we know that a rooted matrix $C'$ and its translates are possessed of a rooted eigenvector for $\rho_r(C')$. In this section, we shall apply properties of the equitable quotient to provide matrices which are not translated from a rooted matrix but still have positive rooted eigenvectors.
We use this method to reduce the size of $C'$ in finding the bound $\lambda'$ of $\lambda=\rho(C)$ obtained in Theorem~\ref{t3.1} and Theorem~\ref{t3.1'}.

\begin{thm}\label{t6.1}
Let $C=(c_{ij})$ be a nonnegative $n\times n$ matrix with row-sum vector $(r_1,\ldots,r_n)^T$,  and
 $\Pi=\{\pi_1, \pi_2, \ldots, \pi_\ell\}$ a partition of $\{1, 2, \ldots, n\}$ with $n\in \pi_\ell$.
Let $C'=(c'_{ij})$ be an $n\times n$ matrix that admits
  an $\ell\times \ell$ equitable quotient matrix $\Pi(C')=(\pi'_{ab})$ of $C'$  with respect to $\Pi$ satisfying the following
(i)-(ii):
\begin{enumerate}
\item[(i)] $C[-|n)\leq C'[-|n)$ and
$\Pi(C')$ has row-sum vector  $\Pi(r')=$$(\pi(r')_1,$ $\pi(r')_2,$ $\ldots,$ $\pi(r')_\ell)^T$ with $\pi(r')_a=\max_{i\in \pi_a}r_i$ for $1\leq a\leq \ell$.
\item[(ii)] $\Pi(C')$ has a positive rooted eigenvector $\Pi(v')=$$(\pi(v')_1,$ $\pi(v')_2,$ $\ldots,$ $\pi(v')_\ell)^T$ for some nonnegative eigenvalue $\lambda'$.
\end{enumerate}
Then
\begin{equation}\label{e8.1}
\rho(C)\leq \lambda'.
\end{equation} Moreover, if $C$ is irreducible, then
$\rho(C)= \lambda'$ if and only if
\begin{enumerate}
\item[(a)] $r_i=\pi(r')_a$ \qquad for $1\leq a\leq \ell$ and $i\in \pi_a$, and
\item[(b)]  $c'_{ij}=c_{ij}$ \qquad for all $1\leq i, j\leq n$ such that for $1\leq b\leq \ell$ with $j\in \pi_b$ we have  $\pi(v')_b>\pi(v')_\ell$.
\end{enumerate}
\end{thm}

\begin{proof} Let $S$ be the $n\times \ell$ characteristic matrix of $\Pi.$
 From the construction of $\Pi$ and $C'$, $r'=S\Pi(r')=(r'_1,\ldots,r'_n)^T$ is the row-sum vector of $C'$, and
 $v'=S\Pi(v')$ is a positive rooted eigenvector of $C'$ for $\lambda'$  by Lemma~\ref{q1}. Since $C$ is nonnegative, there exists  a nonnegative left eigenvector $v^T$ of $C$ for $\rho(C)$ by Theorem~\ref{PF}(i).
  Hence $v^Tv'>0$.
   Thus assumptions (i)-(iv) of Theorem~\ref{t3.1} hold, concluding $\rho(C)\leq \lambda'$.

   Suppose that $C$ is irreducible. Then the above $v$ is positive. Hence the equivalent condition (b) of $\rho(C)=\lambda'$ in Theorem~\ref{t3.1} becomes
  $c'_{ij}=c_{ij}$ for $1\leq i\leq n$,$1\leq j\leq n-1$ with $v'_j>v'_n$, and this is equivalent to the (b) here from the structure of  $v'=S\Pi(v')$.
  The equivalent condition (a) here is immediate from that in Theorem~\ref{t3.1} since $r'_i=\pi(r')_a$ for $i\in\pi_a$.
\end{proof}

Notice that the irreducible assumption of $C$ in the second part of Theorem~\ref{tt6.1} is not necessary.
The following example shows that this is a must in that of Theorem~\ref{t6.1}.

 \begin{exam}
 Consider the following two $3\times 3$ matrices
 $$C=\begin{pmatrix}
 0 & 3 & 0 \\
 1 &  1 & 0\\
 1 & 0 & 0
 \end{pmatrix},\quad   C'=\begin{pmatrix}
 0 & 3 & 0 \\
 1 &  1 & 0\\
 1 & 0 & 1
 \end{pmatrix}\quad  {\rm and~~ }\Pi(C')=\begin{pmatrix} 0 & 3\\ 1 & 1 \end{pmatrix}$$
 is the equitable quotient matrix of $C'$  with respect to the partition $\Pi=\{\{1\}, \{2, 3\}\}.$
  Note that $C[-|3)= C'[-|3)$, and the row-sum vector $(3, 2, 1)^T$ of $C$ is majorized by the row-sum vector $(3, 2, 2)^T$ of $C'$.
 Since $\Pi(C')+I$ is positive and rooted, $\Pi(C')$ has a positive rooted eigenvector for $\lambda'=\rho(\Pi(C'))=(1+\sqrt{13})/2.$
 Hence assumptions (i)-(ii) in Theorem~\ref{t6.1} hold. By direct computing, $\rho(C)=(1+\sqrt{13})/2$, so the the equality in
(\ref{e8.1}) holds.  However, $r_2=2\not=1=r_3$, a contradiction to (a) in Theorem \ref{t6.1}.
 This contradiction is because of the reducibility of $C$.
 \end{exam}

The following is a dual version of Theorem~\ref{t6.1}.

\begin{thm}\label{t6.2}
Let $C=(c_{ij})$ be a nonnegative $n\times n$ matrix with row-sum vector $(r_1,\ldots,r_n)^T$,  and
 $\Pi=\{\pi_1, \pi_2, \ldots, \pi_\ell\}$ a partition of $\{1, 2, \ldots, n\}$ with $n\in \pi_\ell$.
Let $C'$ be an $n\times n$ matrix that admits
  an $\ell\times \ell$ equitable quotient matrix $\Pi(C')=(\pi'_{ab})$ of $C'$  with respect to $\Pi$ satisfying the following
(i)-(ii):
\begin{enumerate}
\item[(i)] $C[-|n)\geq C'[-|n)$ and
$\Pi(C')$ has row-sum vector  $\Pi(r')=$$(\pi(r')_1,$ $\pi(r')_2,$ $\ldots,$ $\pi(r')_\ell)^T$ with $\pi(r')_a=\min_{i\in \pi_a}r_i$ for $1\leq a\leq \ell$.
\item[(ii)] $\Pi(C')$ has a positive rooted eigenvector $\Pi(v')=$$(\pi(v')_1,$ $\pi(v')_2,$ $\ldots,$ $\pi(v')_\ell)^T$ for some nonnegative eigenvalue $\lambda'$.
\end{enumerate}
Then
\begin{equation}
\rho(C)\geq \lambda'.
\end{equation} Moreover, if $C$ is irreducible then
$\rho(C)= \lambda'$ if and only if
\begin{enumerate}
\item[(a)] $r_i=\pi(r')_a$ \qquad for $1\leq a\leq \ell$ and $i\in \pi_a$, and
\item[(b)] $c'_{ij}=c_{ij}$ \qquad for all $1\leq i, j\leq n$ such that for $1\leq b\leq \ell$ with $j\in \pi_b$ we have  $\pi(v')_b>\pi(v')_\ell$.
\end{enumerate}\qed
\end{thm}

\begin{rem}
\begin{enumerate}
\item[(i)] The positive assumption of $\Pi(v')$ in (ii)  of  Theorem~\ref{t6.2} can be removed in concluding the first part $\rho(C)\geq \lambda'$.
The following is a proof:

{\it Proof.} From (i) and referring to (\ref{C'Q}), we have $CQ\geq C'Q\geq 0$.
Let $v'=S\Pi(v')$ be a rooted eigenvector of $C'$ for $\lambda'$ as shown in the above proof.
Then $u=Q^{-1}v'$ is nonnegative by Lemma~\ref{l3.15}(i), so
$Cv'=CQu\geq C'Qu= C'v'=\lambda'v'.$
Since $v'$ is nonnegative,  $\rho(C)\geq \lambda'$ by Theorem~\ref{PF}(iii). \qed

\item[(ii)] The following counterexample shows that to conclude $\rho(C)\leq \lambda'$, the positive assumption of $\Pi(v')$ in (ii)  of  Theorem~\ref{t6.1} can not  be removed:
    $$C=C'=\begin{pmatrix}1& 2\\ 0 & 2\end{pmatrix}, \lambda'=1, v'=\begin{pmatrix} 1\\ 0\end{pmatrix}, \rho(C)=2, v^T=(0, 1),$$
    where the trivial partition $\Pi=\{\{1\}, \{2\}\}$ of $\{1, 2\}$ is adopted.
\end{enumerate}
\end{rem}

We provide an example in applying Theorem~\ref{t6.1}.

\begin{exam}\label{exammain}
Consider the following two $7\times 7$ matrices $C$ and $C'$ expressed below under the partition $\Pi=\{\{1, 2, 3\}, \{4, 5\}, \{6, 7\}\}:$
\begin{equation}\label{e8.6}C=\left(
\begin{tabular}{ccc|cc|cc} 2 & 1 & 3 & 3 & 3 & 12 & 0\\ 4 & 2 & 1 & 4 & 2 & 6 & 4\\ 2 & 3 & 1 & 4 & 1 & 8 &3 \\
\hline
3 & 5 & 3 & 1 & 1& 3 & 4\\ 5 & 6 & 1 & 1 & 0 & 3 &3\\
\hline
0 & 2 & 1 & 2 & 2 & 6 & 0\\  2 & 2 & 0 & 2 &1& 1 &4\end{tabular}\right), \qquad
  C'=\left(\begin{tabular}{ccc|cc|cc} 2 & 2 & 3 & 3 & 3 & 12 & -1\\ 4 & 2 & 1 & 4 & 2 & 6 & 5\\ 2 & 3 & 2 & 4 & 2 & 8 & 3 \\ \hline
 4& 5 & 3 & 1 & 1& 3 & 3\\
 5 & 6 & 1 & 1 & 1 & 3 &3\\
 \hline 1 & 2 & 1 & 2 & 2 & 6 & -1\\  2 & 2 & 0 & 2 &2& 1 &4\end{tabular}\right).\end{equation}
Apparently, $C[-|7)\leq C'[-|7),$ and
 the row-sum vector
$(24, 23, 22, 20,$ $19, 13, 12)^T$ of $C$ is majorized by the  row-sum vector $(24, 24, 24, 20, 20, 13, 13)^T$ of $C'$,
so assumption (i)  of Theorem~\ref{t6.1} holds.
Note that $C'$ is not rooted  and neither of its translates.
Since  $C'$ has equitable quotient matrix
$$\Pi(C')=\begin{pmatrix} 7 & 6 & 11 \\ 12 & 2 & 6\\ 4& 4 & 5\end{pmatrix},$$
in which $\Pi(C')+2I$ is rooted, so assumption (ii) of Theorem~\ref{t6.1} holds for $\lambda'=\rho_r(C')$ by Lemma~\ref{l4.1} and Lemma~\ref{l5.3}(i).
Hence by Theorem~\ref{t6.1}, $\rho(C)\leq \rho_r(\Pi(C'))\approx 18.6936.$

If applying Lemma~\ref{lem1.2} by constructing the following nonnegative matrix $C''$ that majors $C$, and find its equitable quotient matrix $\Pi(C'')$ with respect to the above partition $\Pi$:
$$C''=\left(
\begin{tabular}{ccc|cc|cc} 2 & 2 & 3 & 3 & 3 & 12 & 0\\ 4 & 2 & 1 & 4 & 2 & 6 & 6\\ 2 & 3 & 2 & 4 & 2 & 8 &4 \\
\hline
4 & 5 & 3 & 1 & 1& 3 & 4\\ 5 & 6 & 1 & 1 & 1 & 3 &4\\
\hline
 1& 2 & 1 & 2 & 2 & 6 & 0\\  2 & 2 & 0 & 2 &2& 2 &4\end{tabular}\right), \qquad \Pi(C'')=\begin{pmatrix} 7 & 6 & 12 \\ 12 & 2& 7\\ 4& 4 & 6\end{pmatrix},$$
 one will find the upper bound
$$\rho(C'')=\rho (\Pi(C'')\approx 19.4$$
of $\rho(C)$ which is larger than the previous one.
\end{exam}

\section{More irrelevant columns}

Considering the part $\pi_\ell$ of column indices of $C$ and $C'$ in the assumption (i) of Theorem~\ref{t6.1},
the assumption $C[-|\pi_\ell]\leq C'[-|\pi_\ell]$ for $C'$ is not really necessary. We might replace the columns indexed by
$\pi_\ell$ in $C'$ by any other columns and adjust the values in the last column of keeping the row-sums of $C'$ unchanged.
In this situation, the columns of $C'$ indexed by $\pi_\ell$ are irrelevant columns (in the comparison of $C$ and $C'$).
For example in Example~\ref{exammain},
the values in the  $6$-th column of $C'$ can be changed to any values (e.g., $(a, b, c, d, e, f, g)^T$), if the values in the $7$-th column of $C'$ make the corresponding change (e.g., $(11-a, 11-b, 11-c, 6-d, 6-e, 5-f, 5-g)^T$ correspondingly), i.e., columns $6$ and $7$ of $C'$ are irrelevant.  The following theorem generalizes this idea when restricting $\Pi[C']$ in Theorem~\ref{t6.1} to be a rooted matrix or its translate.

\begin{thm}\label{main3}
Let  $\Pi=\{\pi_1, \pi_2, \ldots, \pi_\ell\}$ be a partition of $[n]$ with $n\in \pi_\ell$, and
$C$ be an $n\times n$ nonnegative matrix with row-sums $r_1\geq r_2\geq \cdots \geq r_n$.
For $1\leq a \leq \ell$ and $1\leq b\leq \ell-1,$
choose  $r''_a,$ $c''_{ab}$ such that
$$
\left\{
\begin{array}{rcl}
r''_a&=&\max_{i\in \pi_a} r_i;\\
c''_{ab}   &\geq&\sum_{j\in \pi_b} c_{ij}\qquad \hbox{for all } i\in \pi_a;\\
c''_{ab}   &\geq& c''_{\ell b}> 0 \qquad \hbox{for } a\not=b
\end{array}
\right.$$
and let
$$c''_{a\ell}=r''_a-\sum_{j=1}^{\ell-1} c''_{aj}.$$
Then the $\ell\times\ell$ matrix $C''=(c''_{ab})$  has a positive rooted eigenvector $v''=(v''_1, v''_2, \ldots, v''_\ell)^T$ for $\rho_r(C'')$,
and  $\rho(C)\leq \rho_r(C'').$
Moreover, if $C$ is irreducible, then $\rho(C)= \rho_r(C'')$ if and only if
\begin{enumerate}
\item[(a)] $r_i=r''_a$ \qquad for $1\leq a\leq \ell$ and $i\in \pi_a$, and
\item[(b)]
$\sum_{j\in \pi_b}c_{ij} =c''_{ab}\qquad \hbox{for all $1\leq a, b\leq \ell$ with $v''_b>v''_\ell$ and  $i\in \pi_a$}.$
\end{enumerate}
\end{thm}

\begin{proof} From the construction of $C''$,
$C''+dI$ is a positive rooted matrix for some $d$ large enough, so $C''$ has a positive rooted eigenvector for $\rho_r(C'')$ by Lemma~\ref{l4.1} and Lemma~\ref{l5.3}(i).
In view of the construction of $C'$ in Example~\ref{exammain}, we construct an $n\times n$ matrix $C'$ such that $C'$ has the equitable quotient matrix $\Pi(C')=C''$ and assumptions (i)-(ii) of Theorem \ref{t6.1} hold for $\lambda'=\rho_r(\Pi(C'))$.
Hence the remaining follows from the conclusion of Theorem \ref{t6.1}.
\end{proof}

\begin{rem}
Theorem~\ref{dz2013} is a special case  of Theorem~\ref{main3} with $\Pi=\{\{1\}, \{2\}, \ldots, \{\ell-1\}, \{\ell, \ell+1, \ldots, n\}\}$ and $C''=M_{\ell}(d,f,r_1,r_2,\ldots,r_\ell)$ as shown in (\ref{ne1.2}). The equality case needs to apply Lemma~\ref{l7.1}(iii) by choosing a new $\ell$ to be the least $t$ such that $r_t=r_\ell$.
By using the more irrelevant columns idea in Theorem~\ref{main3}, the assumption  $f:=\max_{1\leq i\not=j\leq n} c_{ij}$ and $d:=\max_{1\leq i\leq n}c_{ii}$ in Theorem~\ref{dz2013} can be replaced by the possible smaller number $f:=\max_{1\leq i\leq n,1\leq j\leq \ell-1,i\ne j} c_{ij}$ and $d:=\max_{1\leq i\leq \ell-1} c_{ii}$ respectively.
\end{rem}

The following is a dual theorem of Theorem~\ref{main3}.
\begin{thm}\label{main4}
Let  $\Pi=\{\pi_1, \pi_2, \ldots, \pi_\ell\}$ be a partition of $[n]$ with $n\in \pi_\ell$, and
$C$ an $n\times n$ nonnegative matrix with row-sums $r_1\geq r_2\geq \cdots \geq r_n$.
For $1\leq a \leq \ell$ and $1\leq b\leq \ell-1,$
choose  $r''_a,$ $c''_{ab}$ such that
\begin{equation}\label{e9.1}
\left\{
\begin{array}{rcl}
r''_a&=&\min_{i\in \pi_a} r_i;\\
c''_{ab}   &\leq&\sum_{j\in \pi_b} c_{ij}\qquad \hbox{for all } i\in \pi_a;\\
c''_{ab}   &\geq& c''_{\ell b}> 0 \qquad \hbox{for } a\not=b
\end{array}
\right.\end{equation}
and let
\begin{equation}\label{e9.2}
c''_{a\ell}=r''_a-\sum_{j=1}^{\ell-1} c''_{aj}.
\end{equation}
Then the $\ell\times\ell$ matrix $C''=(c''_{ab})$  has a positive rooted eigenvector $v''=(v''_1, v''_2, \ldots, v''_\ell)^T$ for $\rho(C'')$,
and
$\rho(C)\geq \rho(C'').$
Moreover, if $C$ is irreducible, then $\rho(C)= \rho(C'')$ if and only if
\begin{enumerate}
\item[(a)] $r_i=r''_a$ \qquad for $1\leq a\leq \ell$ and $i\in \pi_a$, and
\item[(b)]
$\sum_{j\in \pi_b}c_{ij} =c''_{ab}\qquad \hbox{for all $1\leq a, b\leq \ell$ with $v''_b>v''_\ell$ and  $i\in \pi_a$}.$
\end{enumerate}
\end{thm}

\section{Some new lower bounds of spectral radius}

We shall apply Theorem~\ref{main4} to obtain a lower bound of $\rho(C)$ for a nonnegative matrix $C$.

\begin{thm}\label{main5}
Let
$C=(c_{ij})$ be an $n\times n$ nonnegative matrix with row-sums $r_1\geq r_2\geq \cdots \geq r_n$.
For $1\leq t< n,$ let $\Pi_t=\{\{1, \ldots, t\}, \{t+1, \ldots, n\}\}$ be a partition of $[n]$.
For $d\geq\max_{t<i\leq n}c_{ii}$ and $f\geq\max_{1\leq i\leq n, t<j\leq n, i\not=j}c_{ij},$
assume that $0<r_n-(n-t-1)f-d\leq r_t-(n-t)f.$
Then
\begin{equation}\label{ne9.1}\rho(C)\geq \frac{r_t-f+d+\sqrt{(r_t-(2n-2t-1)f-d)^2+4(n-t)f(r_n-(n-t-1)f-d)}}{2}.\end{equation}
Moreover, if $C$ is irreducible and $f>0$, then the equality holds in (\ref{ne9.1}) if and only if $r_1=r_n$ or
\begin{enumerate}
\item[(a)] $r_1=r_t$ and $r_{t+1}=r_n$, and
\item[(b)]
$\sum_{j\in [t]}c_{ij} =r_t-(n-t)f\quad \hbox{for all  $i\in [t]$},$ and

$\sum_{j\in [t]}c_{ij} =r_n-(n-t-1)f-d\quad \hbox{for all  $t<i\leq n$}$.
\end{enumerate}
\end{thm}
\begin{proof} The lower bound of $\rho(C)$ in (\ref{ne9.1}) follows by
applying Theorem~\ref{main4} with the following positive rooted matrix
$$C''=\begin{pmatrix}
 r_t-(n-t)f & (n-t)f \\
 r_n-(n-t-1)f-d& (n-t-1)f+d
 \end{pmatrix},$$
 which has row-sum vector $(r_t, r_n)^T$ and the assumptions in (\ref{e9.1}) and (\ref{e9.2}) of Theorem~\ref{main4} hold from the assumptions.
 Note that $C''$ has a positive rooted eigenvector  $(v''_1, v''_2)^T$
 for $\rho(C'')$ by  Lemma~\ref{l5.3}(i), and the value
  $\rho(C'')$ is as shown  in  the right of (\ref{ne9.1}).
To study the equality case in (\ref{ne9.1}), we apply conditions (a)-(b) in Theorem~\ref{main4},
in which (a) is exactly the (a) of this theorem.
If $v''_1>v''_2$ then the condition (b) of this theorem is exactly the (b) of Theorem~\ref{main4}.
Notice that  $v''_2=v''_1$ if and only if  $\rho(C'')=r_t=r_n$ by Theorem \ref{PF}
using the irreducible property of  $C''$. This is also equivalent to  $r_1=r_n$ under the condition (a).
\end{proof}

The following corollary restricts Theorem~\ref{main5} to binary matrix $C$.
\begin{cor}\label{cor10.2}
Let
$C=(c_{ij})$ be an $n\times n$ (0, 1) matrix with row-sums $r_1\geq r_2\geq \cdots \geq r_n>0$,
and choose $t\geq n-r_n+1$ and $t\leq n$. Then
\begin{equation}\label{ne9.2}
\rho(C)\geq \frac{r_t+\sqrt{r_t^2-4(r_n-1)(r_t-r_n)}}{2}.\end{equation}
Moreover, if $C$ is irreducible, then equality holds in (\ref{ne9.2}) if and only if $r_1=r_n$ or
\begin{enumerate}
\item[(a)] $r_1=r_t$ and $r_{t+1}=r_n$, and
\item[(b)]
$\sum_{j\in [t]}c_{ij} =r_t-(n-t)\quad \hbox{for all  $i\in [t]$},$ and

$\sum_{j\in [t]}c_{ij} =r_n-(n-t)\quad \hbox{for all  $t<i\leq n$}$.
\end{enumerate}\qed
\end{cor}
\begin{proof}
If $t=n$ then (\ref{ne9.2}) becomes $\rho(C)\geq r_n$, so the corollary follows   from Lemma~\ref{lem1.1}.
Assume $t<n$. Since the assumptions in Theorem~\ref{main5} clearly holds with $d=f=1,$ the corollary also holds by \eqref{ne9.1} in this case.
\end{proof}

One can easily check that the right of (\ref{ne9.2}) is at least $r_n$ (with equality iff $r_t=r_n$), so the above lower bound is better than the known one $r_n$
in Lemma~\ref{lem1.1}.

%\bibliographystyle{plainnat}
%\bibliography{references}
%\bibliographystyle{elsarticle-harv}
%\biboptions{authoryear}
%\bibliography{references}
%\bibliography{bibliography}
\section*{References}
\begin{thebibliography}{20}\frenchspacing

\bibitem{bh:85}
R.A. Brauldi, A.J. Hoffman, On the spectral radius of (0,1)-matrices,
{\it Linear Algebra Appl.} 65 (1985), 133-146.

\bibitem{Brou}
A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012.

\bibitem{cls:13}
\newblock{Yingying Chen, Huiqiu Lin, Jinlong Shu,
Sharp upper bounds on the distance spectral radius of a graph,}
\newblock{\it Linear Algebra Appl.} 439 (2013), 2659-2666.

\bibitem{dz}
X. Duan, B. Zhou, Sharp bounds on the spectral radius of a nonnegative matrix,
{\it Linear Algebra Appl.} 439 (2013), 2961-2970.

\bibitem{ez}
M. N. Ellingham, X. Zha, The Spectral Radius of Graphs on Surfaces,
{\it J. Combin. Theory Ser.} B 78 (2000), 45-56.

\bibitem{h:98}
Yuan Hong, Upper bounds of the spectral radius of graphs in terms of genus,
{\it J. Combin. Theory Ser.} B 74 (1998), 153-159.

\bibitem{hsf:01}
Yuan Hong, Jin-Long Shu, Kunfu Fang, A sharp upper bound of the spectral radius of graphs,
{\it J. Combin. Theory Ser.} B 81 (2001), 177-183.

\bibitem{Horn}
 R. A. Horn , C. R. Johnson, {\it Matrix analysis}, Cambrigde University Press, 1985.

\bibitem{hw:13}
\newblock{Y.-P. Huang and C.-W. Weng},
\newblock{Spectral radius and average $2$-degree sequence of a graph,}
\newblock{\it Discrete Math. Algorithms Appl.} 6(2) (2014), 1450029.

\bibitem{lw13}
C.-A. Liu and C.-W. Weng, Spectral radius and degree sequence of a graph,
{\it Linear Algebra Appl.} 438 (2013), 3511-3515.

\bibitem{Liu}
C.-A. Liu and C.-W. Weng, Spectral radius of bipartite graphs,
{\it Linear Algebra Appl.} 474 (2015), 30-43.

\bibitem{s87}
R. P. Stanley, A bound on the spectral radius of graphs with $e$ edges,
{\it Linear Algebra Appl.} 87 (1987), 267-269.

\bibitem{sw:04}
\newblock{J. Shu and Y. Wu, Sharp upper bounds on the spectral radius of graphs,}
\newblock{\it Linear Algebra Appl.} 377 (2004), 241-248.

\end{thebibliography}

\end{document}

\grid

### 2020-09-05 spectral radius of matrix new method/thesis/1130out.tex
first commit

\documentclass[12pt]{report}%{article}

\topmargin 0pt

\topmargin=-1.5cm
\oddsidemargin=0.7cm
\textheight=23.5cm
\textwidth=15cm
\setlength{\baselineskip}{24pt}
\renewcommand{\baselinestretch}{1.5} %行

\usepackage{fontspec}   %加這個就可以設定字體
\usepackage{xeCJK}       %讓中英文字體分開設置
%\usepackage{times}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ulem}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{tabularx,array}
\usepackage{pgf,tikz}
%\usepackage{colortbl}

\usetikzlibrary{arrows}
\setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
\XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
\XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
\title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
\author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
\date{} %不要日期

\def\UrlFont{\rm}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[chapter]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{remark}[thm]{Remark}
\newtheorem{eg}[thm]{Example}
\newtheorem{conj}[thm]{Conjecture}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{ex}[thm]{Exercise}
\newtheorem{prob}[thm]{Problem}
\newtheorem{exam}[thm]{Example}
\newtheorem{nota}[thm]{Notation}
\newtheorem{rem}[thm]{Remark}
\newtheorem{ques}[thm]{Question}
\newtheorem{pof}[thm]{Proof.}

%\renewcommand {\refname} {Bibliography}

\begin{document}

\chapter{Preliminaries}

Let $\mathbb{R}$ and $\mathbb{C}$ denote the field of real numbers and complex numbers respectively.

\begin{defn}
    Let $C$ be an $n \times n$ real matrix, and $u \in \mathbb{R}^n$ be a column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ of C corresponding to an $\it{eigenvector}$ if $Cu = \lambda u$

\end{defn}

\begin{defn}

When $C$ is a real square matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$ is defined by
$$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
where $|\lambda|$ is the magnitude of complex number $\lambda.$
\end{defn}

We are interested in spectral radius of the following matrix associated with a simple graph.

\begin{defn} Given an undirected graph
G, the$\textit{ adjacency matrix}$ of G is the square matrix $A = (a_{ij})$ indexed by vertices of G,
and
\[a_{ij} =\begin{cases}
1, \text{if $i$ is adjacent to $j$}, \\
0, \text{otherwise.}
\end{cases}
\]

\end{defn}

\begin{defn}
Given an undirected graph G, the $\textit{spectral radius}$ of G is the spectral radius of the adjacency matrix A.
\end{defn}

    We introduce a notation of submatrix, which is taken from some columns and some rows of a matrix.

\begin{defn}For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column indices of $C$ respectively,  We use $C[\alpha|\beta]$ to denote the submatrix of $C$ with size $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$ and $j\in\beta$,
\begin{comment}
$C[\alpha|\beta):=C[\alpha|\overline{\beta}],$ where $\overline{\beta}$ is the complement of $\beta$ in the set of column indices, and
similarly, for the definitions of $C(\alpha|\beta]$ and $C(\alpha|\beta).$
 For $\ell\in \mathbb{N},$ $[\ell]:=\{1, 2, \ldots, \ell\},$ symbol $-$ is the complete set of indices, and we use  $i$ to denote the singleton subset $\{i\}$ to reduce the double use of parentheses. For example of the $n\times n$ matrix $C$,
 $C[-|n)=C[[n]|[n-1]]$ is the $n\times (n-1)$ submatrix of $C$ obtained by deleting the last column of $C$.

    The bracket [] and parentheses () can be used together is the notation of sub-matrix, such as $C[k|e)$ or $C(k|e]$.
\end{comment}

\end{defn}

\begin{thm}
        If $C$ is a nonnegative square matrix, then spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
\end{thm}

The following theorem is from \cite{chang}.

\begin{thm}
 Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]    $PCQ\leq PC'Q$;
\item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
\item[(iii)] there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector $v^TP$; and
\item[(iv)] $v^TPQu>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
    Moreover, $\lambda=\lambda'$
if and only if
    \begin{equation*}
        \label{e3}
(PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
\end{equation*}
\end{thm}

\begin{proof}
            Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
        \begin{equation}
            \label{e1}
            PCQu\leq PC'Qu=\lambda'PQu.
        \end{equation}
        Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
        \begin{equation}
            \label{e2}
            \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
        \end{equation}
        Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.

        Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.  Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
            $\lambda=\lambda'$ by (\ref{e2}). \qed

 \end{proof}

 \newpage
\begin{thebibliography}{20}
\normalsize
\addcontentsline{toc}{chapter}{Bibliography}

\bibitem{chang}
Yen-Jen Chenga, Chih-wen Wenga, A matrix realization of spectral bounds
of the spectral radius of a nonnegative matrix, (journal),....

\bibitem{catalan}
\newblock{James Haglund, The $q$,$t$-Catalan Numbers and the Space of Diagonal Harmonics: With an Appendix on the Combinatorics of Macdonald Polynomials},
\newblock{\it University Lectures Series}, vol. 41, 2008

\bibitem{combinatorics}
\newblock{J.H. van Lint and R.M. Wilson, A Course in Combinatorics, second edition},
\newblock{\it} Cambridge University Press, New York, 2001.

\bibitem{euler}
\newblock{H. W. Gould, Euler's formula nth differences of powers},
\newblock{\it The American Mathematical Monthly }, vol. 85, No. 6, 450-467,1978

\bibitem{rook}
\newblock{Feryal Alayomt and Nicholas Krzywonos, Rook polynomials in three and higher dimensions},
\newblock{\it }, 2009

\bibitem{brualdi}
\newblock{Richard A. Brualdi, Introductory Combinatorics, fifth edition},
\newblock{\it },  Prentice Hall, New Jersey, 2009.

\bibitem{qanalogue}
\newblock{Bruce E. Sagan, Congruence Properties of $q$-Analogs},
\newblock{\it Advances in Mathematics}, 95, 127-143,1992

\bibitem{lagrange}
\newblock{Eric W. Weisstein, Lagrange Interpolating Polynomial}, \newblock{MathWorld}

\bibitem{9}
\newblock{郭子翔,一個新恆等式的發現與研究}, preprint.

\end{thebibliography}

\end{document}

### 2020-09-05 spectral radius of matrix new method/thesis/our_result.tex
first commit

\documentclass[12pt]{report}%{article}

\topmargin 0pt

\topmargin=-1.5cm
\oddsidemargin=0.7cm
\textheight=23.5cm
\textwidth=15cm
\setlength{\baselineskip}{24pt}
\renewcommand{\baselinestretch}{1.5} %行距

\usepackage{fontspec}   %加這個就可以設定字體
\usepackage{xeCJK}       %讓中英文字體分開設置
%\usepackage{times}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ulem}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{tabularx,array}
\usepackage{pgf,tikz}
\usepackage{blkarray} %line 80-92 Q formula matrix index
%\usepackage{colortbl}

\usetikzlibrary{arrows}
\setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
\XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
\XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
\title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
\author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
\date{} %不要日期

\def\UrlFont{\rm}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[chapter]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{remark}[thm]{Remark}
\newtheorem{eg}[thm]{Example}
\newtheorem{conj}[thm]{Conjecture}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{ex}[thm]{Exercise}
\newtheorem{prob}[thm]{Problem}
\newtheorem{exam}[thm]{Example}
\newtheorem{nota}[thm]{Notation}
\newtheorem{rem}[thm]{Remark}
\newtheorem{ques}[thm]{Question}
\newtheorem{pof}[thm]{Proof.}

%\renewcommand {\refname} {Bibliography}

\begin{document}

\chapter{Our result}
We will prove the main Theorems introduced in the introduction. First, we need some natations.
 Throughout fix $k \in [n-1] := \{1,2,...,n-1\}$. Let $E_{kn}$ denote the $n\times n$ binary matrix with an unique $1$ appearing in the  position $(k,n)$. We will apply the Theorem 1.7 with $P=I$ and

\begin{equation}
Q=I+E_{kn}=\begin{blockarray}{cccccc}
%a & b & c & d & e \\
 &  &  & &  \\
\begin{block}{(ccccc)c}
	\label{Q1}
  1 &   &   &   &   &  \\
    & 1 &   &   &   &  \\
    &   & \ddots &   & 1 & k \\
    &   &   & 1 &   &  \\
  0 &   &   &   & 1 &  \\
\end{block}
\end{blockarray}
\end{equation}

\begin{defn}\label{v_rooted}
 ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

The following Lemma is immediate from the above definition.
\bigskip

\begin{lem}
If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}
\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
\qed
\end{lem}

\begin{thm} \label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item[(ii)] there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
\item[(a)]    $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
\item[(b)]  $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
\item[(c)]   $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
\end{enumerate} \qed

\end{thm}

\begin{proof}
The proof is based on Theorem 1.7 with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1} )  $. The assumption (i) $PCQ\leq PC'Q$ of Theorem 1.7 holds by the condition (i) of this theorem. Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and Lemma 2.2(i). Hence the assumption (ii) of Theorem 1.7 holds. The assumptions (iii) and (iv) of Theorem 1.7 clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and $v'= Qu$  Hence $\lambda \leq \lambda' $ by the conclusion of Theorem 1.7. Moreover $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to conditions (a),(b),(c) of this theorem. 
\end{proof}

We are interested in the matrices $C'$ that have $k$-rooted eigenvectors.
Motivated by the condition (i) of theorem 2.3, we provide the following two definitions.

\begin{defn}
For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$.
\end{defn}

Note that the last column of $C'Q$ is the $(k, n)$-{\it sum} vector of $C'$

\begin{defn}\label{m_rooted}
A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-{\it sum} vector are all $k$-rooted except the last column of $C'$.
\end{defn}

The following theorem shows that a $k$-rooted matrix has a $k$-rooted eigenvector.

\begin{thm} \label{lma_m_rooted}
Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
    \begin{enumerate}
        \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
        \item[(ii)]Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
        \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
    \end{enumerate}
\end{thm}

\begin{proof}
(i) is immediate from Definition~\ref{m_rooted} and the observation that
$$Q^{-1}=I-E_{kn}=\begin{pmatrix}
1 &  & & &  & 0 \\
 & 1 &  &      &  &  \\
 &  & \ddots & &  & -1 \\
 &  &        & &  &  \\
  &  & & & 1 &  \\
0 &  & & &  & 1 \\
\end{pmatrix},$$
and $Q^{-1}C'Q$ is
$$\begin{pmatrix}
c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
\vdots \\
c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
\vdots              & \vdots & \ddots              & \vdots & \vdots \\
c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
\end{pmatrix}.
$$

(ii)
By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted.
Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
$Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$
$C'Qu=\rho(C')Qu$.

(iii)
Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.

\end{proof}

\begin{lem}\label{l_diag}
If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
\end{lem}

\begin{thm}
Let $C$ be an $n\times n$ nonnegative Tmatrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
such that $c'_{ij}\geq c_{ij}$ and $c'_{kj}\geq c'_{nj}>0$, and choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, and
$r'_k \geq r'_n$. Moreover choose $c'_{in}:=r'_i-c'_{ik}$. Then $\rho(C)\leq \rho(C')$, when $C'=(c'_{ij})$.
\end{thm}

\begin{proof}

The assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on (\ref{lma_m_rooted}) ; by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has a $k$-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and then $\rho(C') \geq \rho(C)$  \qed

\noindent{\bf Example}
For the following $4\times 4$ matrix
$$C=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 0 & 1\\
1 & 1 & 0 & 1\\
1 & 1 & 1 & 0
\end{pmatrix},$$
we choose
$$C'=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 1 &  0\\
1 & 1 & 0 & 1\\
1 & 1 & 1 & 0
\end{pmatrix}.$$
Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ \ref{thm_main},   
Then
$\rho(C)\leq \rho(C')$ by Theorem 4.8.

{\bf Counterexample}
For the following two $4\times 4$ matrices
$$C=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 0 & 1\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 0
\end{pmatrix},\quad C'=\begin{pmatrix}
0 & 0 & 1 & 1\\
1 & 0 & 1 &  0\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 0
\end{pmatrix},$$
specify $n$=4, $k$=3 in $Q = I +E_{kn} = I + E_{34}$  
$$CQ=\begin{pmatrix}
0 & 0 & 1 & 2\\
1 & 0 & 0 & 1\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 1
\end{pmatrix},\quad C'Q=\begin{pmatrix}
0 & 0 & 1 & 2\\
1 & 0 & 1 & 1\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 1
\end{pmatrix},$$

we have $CQ\leq C'Q$, but
$\rho(C)=2.234\not\leq 2.148= \rho(C')$.
This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.

\end{proof}

\end{document}

### 2020-09-05 spectral radius of matrix new method/thesis/preliminiaries.tex
first commit

--- 2020-09-05 spectral radius of matrix new method/thesis/1130out.tex
@@
 \setlength{\baselineskip}{24pt}
-\renewcommand{\baselinestretch}{1.5} %行
+\renewcommand{\baselinestretch}{1.5} %行距
 
@@
 %\usepackage{times}
+\usepackage{comment}
 \usepackage{amssymb}
@@
 \begin{defn}
-    Let $C$ be an $n \times n$ real matrix, and $u \in \mathbb{R}^n$ be a column vector.
-The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ of C corresponding to an $\it{eigenvector}$ if $Cu = \lambda u$
+    Let $C$ be an $n \times n$ real matrix, and $u \in \mathbb{R}^n$ be a nonzero column vector.
+The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
 
@@
 
-When $C$ is a real square matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$ is defined by
+When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$ is defined by
 $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
@@
 \begin{defn}
-Given an undirected graph G, the $\textit{spectral radius}$ of G is the spectral radius of the adjacency matrix A.
+Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral radius of the adjacency matrix of G.
 \end{defn}
@@
 \begin{defn}For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column indices of $C$ respectively,  We use $C[\alpha|\beta]$ to denote the submatrix of $C$ with size $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$ and $j\in\beta$,
+
+The following theorem is a part of Perron-Frobenius theorem \cite{'content'}.
 \begin{comment}
@@
 
+%Peron Frobius theorem
 \begin{thm}
@@
 
-The following theorem is from \cite{chang}.
+The following theorem is from \cite{chang}. For completeness, we also provide the proof.
 
@@
 if and only if
-    \begin{equation*}
-        \label{e3}
+    \begin{equation}
+        \label{pre0}
 (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
-\end{equation*}
+\end{equation}
 \end{thm}
@@
 \begin{proof}
-            Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
+            Multiplying the nonnegative vector $u$ in assumption (ii), where $Qu$ is eigenvector of $C'$,  to the right of both terms of  (i),
         \begin{equation}
-            \label{e1}
+            \label{pre1}
             PCQu\leq PC'Qu=\lambda'PQu.
         \end{equation}
-        Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
+        Multiplying the nonnegative vector $v^T$  in assumption (iii) , where $v^TP$ is left eigenvector of $C$ for $\lambda$,to the left of all terms  in (\ref{pre1}), we have
         \begin{equation}
-            \label{e2}
+            \label{pre2}
             \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
@@
 
-        Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.
+        Assume that $\lambda=\lambda'$, so the inequality in (\ref{pre2}) is an equality.
 Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
-         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
-            $\lambda=\lambda'$ by (\ref{e2}). \qed
+         Conversely, (\ref{pre0}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
+            $\lambda=\lambda'$ by (\ref{pre2}).
 
@@
 
- \newpage
-\begin{thebibliography}{20}
-\normalsize
-\addcontentsline{toc}{chapter}{Bibliography}
-
-\bibitem{chang}
-Yen-Jen Chenga, Chih-wen Wenga, A matrix realization of spectral bounds
-of the spectral radius of a nonnegative matrix, (journal),....
-
-\bibitem{catalan}
-\newblock{James Haglund, The $q$,$t$-Catalan Numbers and the Space of Diagonal Harmonics: With an Appendix on the Combinatorics of Macdonald Polynomials},
-\newblock{\it University Lectures Series}, vol. 41, 2008
-
-\bibitem{combinatorics}
-\newblock{J.H. van Lint and R.M. Wilson, A Course in Combinatorics, second edition},
-\newblock{\it} Cambridge University Press, New York, 2001.
-
-\bibitem{euler}
-\newblock{H. W. Gould, Euler's formula nth differences of powers},
-\newblock{\it The American Mathematical Monthly }, vol. 85, No. 6, 450-467,1978
-
-\bibitem{rook}
-\newblock{Feryal Alayomt and Nicholas Krzywonos, Rook polynomials in three and higher dimensions},
-\newblock{\it }, 2009
-
-\bibitem{brualdi}
-\newblock{Richard A. Brualdi, Introductory Combinatorics, fifth edition},
-\newblock{\it },  Prentice Hall, New Jersey, 2009.
-
-\bibitem{qanalogue}
-\newblock{Bruce E. Sagan, Congruence Properties of $q$-Analogs},
-\newblock{\it Advances in Mathematics}, 95, 127-143,1992
-
-\bibitem{lagrange}
-\newblock{Eric W. Weisstein, Lagrange Interpolating Polynomial}, \newblock{MathWorld}
-
-\bibitem{9}
-\newblock{郭子翔,一個新恆等式的發現與研究}, preprint.
-
-\end{thebibliography}
-
 \end{document}

### 2020-09-05 spectral radius of matrix new method/thesis/thesis_form.tex
first commit

--- 2020-09-05 spectral radius of matrix new method/paper/article_struc1112.tex
@@
-\documentclass[12pt]{article}
-%\usetheme{Warsaw}
-\usepackage{times}  % fonts are up to you
-\usepackage{amssymb, amsmath, mathrsfs,amsthm}
-\usepackage{multicol}
-\usepackage{bm}
+\documentclass[12pt]{report}%{article}
+
+\topmargin 0pt
+
+\topmargin=-1.5cm
+\oddsidemargin=0.7cm
+\textheight=23.5cm
+\textwidth=15cm
+\setlength{\baselineskip}{24pt}
+\renewcommand{\baselinestretch}{1.5} %行距
+
+\usepackage{fontspec}   %加這個就可以設定字體
+\usepackage{xeCJK}       %讓中英文字體分開設置
+%\usepackage{times}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{ulem}
+\usepackage{amsfonts}
+\usepackage{mathrsfs}
+\usepackage{tabularx,array}
+\usepackage{pgf,tikz}
+%\usepackage{colortbl}
 
-\usepackage{fontspec}
-\usepackage{xeCJK}
-%\setCJKmainfont{微軟正黑體}
-\setCJKmainfont{simsun.ttf}
-\setCJKsansfont{simhei.ttf}
-\setCJKmonofont{simfang.ttf}
-\XeTeXlinebreaklocale "zh"
-\XeTeXlinebreakskip = 0pt plus 1pt
+\usetikzlibrary{arrows}
+\setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
+\XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
+\XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
+\title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
+\author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
+\date{} %不要日期
 
-\begin{document}
+\def\UrlFont{\rm}
 
-% THEOREMS ---------------------------------------------------------------
 \theoremstyle{plain}
-% block中的字會變成數學體, 斜體字
-\newtheorem{thm}{Theorem}[section]
+\newtheorem{thm}{Theorem}[chapter]
 \newtheorem{cor}[thm]{Corollary}
@@
 \newtheorem{remark}[thm]{Remark}
-\newtheorem{pf}[thm]{Proof}
-
 \newtheorem{eg}[thm]{Example}
@@
 \theoremstyle{definition}
-% block中的字是正常字體
+\newtheorem{defn}[thm]{Definition}
 \newtheorem{ex}[thm]{Exercise}
-\newtheorem{defn}[thm]{Definition}
 \newtheorem{prob}[thm]{Problem}
 \newtheorem{exam}[thm]{Example}
+\newtheorem{nota}[thm]{Notation}
 \newtheorem{rem}[thm]{Remark}
+\newtheorem{ques}[thm]{Question}
+\newtheorem{pof}[thm]{Proof.}
 
-\newtheorem{algo}[thm]{Algorithm}
+%\renewcommand {\refname} {Bibliography}
 
-\title{TBA}
-\author{Ke-Han Chen\\} % 作者
-%\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
-\date{October 18th, 2018}
-\date{\today} % 日期
+\begin{document}
+%封面
 
-\maketitle
-\begin{abstract}
-    This is my abstract.
-\end{abstract}
+\thispagestyle{empty}
+\begin{center}
+{ \Huge 國~~~~立~~~~交~~~~通~~~~大~~~~學}~\\~\\
 
-\section{Preliminaries}
+\bigskip
+
+{ \Huge 應~用~數~學~系}~\\~\\
+
+\bigskip
+
+{ \Huge 碩~~士~~論~~文}~\\~\\
+
+\bigskip \bigskip\bigskip\bigskip\bigskip\bigskip
+
+{ \Huge TBA}~\\~\\
+
+\bigskip
+
+{ \Huge 待輸入}~\\~\\
+~\\~\\~\\~\\~\\
+\bigskip \bigskip\bigskip\bigskip\bigskip\bigskip
+\bigskip \bigskip\bigskip\bigskip\bigskip\bigskip
+\bigskip\bigskip\bigskip
+
+{ \Large
+\begin{tabular}{rcl}
+研究生&：&XXX\\
+指導教授&：&翁志文~教授
+\end{tabular} }
+
+\bigskip\bigskip
+{ \Large 中~~華~~民~~國~~一~~百~~零~~八~~年~~一~~月 }
+\large
+\end{center}
+\pagebreak
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\renewcommand{\baselinestretch}{2} %行距
+\thispagestyle{empty}
+\begin{center}
+{
+\Large
+TBA\\
+待輸入 \\~\\
+\begin{tabular}{lccr}
+Student: XXX  &&~~~& Advisor: Chih-Wen Weng\\
+研究生:陳科翰　 &&~~~& 指導教授：翁志文~教授
+\end{tabular}
+}~\\
+
+\bigskip
+
+\renewcommand{\baselinestretch}{1} %行距
+
+{ \LARGE 國~~~~立~~~~交~~~~通~~~~大~~~~學}\\~\\
+{ \LARGE 應~用~數~學~系}\\~\\
+{ \LARGE 碩~~士~~論~~文}\\~\\~\\~\\~\\
+\renewcommand{\baselinestretch}{1} %行距
+{ \large A Thesis
+
+Submitted to Department of Applied Mathematics
+
+College of Science
+
+National Chiao Tung University
+
+in Partial Fulfillment of Requirements
+
+for the Degree of Master
+
+in Applied Mathematics
+\bigskip \medskip
+
+January 2019
+
+Hsinchu, Taiwan, Republic of China \bigskip \medskip
+
+ 中~~華~~民~~國~~一~~百~~零~~八~~年~~一~~月 }
+\end{center}
+\pagebreak
+%中文摘要
+\pagenumbering{roman}
+\begin{center}
+{  \LARGE
+待輸入
+\bigskip\bigskip\bigskip
+
+研究生：陳科翰  ~~~~~~~~~~ 指導教授：翁志文~教授 \\
+國立交通大學  \\
+\bigskip
+應用數學系
+\bigskip\bigskip\bigskip\bigskip
+} \\~\\~\\~\\
+\addcontentsline{toc}{chapter}{Abstract (in Chinese)}
+{\large 摘~要}
+\end{center}
+ \bigskip
+
+待輸入\\
+\bigskip
+
+\noindent 關鍵詞：待輸入。
+\pagebreak
+
+%英文摘要
+\begin{center}{\LARGE
+TBA
+\bigskip\bigskip\bigskip}
+
+{ \large
+Student: XXX  ~~~~~ Advisor: Chih-Wen Weng \\
+\Large
+
+Department ~of~ Applied ~Mathematics
+\bigskip
+
+National~ Chiao ~Tung~ University
+\bigskip\bigskip\bigskip\bigskip}\\
+{\large Abstract}
+\end{center}
+
+%\begin{abstract}
+\addcontentsline{toc}{chapter}{Abstract (in English)}
+
+TBA
+\bigskip
+
+\noindent {\bf Keywords}: TBA
+%\end{abstract}
+\pagebreak
+\renewcommand{\baselinestretch}{1.2}
+% 目錄
+\large
+\tableofcontents
+
+\pagebreak
+% Introduction
+
+\chapter{Introduction}
+\normalsize
+\pagenumbering{arabic}
+
+\chapter{Preliminaries}
 
@@
 \end{defn}
+
 \begin{defn}
@@
 \end{defn}
+
     We introduce a notation of sub-matrix, which is taken from some columns and some rows of a matrix.
+
     \begin{defn}We use $C[\alpha|\beta]$ to denote the sub-matrix of rows $\alpha$ of $C$ and columns $\beta$ of $C$ and $C(\alpha|\beta)$ is the sub-matrix of rows $[n]$ - $\alpha$ of $C$ and columns $[n] - \beta$ of $C$.
@@
 
-\thm
+\begin{thm}
         If $C$ is nonnegative square matrix, then the following holds. \\
         The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
+\end{thm}
 
@@
 
-\begin{pf}
+\begin{proof}
             Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
@@
 
- \end{pf}
+ \end{proof}
+
+\chapter{Our result}
 
@@
 
-\section{Our first result}
-
 \begin{thm} \label{thm_main}
@@
 
-{\bf $k$-rooted matrix}
-
-\begin{defn}[(k,n)-sum]
+\begin{defn}
 For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
@@
 
-\begin{defn}[k-rooted matrix]\label{m_rooted}
+\begin{defn}\label{m_rooted}
 A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-sum vector are all $k$-rooted except the last column of $C'$.
@@
     \end{enumerate}
+\end{thm}
 
-\begin{pf}
-\subsection{}
+\begin{proof}
 (i) is immediate from Definition~\ref{m_rooted} and the observation that
@@
 
-\subsection{(ii)}
-
+(ii)
 By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted.
@@
 
-\subsection{(iii)}
-
+(iii)
 Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.
 
-\end{pf}
-\end{thm}
+\end{proof}
 
@@
 
-\section{Conclusion}
+\chapter{Conclusion}
 
@@
 
+\newpage
+\begin{thebibliography}{20}
+\normalsize
+\addcontentsline{toc}{chapter}{Bibliography}
+\bibitem{catalan}
+\newblock{James Haglund, The $q$,$t$-Catalan Numbers and the Space of Diagonal Harmonics: With an Appendix on the Combinatorics of Macdonald Polynomials},
+\newblock{\it University Lectures Series}, vol. 41, 2008
+
+\bibitem{combinatorics}
+\newblock{J.H. van Lint and R.M. Wilson, A Course in Combinatorics, second edition},
+\newblock{\it} Cambridge University Press, New York, 2001.
+
+\bibitem{euler}
+\newblock{H. W. Gould, Euler's formula nth differences of powers},
+\newblock{\it The American Mathematical Monthly }, vol. 85, No. 6, 450-467,1978
+
+\bibitem{rook}
+\newblock{Feryal Alayomt and Nicholas Krzywonos, Rook polynomials in three and higher dimensions},
+\newblock{\it }, 2009
+
+\bibitem{brualdi}
+\newblock{Richard A. Brualdi, Introductory Combinatorics, fifth edition},
+\newblock{\it },  Prentice Hall, New Jersey, 2009.
+
+\bibitem{qanalogue}
+\newblock{Bruce E. Sagan, Congruence Properties of $q$-Analogs},
+\newblock{\it Advances in Mathematics}, 95, 127-143,1992
+
+\bibitem{lagrange}
+\newblock{Eric W. Weisstein, Lagrange Interpolating Polynomial}, \newblock{MathWorld}
+
+\bibitem{9}
+\newblock{郭子翔,一個新恆等式的發現與研究}, preprint.
+
+\end{thebibliography}
+
 \end{document}

### 2020-09-05 Triangulation_2020_7_24.tex
0905 no_revision

\documentclass{beamer}

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subfigure,pgf,tikz}
\usetikzlibrary{arrows}
\usepackage[misc]{ifsym}
\usepackage{mathrsfs}
\usepackage{epstopdf}
\usepackage{multicol}

\usepackage{graphicx,xcolor,subfigure}

\usepackage{xeCJK}

\setCJKmainfont{微軟正黑體}

\XeTeXlinebreaklocale "zh"

\XeTeXlinebreakskip = 0pt plus 1pt

\usetheme{Boadilla}

\setbeamertemplate{footlines}[page number]{}
\setbeamertemplate{navigation symbols}

\title[]{Hamiltonicity in locally $1$-tough graphs}

\author[]{ }

\date[]{}

\setbeamertemplate{theorems}[numbered]

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}

\theoremstyle{definition}
\newtheorem{ex}[thm]{Exercise}
\newtheorem{defn}[thm]{Definition}
\newtheorem{prob}[thm]{Problem}
\newtheorem{exam}[thm]{Example}
\newtheorem{rem}[thm]{Remark}
\newtheorem{ques}[thm]{Question}
\newtheorem{conj}[thm]{Conjecture}

\begin{document}

\begin{frame}{\bf Hamiltonian graphs}

A graph is \textcolor{red}{\bf Hamiltonian} if it contains a spanning cycle.
\bigskip

\begin{center}
\begin{tikzpicture}[scale=2]

\foreach \i in {0,1,...,2}
{
\coordinate (v\i) at ({sin(2*\i*pi /3 r)},{cos(2*\i*pi /3 r)}) ;
}

\coordinate (v3) at (0,1/4);
\coordinate (v4) at (0,-1/4);

\draw[very thick] (v0)--(v3)--(v2)--(v1)--(v4);
\draw[very thick,color=red] (v0)--(v1)--(v3)--(v4)--(v2)--(v0);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\end{tikzpicture}
\bigskip

The red edges form a spanning cycle of the above graph
\end{center}
\end{frame}

\begin{frame}{\bf Definitions}

\begin{enumerate}
\item A \textcolor{red}{\bf triangulated graph} is a planar graph such that any edge is in a cycle and any face is a  triangle.
\item A \textcolor{red}{\bf chordal graph} is a graph such that every cycle of length at least $4$ contains a \textcolor{red}{\bf chord}, i.e., an edge connecting two nonadjacent vertices of the cycle.
\end{enumerate}

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,2}
{
\coordinate (v\i) at ({sin(2*\i*pi /3 r)},{cos(2*\i*pi /3 r)}) ;
}

\coordinate (v3) at (0,1/4);
\coordinate (v4) at (0,-1/4);

\draw[very thick] (v0)--(v3)--(v2)--(v1)--(v4);
\draw[very thick,color=red] (v0)--(v1)--(v3)--(v4)--(v2)--(v0);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}
\begin{rem} 
\begin{enumerate}
\item A triangulated of order at least $4$ contains $3+3(n-3)=3n-6$ edges and $2n-4$ faces.
\item If $C$ is a Hamiltonian cycle of a triangulated planar graph $T$ then there are $n-2$ faces and $n-3$ edges inside $C$. 
\end{enumerate}
\end{rem}
\end{frame}

\begin{frame}{\bf Problem}

Can every edge of a triangulated graph be drawn as an edge of an outer face.
\bigskip

{\bf Answer:} Yes

\bigskip

\begin{center}
\begin{tikzpicture}[scale=2]

\foreach \i in {0,1,...,2}
{
\coordinate (v\i) at ({sin(2*\i*pi /3 r)},{cos(2*\i*pi /3 r)}) ;
}

\coordinate (v3) at (0,1/4);
\coordinate (v4) at (0,-1/4);

\draw[very thick] (v0)--(v3)--(v2)--(v1)--(v4);
\draw[very thick,color=red] (v0)--(v1)--(v3)--(v4)--(v2)--(v0);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[] (-1/5, -1/8) circle (.02);
\end{tikzpicture}
\end{center}
\bigskip

Plane is homeomorphic to the surface obtained from a sphere deleting a point.
\end{frame}

\begin{frame}{\bf A $4$-regular triangulated graph}

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,2}
{
\coordinate (v\i) at ({2*sin(2*\i*pi /3 r)},{2*cos(2*\i*pi /3 r)}) ;
}

\foreach \i in {3,4,5}
{
\coordinate (v\i) at ({0.6*sin(2*(2*\i-5)*pi /6 r)},{0.6*cos(2*(2*\i-5)*pi /6 r)}) ;
}

\draw[very thick]    (v0)--(v1)--(v2)--(v0) (v3)--(v4)--(v5)--(v3) (v0)--(v3)--(v1)--(v4)--(v2)--(v5)--(v0);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\end{tikzpicture}
\end{center}

\end{frame}

\begin{frame}{\bf A triangulated graph which is not a chordal graph}

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,2}
{
\coordinate (v\i) at ({2*sin(2*\i*pi /3 r)},{2*cos(2*\i*pi /3 r)}) ;
}

\foreach \i in {3,4,5}
{
\coordinate (v\i) at ({0.6*sin(2*(2*\i-5)*pi /6 r)},{0.6*cos(2*(2*\i-5)*pi /6 r)}) ;
}

\draw[very thick]    (v0)--(v1)--(v4) (v2)--(v0) (v3)--(v4)--(v5)--(v0)--(v3)--(v4)--(v2) ;
\draw[very thick, color=red] (v3)--(v1)--(v2)--(v5)--(v3);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\end{tikzpicture}

There is no chord in the red cycle.
\end{center}
\end{frame}

\begin{frame}{\bf More definitions}
\begin{enumerate}
\item A \textcolor{red}{\bf weakly  pancyclic graph} is a graph which contains cycles of every length between the girth and the circumference.
\item A graph is \textcolor{red}{\bf $t$-tough}  if for every integer $k>1$, the graph cannot be split into $k$ components by removal of fewer than $tk$ vertices
\item The \textcolor{red}{\bf toughness} a non-complete graph $G$ is the maximum $t$ such that $G$ is $t$-tough. The toughness of a complete graph is $\infty$.
\end{enumerate}

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,2}
{
\coordinate (v\i) at ({sin(2*\i*pi /3 r)},{cos(2*\i*pi /3 r)}) ;
}

\coordinate (v3) at (0,1/4);
\coordinate (v4) at (0,-1/4);

\draw[very thick] (v0)--(v3)--(v2)--(v1)--(v4);
\draw[very thick,color=red] (v0)--(v1)--(v3)--(v4)--(v2)--(v0);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\end{tikzpicture}
\end{center}

\begin{rem}
A $t$-tough graph with $t>0$ is connected and  a Hamiltonian graph is $1$-tough.
\end{rem}
\end{frame}

\begin{frame}{\bf A triangulated graph which is not weakly pancyclic}

To be filled later. 
\end{frame}

\begin{frame}{\bf A long standing conjecture}

There is a positive constant $t$ such that every $t$-tough graph is Hamiltonian.
\bigskip

V. Chv\'{a}tal, Tough graphs and hamiltonian circuits, Discrete Math. 5 (1973), 215-228.

\end{frame}

\begin{frame}{\bf Locally property $P$}

Let $P$ be a property on graphs.
A graph $G$ has \textcolor{red}{\bf local $P$} if $G_1(v)$ has property $P$ for every vertex $v$ in $G$.
\bigskip

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,2}
{
\coordinate (v\i) at ({sin(2*\i*pi /3 r)},{cos(2*\i*pi /3 r)}) ;
}

\coordinate (v3) at (0,1/4);
\coordinate (v4) at (0,-1/4);

\draw[very thick] (v1)--(v0)--(v3)--(v2)--(v1)--(v4)--(v2)--(v0) (v3)--(v4) ;
\draw[very thick,color=red] (v1)--(v3)--(v2)--(v1);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill, color=green] (v4) circle (.1);
\end{tikzpicture}
\end{center}
\bigskip

\begin{rem}
A triangulated graph of order at least $4$ is locally Hamiltonian.
\end{rem}
\end{frame}

\begin{frame}{\bf A $1$-tough and locally connected planar graph}
\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,7}
{
\coordinate (v\i) at ({sin(2*\i*pi /8 r)},{cos(2*\i*pi /8 r)}) ;
}

\draw[very thick] (v0)--(v1)--(v2)--(v3)--(v4)--(v5)--(v6)--(v7)--(v0)--(v2)--(v4)--(v6)--(v0) (v1)--(v3)--(v5)--(v7)--(v1);
\draw[very thick,color=red] (v6)--(v7)--(v1)--(v2);
\draw[very thick,fill, color=green] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\draw[very thick,fill] (v6) circle (.1);
\draw[very thick,fill] (v7) circle (.1);
\end{tikzpicture}
\end{center}
\bigskip

The planar graph $DL(8;1,2)$ is $1$-tough and locally connected.
\bigskip

\begin{rem}
$DL(n;1, 2)$ is a planar graph, where $n\geq 4$ and $n$ is even.
\end{rem}

\begin{rem}
Every planar graph can be drawn by using straight lines as edges.
\end{rem}
\end{frame}

\begin{frame}{\bf Question}

Is a triangulated graph $1$-tough?
\bigskip

The answer is `no' as shown in the next page.

\end{frame}

\begin{frame}{\bf A triangulated graph which is not $1$-tough}

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,2}
{
\coordinate (v\i) at ({4*sin(2*\i*pi /3 r)},{4
*cos(2*\i*pi /3 r)}) ;
}

\foreach \i in {3,4,5}
{
\coordinate (v\i) at ({sin(2*(2*\i-5)*pi /6 r)},{cos(2*(2*\i-5)*pi /6 r)}) ;
}

\coordinate (v6) at (0,0);
\coordinate (v7) at (1/2,-2/3);
\coordinate (v8) at (0,-3/2);
\coordinate (v9) at (-1/2,-2/3);
\coordinate (v10) at (-1/3,2/3);
\coordinate (v11) at (-1,-1/4);
\coordinate (v12) at (-1,1);

\draw[very thick] (v3)--(v0)--(v6)--(v1)--(v2)--(v0)   (v8)--(v2)--(v6)--(v5)--(v11)  (v7)--(v4)--(v1)--(v3) (v0)--(v1)--(v3)--(v6)--(v4)--(v2)--(v5)--(v0)
(v4)--(v8)--(v1)--(v7)--(v6)  (v4)--(v9)--(v6)  (v9)--(v2)--(v12) (v6)--(v10)--(v0)--(v12)--(v5)  (v10)--(v5)--(v11)--(v6) (v11)--(v2);

\draw[very thick,fill, color=red] (v0) circle (.1);
\draw[very thick,fill,  color=red] (v1) circle (.1);
\draw[very thick,fill, color=red] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill, color=red] (v4) circle (.1);
\draw[very thick,fill, color=red] (v5) circle (.1);
\draw[very thick,fill, color=red] (v6) circle (.1);
\draw[very thick,fill] (v7) circle (.1);
\draw[very thick,fill] (v8) circle (.1);
\draw[very thick,fill] (v9) circle (.1);
\draw[very thick,fill] (v10) circle (.1);
\draw[very thick,fill] (v11) circle (.1);
\draw[very thick,fill] (v12) circle (.1);
\end{tikzpicture}
\bigskip

Deleting the $6$ red vertices will yield $7$ components.

\end{center}

\end{frame}

\begin{frame}{\bf Lemma}
For a vertex $u$ and  a cut set $S$ of $G$ if $c(G-S)> |S|$ and $G-u$ is $1$-tough
then $u\not\in S$ and $G_1(u)\subseteq S$.
\bigskip

\begin{proof}
If $u\in S$ then $G-u$ has toughness at most $(|S|-1)/c(G-S)<1$, a contradiction;
if $u\not\in S$ then $G-u$ being $1$-tough and $|S|/c(G-S)<1$
implies that there is a single element component $\{u\}$ in $G-S$, so $G_1(u)\subseteq S$.
\end{proof}
\bigskip

T. Nishizeki, A $1$-tough nonhamiltonian maximal planar graph, Discrete Math. 30(1980), 305-307.
\end{frame}

\begin{frame}{\bf Proposition} 
Let $G$ be a connected graph such that  $G-u$ is Hamiltonian for every vertex in $G$.  Then $G$ is $1$-tough. 
\begin{proof}
Suppose $G$ is not $1$-tough and pick a cut set $S$ with $c(G-S)> |S|$. 
As $G-u$  is $1$-tough, $u\not\in S$ by previous lemma. Hence $S=\emptyset,$ a contradiction. 
\end{proof}

\end{frame}

\begin{frame}{\bf Question}

Is every $1$-tough and  locally connected graph Hamiltonian?

\end{frame}

\begin{frame}{\bf A $1$-tough, locally connected, non-Hamiltonian planar graph}
\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,6}
{
\coordinate (v\i) at ({sin(2*\i*pi /7 r)},{cos(2*\i*pi /7 r)}) ;
}

\draw[very thick] (v0)--(v1)--(v2)--(v3)--(v4)--(v5)--(v0)--(v3) (v1)--(v5)  (v3)--(v6)--(v0)  (v5)--(v3)--(v1) ;
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill, color=red] (v2) circle (.1);
\draw[very thick,fill, color=green] (v3) circle (.1);
\draw[very thick,fill, color=red] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\draw[very thick,fill, color=red] (v6) circle (.1);
\end{tikzpicture}
\end{center}

\bigskip

The graph is not Hamiltonian since the two edges of  each red vertex are in every Hamiltonian cycle.

\end{frame}

\begin{frame}{\bf A $1$-tough and locally Hamiltonian planar graph}

\begin{multicols}{2}

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,5}
{
\coordinate (v\i) at ({2*sin(2*\i*pi /6 r)},{2*cos(2*\i*pi /6 r)}) ;
}

\draw[very thick] (v4)--(v2)--(v0)--(v1)--(v2)--(v3)--(v4)--(v5)--(v0)--(v4) (v5)--(v3)--(v1)--(v5) ;
\draw[very thick,color=red] (v1)--(v2)--(v4)--(v5)--(v1);
\draw[very thick,fill,  color=green] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\end{tikzpicture}
\end{center}
\bigskip

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,2}
{
\coordinate (v\i) at ({2*sin(2*\i*pi /3 r)},{2*cos(2*\i*pi /3 r)}) ;
}

\foreach \i in {3,4,5}
{
\coordinate (v\i) at ({0.6*sin(2*(2*\i-5)*pi /6 r)},{0.6*cos(2*(2*\i-5)*pi /6 r)}) ;
}

\draw[very thick]    (v0)--(v1)--(v2)--(v0) (v3)--(v4)--(v5)--(v3) (v0)--(v3)--(v1)--(v4)--(v2)--(v5)--(v0);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\end{tikzpicture}
\end{center}

\end{multicols}

The planar  graph $DL(6;1,2)$ is $1$-tough and locally Hamiltonian, implying locally $1$-tough.
$DL(6;1,2)$ is  a triangulated planar graph.
\bigskip

\end{frame}

\begin{frame}{\bf Question}

Is every $1$-tough and locally $1$-tough graph locally Hamiltonian?
\bigskip

The answer is `no' in the following page.

\end{frame}

\begin{frame}{\bf A $1$-tough and locally $1$-tough graph \\
which is not locally Hamiltonian}
\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,7}
{
\coordinate (v\i) at ({sin(2*\i*pi /8 r)},{cos(2*\i*pi /8 r)}) ;
}

\draw[very thick] (v3)--(v0)--(v1)--(v2)--(v3)--(v4)--(v5)--(v6) (v7)--(v0)--(v2)  (v1)--(v5)--(v0)--(v4)  (v0)--(v6)--(v1)--(v7)--(v4) (v3)--(v5) (v3)--(v1)--(v4);
\draw[very thick,fill, color=green] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill, color=red] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\draw[very thick,fill, color=red] (v6) circle (.1);
\draw[very thick,fill, color=red] (v7) circle (.1);
\end{tikzpicture}
\end{center}
\bigskip

Deleting the green vertex of the above graph yields a $1$-tough non-Hamiltonian graph (The red vertices have degree $2$).

\bigskip

The above graph is not planar.

\end{frame}

\begin{frame}{\bf Question}

Is a $1$-tough and locally $1$-tough graph Hamiltonian.

\bigskip

The answer is `no' as shown in the next page.

\end{frame}

\begin{frame}{\bf A triangulated $1$-tough non-Hamiltonian graph }

\begin{center}
\begin{tikzpicture}[scale=0.5]

\foreach \i in {0,1,2}
{
\coordinate (v\i) at ({5*sin(2*\i*pi /3 r)},{5
*cos(2*\i*pi /3 r)}) ;
}

\foreach \i in {3,4,5,6,7,8}
{
\coordinate (v\i) at ({2*sin(2*(\i-3)*pi /6 r)},{2*cos(2*(\i-3)*pi /6 r)}) ;
}

\foreach \i in {9,10, 11}
{
\coordinate (v\i) at ({0.5*sin(2*(\i-9)*pi /3 r)},{0.5*cos(2*(\i-9)*pi /3 r)}) ;
}

\coordinate (v12) at (0,0);

\draw[very thick] (v4)--(v9)--(v8)--(v11)--(v6)--(v10)--(v4)--(v8)--(v6)--(v4)--(v0)--(v1)--(v2)--(v0)--(v3)--(v4)--(v5)--(v6)--(v7)--(v8)--(v3)
(v4)--(v1)--(v5) (v7)--(v2)--(v6)--(v1) (v2)--(v8) (v10)--(v12)--(v9) (v4)--(v12)--(v11) (v6)--(v12)--(v8)--(v0);

\draw[very thick,fill, color=red] (v0) circle (.1);
\draw[very thick,fill,  color=red] (v1) circle (.1);
\draw[very thick,fill, color=red] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill, color=red] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\draw[very thick,fill, color=red] (v6) circle (.1);
\draw[very thick,fill] (v7) circle (.1);
\draw[very thick,fill, color=red] (v8) circle (.1);
\draw[very thick,fill] (v9) circle (.1);
\draw[very thick,fill] (v10) circle (.1);
\draw[very thick,fill] (v11) circle (.1);
\draw[very thick,fill,, color=red] (v12) circle (.1);
\end{tikzpicture}

Seven separating triangles in the above graph.

\end{center}
\bigskip

Michal Tk\'{a}\v{c}, On the shortness exponent of l-tough, maximal planar graphs, Discrete Math. 154(1996), 321-328.
\end{frame}

\begin{frame}{\bf Plan}

We shall develop theory of  $1$-tough and locally $1$-tough graph.

\end{frame}

\begin{frame}{\bf Lemma}
If $G$ is $1$-tough and locally $1$-tough then $G-u$ is $1$-tough for every vertex $u$ in $G$.

\begin{proof}
Assume that $G-u$ is not $1$-tough. Then $G-u$ is split into $k\geq 2$ components by removal of some subset $S$ of vertices with $|S|<k$, where $u\not\in S$. Assume $\ell$ of these $k$ components intersecting with $G_1(u)$. If $\ell=1$ then by connecting $u$ to this unique component intersecting with $G_1(u)$, there are $k$ components after removal of $S$ from $G$, a contradiction to the $1$-tough property of $G$.
\medskip

Assume $\ell\geq 2$. Then  $|S\cap G_1(u)|\geq \ell$ since $G_1(u)$ is $1$-tough.
Similarly by connecting $u$ to these $\ell$ components intersecting with $G_1(u)$ to form a component, we find $k-\ell+1$ components
after the removal of $S-G_1(u)$ from $G$.  Hence $|S-G_1(u)|\geq k-\ell+1$ since $G$ is $1$-tough.
Then $S=|S\cap G_1(u)|+|S-G_1(u)|\geq \ell+(k-\ell+1)=k+1$, a contradiction.
\end{proof}

\end{frame}

\begin{frame}{\bf Lemma}
If $G$ is $1$-tough and locally $1$-tough then $G$ has toughness greater than $1$.

\begin{proof}
Assume that $G$ has toughness $1$ and pick a subset $S$ of $k$ vertices whose removal will yield $k$ components. Pick $u$ in $S$.
Then the removal of $k-1$ vertices in $S-\{u\}$ from $G-u$ will yield $k$ components, a contradiction to $G-u$ being $1$-tough by previous lemma.
\end{proof}
\end{frame}

\begin{frame}{\bf Toughness of a $1$-tough and locally $1$-tough graph}

By connecting a new vertex to the complete bipartite graph $K_{t, t}$, we have a $1$-tough and locally $1$-tough graph with toughness $(t+1)/t$ for evert $t\geq 1$. Hence the toughness of a $1$-tough and locally $1$-tough graph can approximate to $1$.

\end{frame}

\begin{frame}{\bf Lemma}
If $G$ is $1$-tough and locally $1$-tough of order at least $4$ then $G$ has minimum degree at least $3$.
\bigskip

\begin{proof} If $G$ has minimum degree at most $2$ then $G$ has toughness at most $1=2/2$
because deleting the neighbors of a vertex with minimum degree yields at least two components.
\end{proof}

\begin{rem}
There is only one $1$-tough and locally $1$-tough graph with maximum degree $3$.
\end{rem}

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,2}
{
\coordinate (v\i) at ({sin(2*\i*pi /3 r)},{cos(2*\i*pi /3 r)}) ;
}

\coordinate (v3) at (0,1/4);

\draw[very thick] (v0)--(v3)--(v2)--(v1) (v0)--(v1)--(v3)  (v2)--(v0);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill, color=red] (v3) circle (.1);
\end{tikzpicture}
\end{center}

\end{frame}

\begin{frame}{\bf Lemma}
If $G$ is $1$-tough and locally $1$-tough of order at least $4$ then every edge of $G$ is in at least two triangles.
\bigskip

\begin{proof} Let $e=uv$ be an edge of $G$. Since $u$ has degree at least $3$, $G_1(u)$ is at least $3$, so with  the $1$-tough property of $G_1(u)$, $u$ has at least two neighbors in $G_1(u)$, forming two triangles containing the edge $e$.
\end{proof}
\end{frame}

\begin{frame}{\bf Each edge is in two triangles}

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,7}
{
\coordinate (v\i) at ({3*sin(2*\i*pi /8 r)},{3*cos(2*\i*pi /8 r)}) ;
}

\foreach \i in {8,9,10,11}
{
\coordinate (v\i) at ({2.5*sin(4*(\i-8)*pi /8 r)},{2.5*cos(4*(\i-8)*pi /8 r)}) ;
}

\draw[very thick] (v0)--(v1)--(v2)--(v3)--(v4)--(v5)--(v6)--(v7)--(v0) (v0)--(v8) (v2)--(v9) (v4)--(v10) (v6)--(v11)
(v1)--(v3)--(v5)--(v7)--(v1) (v8)--(v1)--(v9)--(v3)--(v10)--(v5)--(v11)--(v7)--(v8) ;
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\draw[very thick,fill] (v6) circle (.1);
\draw[very thick,fill] (v7) circle (.1);
\draw[very thick,fill] (v8) circle (.1);
\draw[very thick,fill] (v9) circle (.1);
\draw[very thick,fill] (v10) circle (.1);
\draw[very thick,fill] (v11) circle (.1);
\end{tikzpicture}
\bigskip

Each edge of the above non-triangulated graph is in two triangles. This graph is $1$-tough, but not locally $1$-tough.
\end{center}

\end{frame}

\begin{frame}{\bf Proposition}
If $G$ is a $1$-tough and locally $1$-tough planar graph of order at least $4$ and $C$ is a cycle of maximum length in $G$, then
each edge in $C$ is in at least two triangles of the subgraph induced on the vertex set of $C$.
\bigskip

\begin{proof}  If the two triangles of an edge in previous lemma contain a vertex not in $C$ then we have a cycle of length one more than that of $C$, a contradiction to the maximum length assumption of $C$.
\end{proof}
\end{frame}

\begin{frame}{\bf $1$-tough and locally Hamiltonian planar graph of order $7$}

\begin{multicols}{2}

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,...,5}
{
\coordinate (v\i) at ({2*sin(2*\i*pi /6 r)},{2*cos(2*\i*pi /6 r)}) ;
}
\coordinate (v6) at (0,0);

\draw[very thick] (v3)--(v5)--(v0)--(v1)--(v2)--(v4)--(v3)  (v0)--(v4) (v2)--(v6);
\draw[very thick,color=red] (v0)--(v6)--(v4)--(v5)--(v1)--(v3)--(v2)--(v0);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\draw[very thick,fill, color=green] (v6) circle (.1);
\end{tikzpicture}

The graph $DL(6;1,2)^+$.

\end{center}
\bigskip

\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,2}
{
\coordinate (v\i) at ({2*sin(2*\i*pi /3 r)},{2*cos(2*\i*pi /3 r)}) ;
}

\foreach \i in {3,4,5}
{
\coordinate (v\i) at ({0.6*sin(2*(2*\i-5)*pi /6 r)},{0.6*cos(2*(2*\i-5)*pi /6 r)}) ;
}

\coordinate (v6) at (0,0);

\draw[very thick] (v3)--(v0)--(v6)--(v1)--(v2)--(v0)   (v2)--(v6)--(v5) (v4)--(v1)--(v3);
\draw[very thick,color=red] (v0)--(v1)--(v3)--(v6)--(v4)--(v2)--(v5)--(v0);
\draw[very thick,fill] (v0) circle (.1);
\draw[very thick,fill] (v1) circle (.1);
\draw[very thick,fill] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\draw[very thick,fill] (v6) circle (.1);
\end{tikzpicture}

\bigskip

A triangulated graph of order $7$ (There are many different ones including $DL(6;1,2)^+$).

\end{center}
\end{multicols}

\end{frame}

\begin{frame}{\bf Problems}

\begin{enumerate}
\item For $n\leq 7$, find  non-triangulated planar Hamiltonian graphs of order $n$  such that each edge in its Hamiltonian cycle is in two triangles.
\item How many edges are possible for a planar Hamiltonian graph of order $n$ such that each edge in its Hamiltonian cycle is in two triangles?
\item Determine all the  non-triangulated planar Hamiltonian graphs of order $n$  such that each edge in its Hamiltonian cycle is in two triangles.
\item Find a $1$-tough and locally $1$-tough planar graph which is not triangulated.
\end{enumerate}
\end{frame}

\begin{frame}{\bf Lemma}
Let $S$ be a cut set of a locally $1$-tough connected graph $G$. If $x\in S$ is connected to at least two components in $G-S$ then $x$ has degree at least two in the subgraph induced on $S$.
\begin{proof}
The $1$-tough of $G_1(x)$ implies $|G_1(x)\cap S|$ is at least the number of components in $G-S$ that are connected to $x$.
\end{proof}

A cut set $S$ of $G$ is \textcolor{red}{\bf effective} if each  $x\in S$ is connected to at least two components in $G-S$.
\end{frame}

\begin{frame}{\bf Effective cut set}
\begin{center}
\begin{tikzpicture}[scale=1]

\foreach \i in {0,1,2}
{
\coordinate (v\i) at ({2*sin(2*\i*pi /3 r)},{2*cos(2*\i*pi /3 r)}) ;
}

\foreach \i in {3,4,5}
{
\coordinate (v\i) at ({0.6*sin(2*(2*\i-5)*pi /6 r)},{0.6*cos(2*(2*\i-5)*pi /6 r)}) ;
}

\coordinate (v6) at (0,0);

\draw[very thick] (v3)--(v0)--(v6)--(v1)--(v2)--(v0)   (v2)--(v6)--(v5) (v4)--(v1)--(v3) (v0)--(v1)--(v3)--(v6)--(v4)--(v2)--(v5)--(v0);
\draw[very thick,fill, color=green] (v0) circle (.1);
\draw[very thick,fill, color=green] (v1) circle (.1);
\draw[very thick,fill, color=green] (v2) circle (.1);
\draw[very thick,fill] (v3) circle (.1);
\draw[very thick,fill] (v4) circle (.1);
\draw[very thick,fill] (v5) circle (.1);
\draw[very thick,fill, color=green] (v6) circle (.1);
\end{tikzpicture}

\bigskip

The green vertices form an effective cut set.

\end{center}

\end{frame}
\end{document}

### 2020-09-24 spectral radius of matrix new method/slides/conclusion_dec.tex
092420 slides_comparison before proofs

--- 2020-09-05 spectral radius of matrix new method/paper/article_struc1112.tex
@@
-\documentclass[12pt]{article}
+\documentclass{beamer}
 %\usetheme{Warsaw}
 \usepackage{times}  % fonts are up to you
-\usepackage{amssymb, amsmath, mathrsfs,amsthm}
+\usepackage{amssymb, amsmath, mathrsfs}
 \usepackage{multicol}
@@
 \usepackage{xeCJK}
-%\setCJKmainfont{微軟正黑體}
-\setCJKmainfont{simsun.ttf}
-\setCJKsansfont{simhei.ttf}
-\setCJKmonofont{simfang.ttf}
+\setCJKmainfont{微軟正黑體}
 \XeTeXlinebreaklocale "zh"
 \XeTeXlinebreakskip = 0pt plus 1pt
-
-\begin{document}
 
@@
 \newtheorem{remark}[thm]{Remark}
-\newtheorem{pf}[thm]{Proof}
 
@@
 \newtheorem{algo}[thm]{Algorithm}
+%--------------------------------------------------------------------------
+\setbeamertemplate{footline}[page number]{}
+% 加頁碼, 到資料夾裡可以改得更徹底
+\setbeamertemplate{navigation symbols}
+% 加這行會把outline顯示在最上層
 
-\title{TBA}
-\author{Ke-Han Chen\\} % 作者
-%\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
+\begin{document}
+
+\title[]{TBA}
+\author[]{Ke-Han Chen\\} % 作者
+\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
 \date{October 18th, 2018}
-\date{\today} % 日期
+%\date{\today} % 日期
 
+\begin{frame}
 \maketitle
-\begin{abstract}
-    This is my abstract.
-\end{abstract}
+\end{frame}
 
-\section{Preliminaries}
+\begin{frame}{\bf Preliminaries}
+    \begin{thm}
+        If $C$ is nonnegative square matrix, then the following holds. \\
+        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnogative right eigenvector and a corresponding nonnegative left eigenvector.
+    \end{thm}
+\end{frame}
 
-\begin{defn}
-Spectral radius of a matrix $C$ is the largest absolute value of real eigenvalue of $C$. And here we are interested in spectral radius of the adjacency matrix for some simple graph.
-\end{defn}
-\begin{defn}
-    Eigenvalue of a matrix $C$ corresponds to an eigenvector $u$, where $u$ and its eigenvalue $\lambda $  satisfies $Cu = \lambda u$. 
-\end{defn}
-    We introduce a notation of sub-matrix, which is taken from some columns and some rows of a matrix. 
-    \begin{defn}We use $C[\alpha|\beta]$ to denote the sub-matrix of rows $\alpha$ of $C$ and columns $\beta$ of $C$ and $C(\alpha|\beta)$ is the sub-matrix of rows $[n]$ - $\alpha$ of $C$ and columns $[n] - \beta$ of $C$.
-    The bracket [] and parentheses () can be used together is the notation of sub-matrix, such as $C[k|e)$ or $C(k|e]$. 
-\end{defn}
-
-\thm
-        If $C$ is nonnegative square matrix, then the following holds. \\
-        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
+\begin{frame}{\bf Preliminaries}
 
@@
 \end{thm}
+\end{frame}
 
-\begin{pf}
+\begin{frame}{\bf Proof}
             Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
@@
         Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
+\end{frame}
 
+\begin{frame}{\bf Proof (Continue)}
         Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.
@@
          Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
-            $\lambda=\lambda'$ by (\ref{e2}). \qed
+            $\lambda=\lambda'$ by (\ref{e2}).
+\end{frame}
 
- \end{pf}
+\begin{frame}{\bf Our Method}
 
@@
 \end{pmatrix}.$$
-\begin{defn}\label{v_rooted}
- ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
+
+\end{frame}
+
+\begin{frame}{\bf $k$-rooted vector}
+
+\begin{defn}
+ A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
 \end{defn}
@@
 
-\begin{lem}
-If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
+\begin{lem}{vector rooted lemma}
+If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
 \begin{enumerate}
@@
 
-\section{Our first result}
+\end{frame}
+
+\begin{frame}{\bf Our first result}
 
@@
 \end{thm}
+\end{frame}
 
-{\bf $k$-rooted matrix}
+\begin{frame}{\bf $k$-rooted matrix}
 
@@
 
-\begin{defn}[k-rooted matrix]\label{m_rooted}
+\begin{defn}[k-rooted matrix]
 A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-sum vector are all $k$-rooted except the last column of $C'$.
@@
 
+\end{frame}
+
+\begin{frame}
+
 \begin{thm}
-Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
     \begin{enumerate}
@@
     \end{enumerate}
+\end{thm}
 
-\begin{pf}
-\subsection{}
-(i) is immediate from Definition~\ref{m_rooted} and the observation that 
+\end{frame}
+
+\begin{frame}{\bf Remark}
+
 $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
@@
 0 &  & & &  & 1 \\
-\end{pmatrix},$$
-and $Q^{-1}C'Q$ is 
+\end{pmatrix}.$$
+
+The matrix $Q^{-1}C'Q$ is
 $$\begin{pmatrix}
@@
 $$
+\end{frame}
 
-\subsection{(ii)}
+\begin{frame}{}
 
-By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted. 
-Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have 
-$C'Qu=\rho(C')Qu$.
+	\begin{proof}
+        For (i), the form of $Q^{-1}C'Q$ in last page shows that $Q^{-1}C'Q \geq 0$ if and only if C' is k-rooted.
+	For (ii), C' is k-rooted and it has an k-rooted eigenvector Qu. And base on (i), $Q^{-1}C'Q$ is nonnegative implies that it has an eigenvector corresponding to spectral radius of $Q^{-1}C'Q$ 
+	\begin{enumerate}
+        \item[(i)] $C^{ '}*Qu$ = $\lambda * Qu $ = $Q * \lambda u$  ....times $Q^{-1}$ to the left
+        \item[(ii)] $Q^{-1} C^{ '}Q$* u = $\lambda * u$
+    \end{enumerate}
+where $\lambda$ is the spectral readius of C', so it is necessary that (iii) holds.
 
-\subsection{(iii)}
+    \end{proof}
 
-Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.
+\end{frame}
 
-\end{pf}
-\end{thm}
+\begin{frame}
 
@@
 
-\section{Conclusion}
+\end{frame}
+
+\begin{frame}
 
@@
 
-{\bf Proof}
+\end{frame}
+
+\begin{frame}{\bf Proof}
 
@@
 
-{Example}
+\end{frame}
+
+\begin{frame}{\bf Example}
 For the following $4\times 4$ matrix
@@
 $\rho(C)\leq \rho(C')$ by previous theorem.
+\end{frame}
 
-{\bf Counterexample}
+\begin{frame}{\bf Counterexample}
 For the following two $4\times 4$ matrices
@@
 This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$. 
+\end{frame}
 

### 2020-09-24 spectral radius of matrix new method/slides/conclusion_dec.tex

@@
 \institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
-\date{October 18th, 2018}
+\date{October 29th, 2018}
 %\date{\today} % 日期
@@
     \begin{thm}
-        If $C$ is nonnegative square matrix, then the following holds. \\
-        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnogative right eigenvector and a corresponding nonnegative left eigenvector.
+        If $C$ is nonnegative square matrix, then the following (i)-(iii) hold.
+    \begin{enumerate}
+        \item[(i)] The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnogative right eigenvector and a corresponding nonnegative left eigenvector.
+        \item[(ii)] If there exists a column vector $v$ > 0, and a nongative numver $\lambda$ such that $Cv \leq \lambda v$, then $\rho(C) \leq \lambda$.
+        \item[(iii)] If there exists a column vector $v \geq 0, v \neq 0$ and a nonnegative number $\lambda$ such that $Cv \geq \lambda v$, then $\rho(C) \leq \lambda$.
+    \end{enumerate}
+
     \end{thm}
@@
 \begin{equation*}
-        \label{e3}
 (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
@@
             Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
-        \begin{equation}
-            \label{e1}
+        \begin{equation}\label{e1}
             PCQu\leq PC'Qu=\lambda'PQu.
@@
         Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
-        \begin{equation}
-            \label{e2}
+        \begin{equation}\label{e2}
             \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
@@
         Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.
-Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
-         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
+Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
+        Conversely, (\ref{e2}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
             $\lambda=\lambda'$ by (\ref{e2}).
@@
 
-\begin{thm} \label{thm_main}
+\begin{thm}
     Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
@@
 \begin{thm}
+If $C'$ is a $k$-rooted matrix, then $Q^{-1}C'Q$ is nonnegative, $\rho(C')$ is an eigenvalue of $C'$,
+and $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$,
+where $u$ is a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$.
+    Moreover, with $v'=(v'_1, v'_2, \ldots, v'_n)^T$, $r'_{i} = C'_{ik} + C'_{in}$
+    the following (i)-(ii) hold.
 \begin{enumerate}
-        \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-        \item[(ii)]$C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$ as an eigenvalue. $u$ is a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$.
-        \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
+    \item[(i)] If $C' (k|n)$ is positive, then $v'$ is positive.
+    \item[(ii)] If  $C' (k|n)$ is positive and  $r'_i> r'_n$ for all $1\leq i\leq n-1$, then $v'_j>v'_n$ for all $1\leq j\leq n-1.$
 \end{enumerate}
+
 \end{thm}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{proof}
+(i) suppose that $C' [n|n)$ is positive and $v'_n=0$. Then
+$$\sum_{j=1}^{n-1}c'_{nj}v'_j=\sum_{j=1}^nc'_{nj}v'_j=(C'v')_n=\rho(C')v'_n=0.$$
+Hence $v'$ is a zero vector since $c'_{nj}>0$ for $j\leq n-1$, a contradiction. So $v'_n>0$ and $v'>0$ since $v'$ is rooted.
+
+(ii) The assumptions imply that the matrix $Q^{-1}C'Q$ in (\ref{e3.1}) is irreducible.
+Hence $u$ is positive. By Lemma~\ref{l3.15}(ii), $v'_j>v'_n$ for $1\leq j<n.$
+\end{proof}
+
+\end{frame}
+
+\begin{frame}{background}
+
+    \begin{enumerate}
+        \item[(i)] $C^{ '}$*Qu = $\lambda * Qu $ = Q * $\lambda u$  ....times $Q^{-1}$ to the left
+        \item[(ii)] $Q^{-1} C^{ '}Q$* u = $\lambda * u$
+    \end{enumerate}
+
+    Here the $\lambda$ is expected to be the spectral radius of $C^{ '}$ so we wish that $Q^{-1}C^{ '}Q$ > 0, such that this condition $Q^{-1}C^{ '}Q$ > 0 allows that \\
+    \begin{enumerate}
+        \item[(i)] $ C^{ '}$ is k-rooted $\Leftrightarrow Q^{-1}C^{ '}Q > 0$
+        \item[(ii)] $ C^{ '}$ is k-rooted $\Rightarrow C^{ '}$ has a rooted eigenvector
+    \end{enumerate}
+	\begin{proof}
+        if $C^{ '}$ is k-rooted, all columns and (k,n)-sum are rooted except the last one and then $c'_{kj}-c'_{nj} \geq 0$ and $c'_{ij} \geq 0$ for $i \neq k, i < n$, for $1 \leq j \leq n-1$.
+So all columns except the last of $Q^{-1}C^{ '}Q$ is nonnegative.
+    \end{proof}
 
@@
 
-\begin{frame}{}
-
+\begin{frame}
     \begin{proof}
-        For (i), the form of $Q^{-1}C'Q$ in last page shows that $Q^{-1}C'Q \geq 0$ if and only if C' is k-rooted.
-	For (ii), C' is k-rooted and it has an k-rooted eigenvector Qu. And base on (i), $Q^{-1}C'Q$ is nonnegative implies that it has an eigenvector corresponding to spectral radius of $Q^{-1}C'Q$ 
-	\begin{enumerate}
-        \item[(i)] $C^{ '}*Qu$ = $\lambda * Qu $ = $Q * \lambda u$  ....times $Q^{-1}$ to the left
-        \item[(ii)] $Q^{-1} C^{ '}Q$* u = $\lambda * u$
-    \end{enumerate}
-where $\lambda$ is the spectral readius of C', so it is necessary that (iii) holds.
-
+        $C^{ '}$ is k-rooted also implies that (k,n)-sum vector is k-rooted,
+	the last column of $Q^{-1}C^{ '}Q$ is nonnegative.
+	conversely, if all the columns of $Q^{-1}C^{ '}Q$ are nonegative, $C^{ '}$ is k-rooted.
     \end{proof}
+	second, $C^{ '}$ is k-rooted implies that the two postulations of the lemma, $C' (k|n)$ is positive and  $r'_i> r'_n$ for all $1\leq i\leq n-1$ also note that the conclusion of the lemma !!adapt it!!
+is $v'$ is positive.
+and $v'_j>v'_n$ for all $1\leq j\leq n-1.$ ,that is, the eigenvector of $C^{ '}$ is  k-rooted.
 
@@
 
-\begin{frame}
+\begin{frame}{application and some summantion}
+    \begin{thm}
+        maybe the form of Q, is able to generalize the condition of some matrices with same eigenvalues\\
+        or the choice of $C^{ '}$ and Q might affect the spectral radius.
+        the form of eigenvector transformed but the relation in reader's mind remain, so he or she doesn't comprehense the condition difference immediately. \\
+	$Q^{-1}C^{ '}Q > 0 \Rightarrow C^{ '}$ has a rooted eigenvector
 
-\begin{lem}\label{l_diag}
-If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
-the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
-\end{lem}
-
+    \end{thm}
 \end{frame}
@@
 \begin{thm}
-Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
-such that $c'_{ij}\geq c_{ij}$, and then choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$ and $c'_{kj}\geq c'_{nj}>0$, and 
-let $c'_{in}:=r'_i-c'_{ik}$ with $r'_k \geq r'_n$.
-Whereas $c'_{kk}\geq c'_{nk}$ is not necessary.
-Then the $n\times n$ matrix $C'=(c'_{ij})$ has a positive $k$-rooted eigenvector for $\rho(C')$ and $\rho(C)\leq \rho(C')$.
+Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $r'_i$, $c'_{ij}$
+such that $c'_{ij}\geq c_{ij}$, $r'_i\geq c_{ik}+c_{in}$ and $c'_{kj}\geq c'_{nj}>0$, and 
+let $c'_{in}:=r'_i-c'_{ik}$. Then the $n\times n$ matrix $C'=(c'_{ij})$ has a positive $k$-rooted eigenvector for $\rho(C')$ and $\rho(C)\leq \rho(C')$. 
 \end{thm}
@@
 \begin{frame}{\bf Proof}
-
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by \ref{l_diag}, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
-C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$.
-So C'+d*I and C+d*I meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed
 
@@
 1 & 0 & 0 & 1\\ 
-1 & 1 & 0 & 1\\
+1 & 1 & 0 & 0\\ 
 1 & 1 & 1 & 0
@@
 1 & 0 & 1 &  0\\
-1 & 1 & 0 & 1\\
+1 & 1 & 0 & 0\\
 1 & 1 & 1 & 0
@@
 
-\begin{frame}{\bf Counterexample}
-For the following two $4\times 4$ matrices
-$$C=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 0 & 1\\
-1 & 1 & 0 & 0\\
-1 & 1 & 1 & 0
-\end{pmatrix},\quad C'=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 1 &  0\\
-1 & 1 & 0 & 0\\
-1 & 1 & 1 & 0
-\end{pmatrix},$$ 
-we have $CQ\leq C'Q$, but 
-$\rho(C)=2.234\not\leq 2.148= \rho(C')$. 
-This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$. 
+\begin{frame}{conclusion}
+    \begin{thm}
+    \end{thm}
 \end{frame}
-
 \end{document}

### 2020-09-30 spectral radius of matrix new method/paper_form/article_struc1108.tex
0930 preliminiaries and rename half

--- 2020-09-05 spectral radius of matrix new method/paper/article_struc1112.tex
@@
 \newtheorem{algo}[thm]{Algorithm}
+%--------------------------------------------------------------------------
+%\setbeamertemplate{footline}[page number]{}
+% 加頁碼, 到資料夾裡可以改得更徹底
+%\setbeamertemplate{navigation symbols}
+% 加這行會把outline顯示在最上層
+
+\begin{document}
 
@@
 
-\begin{defn}
-Spectral radius of a matrix $C$ is the largest absolute value of real eigenvalue of $C$. And here we are interested in spectral radius of the adjacency matrix for some simple graph.
-\end{defn}
-\begin{defn}
-    Eigenvalue of a matrix $C$ corresponds to an eigenvector $u$, where $u$ and its eigenvalue $\lambda $  satisfies $Cu = \lambda u$. 
-\end{defn}
-    We introduce a notation of sub-matrix, which is taken from some columns and some rows of a matrix. 
-    \begin{defn}We use $C[\alpha|\beta]$ to denote the sub-matrix of rows $\alpha$ of $C$ and columns $\beta$ of $C$ and $C(\alpha|\beta)$ is the sub-matrix of rows $[n]$ - $\alpha$ of $C$ and columns $[n] - \beta$ of $C$.
-    The bracket [] and parentheses () can be used together is the notation of sub-matrix, such as $C[k|e)$ or $C(k|e]$. 
-\end{defn}
+\begin{thm}
+%\begin{Def}
+spectral radius of a matrix C is the largest abstract value of real eigenvalue of C. And here we are interested in spectral radius of the adjacency matrix for some simple graph.
+
+    eigenvalue of a matrix C corresponds to an eigenvector u, where u and its eigenvalue \lambda satisfies Cu = \lambda u.
+Furthermore, if collecting all the eigenvectors forming a matrix of all eigenvectors, U, then CU = DU, where D is the diagonal matrix with eigenvalues d1,d2,...,dk correspond to eigenvectors u_1,u_2,...,u_k , where U = [u_1 u2 ...
+u_k] columns are the eigenvectors.
+
+    Here we introduce a notation of submatrix, which is taken from some columns and some rows of a matrix.
+We use C[\alpha|\beta] to denote the submatrix of rows \alpha of C and columns \beta of C and C(\alpha|\beta) is the submatrix of rows [n] - \alpha of C and columns [n] - \beta of C.
+    The bracket [] and parenthese () can be used together is the notation of submatrix, such as C[k|e) or C(k|e]. 
+\end{thm}
 
@@
         If $C$ is nonnegative square matrix, then the following holds. \\
-        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
+        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnogative right eigenvector and a corresponding nonnegative left eigenvector.
 
@@
 
-\begin{pf}
+{\bf Proof}
             Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
@@
 
+{\bf Proof (Continue)}
         Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.
@@
          Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
-            $\lambda=\lambda'$ by (\ref{e2}). \qed
+            $\lambda=\lambda'$ by (\ref{e2}).
 
- \end{pf}
+{\bf Our Method}
 
@@
 \end{pmatrix}.$$
-\begin{defn}\label{v_rooted}
+
+{\bf $k$-rooted vector}
+
+\begin{defn}[k-rooted]
  ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
@@
 
-\begin{lem}
+\begin{lem}[vector rooted lemma]
 If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
@@
     \end{enumerate}
+\end{thm}
 
-\begin{pf}
-\subsection{}
-(i) is immediate from Definition~\ref{m_rooted} and the observation that 
+{\bf Proof of (i)} 
+(i) is immediate from Definition~\ref{d_rooted} and the observation that 
 $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
@@
 
-\subsection{(ii)}
+{\bf Proof of (ii)}
 
-By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted. 
+By Lemma~\ref{l1.4} $v'=Qu$ is $k$-rooted. 
 Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have 
@@
 
-\subsection{(iii)}
+{\bf Proof of (iii)}
 
 Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.
-
-\end{pf}
-\end{thm}
 

### 2020-09-30 spectral radius of matrix new method/paper_form/preliminary/root.tex
0930 preliminiaries and rename half

--- 2020-09-05 spectral radius of matrix new method/paper/article_struc1112.tex
@@
-\documentclass[12pt]{article}
+\documentclass{article}
 %\usetheme{Warsaw}
@@
 \newtheorem{algo}[thm]{Algorithm}
-
-\title{TBA}
-\author{Ke-Han Chen\\} % 作者
-%\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
-\date{October 18th, 2018}
-\date{\today} % 日期
-
-\maketitle
-\begin{abstract}
-    This is my abstract.
-\end{abstract}
 
@@
 \end{pmatrix}.$$
-\begin{defn}\label{v_rooted}
+\begin{defn}[k-rooted]
  ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
@@
 
-\section{Our first result}
-
-\begin{thm} \label{thm_main}
-    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
-Assume that
-\begin{enumerate}
-\item[(i)]   $C[-|n)\leq C'[-|n)$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-\item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
-such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
-\item[(iv)] $v^Tv'>0.$
-\end{enumerate}
- Then $\lambda\leq \lambda'$.
-Moreover, $\lambda=\lambda'$
-if and only if
-\begin{enumerate}
-\item[(a)] $c_{ik}+c_{in}=c'_{ik}+c'_{in}$\qquad for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
-\item[(b)]
-$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
-\end{enumerate} \qed
-\end{thm}
-
-{\bf $k$-rooted matrix}
-
-\begin{defn}[(k,n)-sum]
-For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
-\end{defn}
-
-\begin{defn}[k-rooted matrix]\label{m_rooted}
-A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-sum vector are all $k$-rooted except the last column of $C'$.
-\end{defn}
-
-\begin{thm}
-Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-    \begin{enumerate}
-        \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-        \item[(ii)]$C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$ as an eigenvalue. $u$ is a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$.
-        \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
-    \end{enumerate}
-
-\begin{pf}
-\subsection{}
-(i) is immediate from Definition~\ref{m_rooted} and the observation that 
-$$Q^{-1}=I-E_{kn}=\begin{pmatrix}
-1 &  & & &  & 0 \\
- & 1 &  &      &  &  \\
- &  & \ddots & &  & -1 \\
- &  &        & &  &  \\
-  &  & & & 1 &  \\
-0 &  & & &  & 1 \\
-\end{pmatrix},$$
-and $Q^{-1}C'Q$ is 
-$$\begin{pmatrix}
-c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
-\vdots \\
-c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
-c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
-c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
-\vdots              & \vdots & \ddots              & \vdots & \vdots \\
-c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
-\end{pmatrix}.
-$$
-
-\subsection{(ii)}
-
-By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted. 
-Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have 
-$C'Qu=\rho(C')Qu$.
-
-\subsection{(iii)}
-
-Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.
-
-\end{pf}
-\end{thm}
-
-\begin{lem}\label{l_diag}
-If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
-the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
-\end{lem}
-
-\section{Conclusion}
-
-\begin{thm}
-Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
-such that $c'_{ij}\geq c_{ij}$, and then choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$ and $c'_{kj}\geq c'_{nj}>0$, and 
-let $c'_{in}:=r'_i-c'_{ik}$ with $r'_k \geq r'_n$.
-Whereas $c'_{kk}\geq c'_{nk}$ is not necessary.
-Then the $n\times n$ matrix $C'=(c'_{ij})$ has a positive $k$-rooted eigenvector for $\rho(C')$ and $\rho(C)\leq \rho(C')$.
-\end{thm}
-
-{\bf Proof}
-
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by \ref{l_diag}, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
-C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$.
-So C'+d*I and C+d*I meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed
-
-{Example}
-For the following $4\times 4$ matrix
-$$C=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 0 & 1\\
-1 & 1 & 0 & 1\\
-1 & 1 & 1 & 0
-\end{pmatrix},$$
-we choose
-$$C'=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 1 &  0\\
-1 & 1 & 0 & 1\\
-1 & 1 & 1 & 0
-\end{pmatrix}.$$
-Then
-$\rho(C)\leq \rho(C')$ by previous theorem.
-
-{\bf Counterexample}
-For the following two $4\times 4$ matrices
-$$C=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 0 & 1\\
-1 & 1 & 0 & 0\\
-1 & 1 & 1 & 0
-\end{pmatrix},\quad C'=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 1 &  0\\
-1 & 1 & 0 & 0\\
-1 & 1 & 1 & 0
-\end{pmatrix},$$ 
-we have $CQ\leq C'Q$, but 
-$\rho(C)=2.234\not\leq 2.148= \rho(C')$. 
-This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.
-
 \end{document}

### 2020-10-06 spectral radius of matrix new method/slides/corre_mis1019.tex
full essay slide 1006 present

--- 2020-09-05 spectral radius of matrix new method/paper/article_struc1112.tex
@@
-\documentclass[12pt]{article}
+\documentclass[]{beamer}
 %\usetheme{Warsaw}
 \usepackage{times}  % fonts are up to you
-\usepackage{amssymb, amsmath, mathrsfs,amsthm}
+\usepackage{amssymb, amsmath, mathrsfs}
 \usepackage{multicol}
@@
 \newtheorem{algo}[thm]{Algorithm}
+%--------------------------------------------------------------------------
+\setbeamertemplate{footline}[page number]{}
+% 加頁碼, 到資料夾裡可以改得更徹底
+\setbeamertemplate{navigation symbols}
+% 加這行會把outline顯示在最上層
 
-\title{TBA}
-\author{Ke-Han Chen\\} % 作者
-%\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
-\date{October 18th, 2018}
-\date{\today} % 日期
+\usepackage{comment}
 
+\begin{document}
+
+\title[]{TBA}
+\author[]{Ke-Han Chen} % 作者
+\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
+\date{October 6th, 2020}
+%\date{\today} % 日期
+
+\begin{frame}
     \maketitle
-\begin{abstract}
-    This is my abstract.
-\end{abstract}
+\end{frame}
 
-\section{Preliminaries}
+\begin{frame}
+    \frametitle{Preliminaries}
+    Let $\mathbb{R}$ and $\mathbb{C}$ denote the field of real numbers and complex numbers respectively.
 
     \begin{defn}
-Spectral radius of a matrix $C$ is the largest absolute value of real eigenvalue of $C$. And here we are interested in spectral radius of the adjacency matrix for some simple graph.
-\end{defn}
-\begin{defn}
-    Eigenvalue of a matrix $C$ corresponds to an eigenvector $u$, where $u$ and its eigenvalue $\lambda $  satisfies $Cu = \lambda u$. 
-\end{defn}
-    We introduce a notation of sub-matrix, which is taken from some columns and some rows of a matrix. 
-    \begin{defn}We use $C[\alpha|\beta]$ to denote the sub-matrix of rows $\alpha$ of $C$ and columns $\beta$ of $C$ and $C(\alpha|\beta)$ is the sub-matrix of rows $[n]$ - $\alpha$ of $C$ and columns $[n] - \beta$ of $C$.
-    The bracket [] and parentheses () can be used together is the notation of sub-matrix, such as $C[k|e)$ or $C(k|e]$. 
+        Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a nonzero column vector.
+The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
+        Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
     \end{defn}
 
-\thm
-        If $C$ is nonnegative square matrix, then the following holds. \\
-        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
+    \begin{defn}
 
-The following theorem is from [].
+    When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$ is defined by
+    $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
+    where $|\lambda|$ is the magnitude of complex number $\lambda.$
+    \end{defn}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Preliminaries}
+
+    We are interested in spectral radius of the following matrix associated with a simple graph.
+
+    \begin{defn} Given an undirected graph
+    G, the$\textit{ adjacency matrix}$ of G is the square matrix $A = (a_{ij})$ indexed by vertices of G,
+    and
+    \[a_{ij} =\begin{cases}
+    1, \text{if $i$ is adjacent to $j$}, \\
+    0, \text{otherwise.}
+    \end{cases}
+    \]
+
+    \end{defn}
+
+    \begin{defn}
+    Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral radius of the adjacency matrix of G.
+    \end{defn}
+
+\end{frame}
+
+\begin{frame}
+    \frametitle{Preliminaries}
+    We introduce a notation of submatrix, which is taken from some columns and some rows of a matrix.
+    \begin{defn}
+        For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column indices of 
+        $C$ respectively,  We use $C[\alpha|\beta]$ to denote the submatrix of $C$ with size
+         $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$ and $j\in\beta$,
+    \end{defn}
+
+\end{frame}
+
+\begin{frame}
+    \frametitle{ Preliminaries}
+
+%The following theorem is from [].\cite{content}
 
@@
     \end{thm}
+\end{frame}
 
-\begin{pf}
+\begin{frame}
+    \frametitle{ Proof}
             Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
@@
         Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
+\end{frame}
 
+\begin{frame}
+    \frametitle{ Proof (Continue)}
         Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.
@@
          Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
-            $\lambda=\lambda'$ by (\ref{e2}). \qed
+            $\lambda=\lambda'$ by (\ref{e2}).
+\end{frame}
 
- \end{pf}
+\begin{frame}
+    \frametitle{ Our Method}
 
@@
 \end{pmatrix}.$$
-\begin{defn}\label{v_rooted}
- ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
+
+\end{frame}
+
+\begin{frame}
+    \frametitle{ $k$-rooted vector}
+
+\begin{defn}
+ A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
 \end{defn}
@@
 
-\section{Our first result}
+\end{frame}
+
+\begin{frame}
+    \frametitle{ Our first result}
 
@@
 \begin{enumerate}
-\item[(i)]   $C[-|n)\leq C'[-|n)$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
+\item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
 \item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
@@
 \end{thm}
+\end{frame}
 
+\begin{frame}{}
+
+    \begin{proof}
+        The proof is based on Theorem 1.7 with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1})  $.%!!!!!!!! 
+        The assumption (i) $PCQ\leq PC'Q$ of Theorem 1.7 holds by the condition (i) of this theorem. 
+        Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and 
+        Lemma 2.2(i). Hence the assumption (ii) of Theorem 1.7 holds. The assumptions (iii) and (iv) 
+        of Theorem 1.7 clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and $v'= Qu$  
+        Hence $\lambda \leq \lambda' $ by the conclusion of Theorem 1.7. Moreover $\lambda = \lambda'$ 
+        if and only if (\ref{pre0}) holds, and this is equivalent to conditions (a),(b),(c) of this theorem. 
+        \end{proof}
+
+\end{frame}
+
+\begin{frame}
     {\bf $k$-rooted matrix}
-
     \begin{defn}[(k,n)-sum]
@@
     \end{defn}
+\end{frame}
 
-\begin{thm}
+\begin{frame}
+
+    \begin{thm} \label{lma_m_rooted}
         Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
@@
                 \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-        \item[(ii)]$C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$ as an eigenvalue. $u$ is a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$.
+                \item[(ii)]Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
                 \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
             \end{enumerate}
+        \end{thm}
 
-\begin{pf}
-\subsection{}
-(i) is immediate from Definition~\ref{m_rooted} and the observation that 
+\end{frame}
+
+\begin{frame}
+    \frametitle{Remark}
+
     $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
@@
     0 &  & & &  & 1 \\
-\end{pmatrix},$$
-and $Q^{-1}C'Q$ is 
+    \end{pmatrix}.$$
+
+    The matrix $Q^{-1}C'Q$ is
     $$\begin{pmatrix}
@@
     $$
+\end{frame}
 
-\subsection{(ii)}
+\begin{frame}{Remark}
 
+	\begin{proof}
+        (i) is immediate from Definition~\ref{m_rooted} and the observation that   
+        $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
+        1 &  & & &  & 0 \\
+         & 1 &  &      &  &  \\
+         &  & \ddots & &  & -1 \\
+         &  &        & &  &  \\
+          &  & & & 1 &  \\
+        0 &  & & &  & 1 \\
+        \end{pmatrix},$$
+    \end{proof}
+
+\end{frame}
+
+\begin{frame}
+    \begin{proof}
+        and $Q^{-1}C'Q$ is
+        $$\begin{pmatrix}
+        c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
+        \vdots \\
+        c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
+        c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
+        c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
+        \vdots              & \vdots & \ddots              & \vdots & \vdots \\
+        c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
+        \end{pmatrix}.$$
+    \end{proof}
+\end{frame}
+
+\begin{frame}
+    \begin{proof}{Continue}
+        (ii)
             By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted.  
             Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
+            $Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
             $C'Qu=\rho(C')Qu$.
 
-\subsection{(iii)}
-
+        (iii)
         Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.
 
-\end{pf}
-\end{thm}
+    \end{proof}
+\end{frame}
+
+\begin{frame}
 
@@
 
-\section{Conclusion}
+\end{frame}
+
+\begin{frame}
 
 \begin{thm}
-Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
-such that $c'_{ij}\geq c_{ij}$, and then choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$ and $c'_{kj}\geq c'_{nj}>0$, and 
-let $c'_{in}:=r'_i-c'_{ik}$ with $r'_k \geq r'_n$.
-Whereas $c'_{kk}\geq c'_{nk}$ is not necessary.
-Then the $n\times n$ matrix $C'=(c'_{ij})$ has a positive $k$-rooted eigenvector for $\rho(C')$ and $\rho(C)\leq \rho(C')$.
+    Let $C$ be an $n\times n$ nonnegative Tmatrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
+    such that $c'_{ij}\geq c_{ij}$ and $c'_{kj}\geq c'_{nj}>0$, and choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, and
+    $r'_k \geq r'_n$. Moreover choose $c'_{in}:=r'_i-c'_{ik}$. Then $\rho(C)\leq \rho(C')$, when $C'=(c'_{ij})$.
 \end{thm}
 
-{\bf Proof}
+\end{frame}
 
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by \ref{l_diag}, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
+\begin{frame}
+    \frametitle{ Proof}
+
+The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by *, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
 C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$.
-So C'+d*I and C+d*I meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed
+So C'+d*I and C+d*I meet the conditions of (\ref{l_diag}), and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed
 
-{Example}
+\end{frame}
+
+\begin{frame}
+    \frametitle{ Example}
     For the following $4\times 4$ matrix
@@
     $\rho(C)\leq \rho(C')$ by previous theorem.
+\end{frame}
 
-{\bf Counterexample}
+\begin{frame}
+    \frametitle{Counterexample}
     For the following two $4\times 4$ matrices
@@
     This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$. 
+\end{frame}
 

### 2020-11-04 spectral radius of matrix new method/slides/slide100620.tex
update with slides and tree idea

--- 2020-10-06 spectral radius of matrix new method/slides/corre_mis1019.tex
@@
 \institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
-\date{October 6th, 2020}
-%\date{\today} % 日期
+% \date{October 6th, 2020}% 日期
+\date{\today} % 日期
 
@@
 
-    \begin{thm}
+    \begin{thm}\label{pre_thm}
         Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
@@
         \begin{enumerate}
-            \item[(i)]    $PCQ\leq PC'Q$;
+            \item[(i)]    $PCQ\leq PC'Q$;\label{Q1}
             \item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
@@
             if and only if
-                \begin{equation*}
+                \begin{equation}
                     \label{e3}
             (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
-        \end{equation*}
+        \end{equation}
     \end{thm}
@@
 
-\begin{lem}{vector rooted lemma}
+\begin{lem}{vector rooted lemma}\label{v_rooted}
 If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
@@
 
-\begin{thm} \label{thm_main}
+\begin{thm}\label{thm_main}
     Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
@@
     \begin{proof}
-        The proof is based on Theorem 1.7 with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1})  $.%!!!!!!!! 
-        The assumption (i) $PCQ\leq PC'Q$ of Theorem 1.7 holds by the condition (i) of this theorem. 
+        The proof is based on Theorem (\ref{pre_thm}) with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1})  $.%!!!!!!!! 
+        The assumption (i) $PCQ\leq PC'Q$ of Theorem (\ref{pre_thm}) holds by the condition (i) of this theorem. 
         Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and 
-        Lemma 2.2(i). Hence the assumption (ii) of Theorem 1.7 holds. The assumptions (iii) and (iv) 
-        of Theorem 1.7 clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and $v'= Qu$  
-        Hence $\lambda \leq \lambda' $ by the conclusion of Theorem 1.7. Moreover $\lambda = \lambda'$ 
-        if and only if (\ref{pre0}) holds, and this is equivalent to conditions (a),(b),(c) of this theorem. 
+        Lemma 2.2(i). Hence the assumption (ii) of Theorem (\ref{pre_thm}) holds. The assumptions (iii) and (iv) 
+        of Theorem (\ref{pre_thm}) clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and $v'= Qu$  
+        Hence $\lambda \leq \lambda' $ by the conclusion of Theorem (\ref{pre_thm}). Moreover $\lambda = \lambda'$ 
+        if and only if (\ref{e3}) holds, and this is equivalent to conditions (a),(b) of this theorem. 
         \end{proof}
@@
 \begin{frame}
-    \begin{proof}{Continue}
+    \frametitle{{Continue}}
+    \begin{proof}
         (ii)
@@
 
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by *, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
+The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by (~\ref{v_rooted}), For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
 C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$.

### 2020-11-04 spectral radius of matrix new method/slides/slide101320.tex
update with slides and tree idea

--- 2020-11-04 spectral radius of matrix new method/slides/slide100620.tex
@@
 
-\begin{frame}
-    \frametitle{Preliminaries}
+\begin{frame}{Preliminaries}
+
     Let $\mathbb{R}$ and $\mathbb{C}$ denote the field of real numbers and complex numbers respectively.
-
     \begin{defn}
@@
     \end{defn}
-
     \begin{defn}
-
         When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$ is defined by
@@
 \begin{frame}
-    \frametitle{Preliminaries}
 
@@
 
-    \begin{defn} Given an undirected graph
-    G, the$\textit{ adjacency matrix}$ of G is the square matrix $A = (a_{ij})$ indexed by vertices of G,
-    and
+    \begin{defn}
+    Given an undirected graph G, the$\textit{ adjacency matrix}$ of G is the square matrix $A = (a_{ij})$ indexed by vertices of G, and
     \[a_{ij} =\begin{cases}
@@
     \]
-
     \end{defn}
@@
 \begin{frame}
-    \frametitle{Preliminaries}
     We introduce a notation of submatrix, which is taken from some columns and some rows of a matrix.
@@
 
-\begin{frame}
-    \frametitle{ Preliminaries}
+% \begin{frame}
 
@@
         \end{equation}
-    \end{thm}
-\end{frame}
+    \end{thm}%
+% \end{frame}
 
-\begin{frame}
-    \frametitle{ Proof}
+% \begin{frame}
+    % \frametitle{ Proof}
             Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
@@
         Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
-\end{frame}
+% \end{frame}
 
@@
 
-\begin{frame}
+% \begin{frame}
     \frametitle{ $k$-rooted vector}
@@
 
-\begin{lem}{vector rooted lemma}\label{v_rooted}
+\begin{lem}
+\begin{equation}
+    \textit{vector rooted lemma}\label{v_rooted}
+\end{equation}
 If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
@@
 
-\end{frame}
+% \end{frame}
 
-\begin{frame}
+% \begin{frame}
     \frametitle{ Our first result}
@@
 \end{thm}
-\end{frame}
+% \end{frame}
 
-\begin{frame}{}
+% \begin{frame}{}
 
@@
 
-\end{frame}
+% \end{frame}
 
-\begin{frame}
+% \begin{frame}
     {\bf $k$-rooted matrix}
@@
     \end{defn}
-\end{frame}
+% \end{frame}
 
-\begin{frame}
+% \begin{frame}
 
@@
 
-\end{frame}
+% \end{frame}
 
@@
 
-\begin{frame}
+% \begin{frame}
 
-\begin{lem}\label{l_diag}
+\begin{lem}\label{l_diag}   %end of label
 If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has

### 2020-11-04 spectral radius of matrix new method/thesis/article110320.tex
update with tree idea 1104

--- 2020-11-04 spectral radius of matrix new method/slides/slide101320.tex
@@
-\documentclass[]{beamer}
-%\usetheme{Warsaw}
-\usepackage{times}  % fonts are up to you
-\usepackage{amssymb, amsmath, mathrsfs}
-\usepackage{multicol}
-\usepackage{bm}
+\documentclass{article}
+% \topmargin 0pt
+
+% \topmargin=-1.5cm
+% \oddsidemargin=0.7cm
+% \textheight=23.5cm
+% \textwidth=15cm
+% \setlength{\baselineskip}{24pt}
+% \renewcommand{\baselinestretch}{1.5} %行距
+
+\usepackage{fontspec}   %加這個就可以設定字體
+\usepackage{xeCJK}       %讓中英文字體分開設置
+%\usepackage{times}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{ulem}
+% \usepackage{amsfonts}
+\usepackage{mathrsfs}
+% \usepackage{tabularx,array}
+% \usepackage{pgf,tikz}
+% \usepackage{blkarray} %line 80-92 Q formula matrix index
+%\usepackage{colortbl}
 
-\usepackage{fontspec}
-\usepackage{xeCJK}
-\setCJKmainfont{微軟正黑體}
-\XeTeXlinebreaklocale "zh"
-\XeTeXlinebreakskip = 0pt plus 1pt
+% \usetikzlibrary{arrows}
+\setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
+% \XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
+% \XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
+% \title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
+% \author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
+% \date{} %不要日期
 
-% THEOREMS ---------------------------------------------------------------
+\def\UrlFont{\rm}
+
 \theoremstyle{plain}
-% block中的字會變成數學體, 斜體字
-\newtheorem{thm}{Theorem}[section]
+\newtheorem{thm}{Theorem}[chapter]
 \newtheorem{cor}[thm]{Corollary}
@@
 \newtheorem{remark}[thm]{Remark}
-
 \newtheorem{eg}[thm]{Example}
@@
 \theoremstyle{definition}
-% block中的字是正常字體
+\newtheorem{defn}[thm]{Definition}
 \newtheorem{ex}[thm]{Exercise}
-\newtheorem{defn}[thm]{Definition}
 \newtheorem{prob}[thm]{Problem}
 \newtheorem{exam}[thm]{Example}
+\newtheorem{nota}[thm]{Notation}
 \newtheorem{rem}[thm]{Remark}
-
-\newtheorem{algo}[thm]{Algorithm}
-%--------------------------------------------------------------------------
-\setbeamertemplate{footline}[page number]{}
-% 加頁碼, 到資料夾裡可以改得更徹底
-\setbeamertemplate{navigation symbols}
-% 加這行會把outline顯示在最上層
+\newtheorem{ques}[thm]{Question}
+\newtheorem{pof}[thm]{Proof.}
 
@@
 
-\title[]{TBA}
-\author[]{Ke-Han Chen} % 作者
-\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
-% \date{October 6th, 2020}% 日期
-\date{\today} % 日期
-
-\begin{frame}
-    \maketitle
-\end{frame}
-
-\begin{frame}{Preliminaries}
-
-    Let $\mathbb{R}$ and $\mathbb{C}$ denote the field of real numbers and complex numbers respectively.
-    \begin{defn}
-        Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a nonzero column vector.
-The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
-        Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
-    \end{defn}
-    \begin{defn}
-        When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$ is defined by
-        $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
-        where $|\lambda|$ is the magnitude of complex number $\lambda.$
-    \end{defn}
-\end{frame}
-
-\begin{frame}
-
-    We are interested in spectral radius of the following matrix associated with a simple graph.
-
-    \begin{defn}
-    Given an undirected graph G, the$\textit{ adjacency matrix}$ of G is the square matrix $A = (a_{ij})$ indexed by vertices of G, and
-    \[a_{ij} =\begin{cases}
-    1, \text{if $i$ is adjacent to $j$}, \\
-    0, \text{otherwise.}
-    \end{cases}
-    \]
-    \end{defn}
-
-    \begin{defn}
-    Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral radius of the adjacency matrix of G.
-    \end{defn}
-
-\end{frame}
-
-\begin{frame}
-    We introduce a notation of submatrix, which is taken from some columns and some rows of a matrix.
-    \begin{defn}
-        For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column indices of 
-        $C$ respectively,  We use $C[\alpha|\beta]$ to denote the submatrix of $C$ with size
-         $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$ and $j\in\beta$,
-    \end{defn}
-
-\end{frame}
-
-% \begin{frame}
-
-%The following theorem is from [].\cite{content}
-
-    \begin{thm}\label{pre_thm}
-        Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
-        Assume that
-        \begin{enumerate}
-            \item[(i)]    $PCQ\leq PC'Q$;\label{Q1}
-            \item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
-            \item[(iii)] there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
-            such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector $v^TP$; and
-            \item[(iv)] $v^TPQu>0.$
-            \end{enumerate}
-            Then $\lambda\leq \lambda'$.
-                Moreover, $\lambda=\lambda'$ 
-            if and only if
-                \begin{equation}
-                    \label{e3}
-            (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
-        \end{equation}
-    \end{thm}%
-% \end{frame}
-
-% \begin{frame}
-    % \frametitle{ Proof}
-            Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
-        \begin{equation}\label{e1}
-            PCQu\leq PC'Qu=\lambda'PQu.
-        \end{equation}
-        Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
-        \begin{equation}\label{e2}
-            \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
-        \end{equation}
-        Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
-% \end{frame}
-
-\begin{frame}
-    \frametitle{ Proof (Continue)}
-        Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.
-Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
-         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
-            $\lambda=\lambda'$ by (\ref{e2}).
-\end{frame}
-
-\begin{frame}
-    \frametitle{ Our Method}
-
- Throughout fix $k\in [n-1]$.
-Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the  position $k,n$ of $E_{kn}$.
+\section{Our Method}
+We use [n-1] as notation of the set of elements from one to n-1, which is {1,2,$...$,n}.
+Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$.
 We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
@@
 
-\end{frame}
-
-% \begin{frame}
-    \frametitle{ $k$-rooted vector}
+% 
+    { $k$-rooted vector}
 
@@
 
-% \end{frame}
+%
 
-% \begin{frame}
-    \frametitle{ Our first result}
+% 
+    { Our first result}
 
@@
 \end{thm}
-% \end{frame}
+%
 
-% \begin{frame}{}
+% {}
 
     \begin{proof}
-        The proof is based on Theorem (\ref{pre_thm}) with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1})  $.%!!!!!!!! 
+        The proof is based on Theorem (\ref{pre_thm}) with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1})$. 
         The assumption (i) $PCQ\leq PC'Q$ of Theorem (\ref{pre_thm}) holds by the condition (i) of this theorem. 
@@
 
-% \end{frame}
+%
 
-% \begin{frame}
+% 
     {\bf $k$-rooted matrix}
@@
     \end{defn}
-% \end{frame}
+%
 
-% \begin{frame}
+%
 
-    \begin{thm} \label{lma_m_rooted}
+    \begin{lem}\label{lma_m_rooted}
         Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
@@
             \end{enumerate}
-        \end{thm}
+    \end{lem}
 
-% \end{frame}
+%
 
-\begin{frame}
-    \frametitle{Remark}
+    \begin{rem}
 
@@
 
-    The matrix $Q^{-1}C'Q$ is
+    The matrix $C'Q$ is
     $$\begin{pmatrix}
@@
     c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
-    c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
+    c'_{k1} & c'_{k2} &\cdots      & c'_{kn-1} & c'_{kk}+c'_{kn}\\
     c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
@@
     $$
-\end{frame}
+    \end{rem}
 
-\begin{frame}{Remark}
+\begin{comment}
+
+{Remark}
 
@@
     \end{proof}
+ \end{comment}
 
-\end{frame}
-
-\begin{frame}
     \begin{proof}
@@
     \end{proof}
-\end{frame}
 
-\begin{frame}
-    \frametitle{{Continue}}
+    {{Continue}}
     \begin{proof}
@@
     \end{proof}
-\end{frame}
 
-% \begin{frame}
+%
 
@@
 
-% \end{frame}
-
-\begin{frame}
+%
 
@@
 
-\end{frame}
+    { Proof}
 
-\begin{frame}
-    \frametitle{ Proof}
+The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by (~\ref{v_rooted}), For certain d, if C'+dI is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
+C' would share the same eigenvector with C'+dI and has eigenvalue $\lambda$.
+So C'+dI and C+dI meet the conditions of (\ref{l_diag}), and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and then $\rho(C') \geq \rho(C)$  \qed
 
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by (~\ref{v_rooted}), For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
-C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$.
-So C'+d*I and C+d*I meet the conditions of (\ref{l_diag}), and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed
-
-\end{frame}
-
-\begin{frame}
-    \frametitle{ Example}
+    { Example}
     For the following $4\times 4$ matrix
@@
     $\rho(C)\leq \rho(C')$ by previous theorem.
-\end{frame}
 
-\begin{frame}
-    \frametitle{Counterexample}
+    {Counterexample}
     For the following two $4\times 4$ matrices
@@
     This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.
-\end{frame}
+
+\begin{thebibliography}{20}
+\normalsize
+\addcontentsline{toc}{chapter}{Bibliography}
+
+\bibitem{chang}
+Yen-Jen Cheng, {\it  A matrix realization of spectral bounds
+of the spectral radius of a nonnegative matrix}, Ph.D. Thesis, NCTU, 2018.
+
+\bibitem{prn_fros1}
+A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012
+
+\bibitem{prn_fros2}
+R. A. Horn , C. R. Johnson, {\it Matrix analysis}, Cambrigde University Press, 1985.
+
+\end{thebibliography}
 

### 2020-11-04 spectral radius of matrix new method/thesis/article110320.tex
1104 temp saved

@@
 \documentclass{article}
+
 % \topmargin 0pt
@@
 
+%\renewcommand {\refname} {Bibliography}
+
 \begin{document}
+
+\section{Preliminaries}
+
+    Let $\mathbb{R}$ and $\mathbb{C}$ denote the
+
+field of real numbers and complex numbers respectively.
+    \begin{defn}
+
+Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a
+
+nonzero column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$
+
+of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
+
+%Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
+    \end{defn}
+
+   \begin{defn}
+        When $C$ is an $n \times n$ real matrix, the $\textit
+
+{spectral radius} $ $\rho(C)$ of $C$ is defined by
+        $$\rho(C):=\max\{~|
+
+\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
+        where $|
+
+\lambda|$ is the magnitude of complex number $\lambda.$
+    \end{defn}
+
+\begin{thm} 
+        %\bf{Perron–Frobenius theorem} \\
+        If $C$ is
+
+nonnegative square matrix, then the spectral radius $\rho(C)$ is an eigenvalue of
+
+$C$ with a corresponding nonnogative right eigenvector and a corresponding
+
+nonnegative left eigenvector.
+    \end{thm}
+
+    We are interested in spectral
+
+radius of the following matrix associated with a simple graph.
+
+    \begin{defn}
+
+  Given an undirected graph G, the$\textit{ adjacency matrix}$ of G is the square
+
+matrix $A = (a_{ij})$ indexed by vertices of G, and
+    \[a_{ij} =\begin{cases}
+
+ 1, \text{if $i$ is adjacent to $j$}, \\
+    0, \text{otherwise.}
+    \end{cases}
+
+   \]
+    \end{defn}
+
+    \begin{defn}
+    Given an undirected graph G, the $
+
+\textit{spectral radius}$  $\rho(G) $ of G is the spectral radius of the adjacency
+
+matrix of G.
+    \end{defn}
+
+    We introduce a notation of submatrix, which is
+
+taken from some columns and some rows of a matrix.
+    \begin{defn}
+        For a
+
+matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column
+
+indices of 
+        $C$ respectively,  We use $C[\alpha|\beta]$ to denote the
+
+submatrix of $C$ with size
+         $ |\alpha| \times |\beta| $ that has entries
+
+$c_{ij}$ for $i\in \alpha$ and $j\in\beta$,
+    \end{defn}
+
+We introduce two
+
+matrices $P$ and $Q$ in the following theorem, where $P$ is a permutation matrix
+
+which is multiplied to the left side, and $Q$ is sum of elementary matrix and
+
+certain binary matrix. In which $P$ generalize row permutation on cases of $C$
+
+matrix,and $Q$ is the transform from $C'$ to C', which is the first n-1 columns
+
+and sum of certain columns. We aim to find C' such that $C'$ majors $C$,i.e. $C
+
+\leq C'$
+
+The following theorem is from [].\cite{content}
+
+    \begin
+
+{thm}\label{pre_thm}
+        Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n
+
+\times n$ matrices.
+        Assume that
+        \begin{enumerate}
+
+\item[(i)]    $PCQ\leq PC'Q$;\label{Q1}
+            \item[(ii)]  there exist a
+
+nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in
+
+\mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated
+
+eigenvector $Qu$;
+            \item[(iii)] there exist a nonnegative row vector
+
+$v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
+
+such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector
+
+$v^TP$; and
+            \item[(iv)] $v^TPQu>0.$
+            \end{enumerate}
+
+     Then $\lambda\leq \lambda'$.
+                Moreover, $\lambda=\lambda'$
+
+         if and only if
+                \begin{equation}
+
+\label{e3}
+            (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n
+
+\hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
+        \end{equation}
+    \end
+
+{thm}%
+
+    % { Proof}
+            Multiplying the nonnegative vector $u$ in
+
+(ii) to the right of both terms of  (i),
+        \begin{equation}\label{e1}
+
+     PCQu\leq PC'Qu=\lambda'PQu.
+        \end{equation}
+        Multiplying the
+
+nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the
+
+left of all terms  in (\ref{e1}), we have
+        \begin{equation}\label{e2}
+
+      \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
+        \end{equation}
+
+       Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $
+
+\lambda\leq \lambda'$ and finish the proof of the first part.
+
+    { Proof
+
+(Continue)}
+        Assume that $\lambda=\lambda'$, so the inequality in (\ref
+
+{e2}) is an equality.  Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i
+
+\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$
+
+with $u_j\not=0.$ 
+         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j}
+
+v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
+            $
+
+\lambda=\lambda'$ by (\ref{e2}).
 
@@
 We use [n-1] as notation of the set of elements from one to n-1, which is {1,2,$...$,n}.
-Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$.
-We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
+Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$. We will apply the previous theorem with $P=I$ and
+
+\begin{equation}
+Q=I+E_{kn}=\begin{pmatrix} \label{Q1}
 1 &  & & &  & 0 \\
@@
 0 &  & & &  & 1 \\
-\end{pmatrix}.$$
+\end{pmatrix}.
+\end{equation}
 
-% 
-    { $k$-rooted vector}
-
-\begin{defn}
- A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
+\begin{defn}[$k$-rooted vector]
+~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
 \end{defn}
@@
 
-\begin{lem}
-\begin{equation}
-    \textit{vector rooted lemma}\label{v_rooted}
-\end{equation}
+\begin{lem}[vector rooted lemma]\label{v_rooted}
 If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
@@
 
-%
-
-% 
-    { Our first result}
-
-\begin{thm}\label{thm_main}
+\begin{thm}[Our first result]\label{thm_main}
     Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
@@
 \item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-\item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+\item[(ii)] there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
 such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
@@
 \begin{enumerate}
-\item[(a)] $c_{ik}+c_{in}=c'_{ik}+c'_{in}$\qquad for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
-\item[(b)]
-$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
+    \item[(a)]    $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
+    \item[(b)]  $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
+    \item[(c)]   $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
 \end{enumerate} \qed
@@
 
-%
+    We are interested in the matrices $C'$ that have $k$-rooted eigenvectors.
+    Motivated by the condition (i) of theorem 2.3, we provide the following two definitions.
 
-% 
-    {\bf $k$-rooted matrix}
     \begin{defn}[(k,n)-sum]
-        For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
+        For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
     \end{defn}
+
+    Note that the last column of $C'Q$ is the $(k, n)$-{\it sum} vector of $C'$
 
@@
 
-%
-
 \begin{lem}\label{l_diag}   %end of label
@@
 \end{lem}
-
-%
 
@@
 
-    { Proof}
+\begin{Proof}
 
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by (~\ref{v_rooted}), For certain d, if C'+dI is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
-C' would share the same eigenvector with C'+dI and has eigenvalue $\lambda$.
-So C'+dI and C+dI meet the conditions of (\ref{l_diag}), and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and then $\rho(C') \geq \rho(C)$  \qed
+The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by (\ref{v_rooted}),
+ For certain d, if C'+dI is k-rooted, then it has a k-rooted eigenvector with its spectral
+  radius $\lambda + d$. C' would share the same eigenvector with C'+dI and has eigenvalue
+   $\lambda$. So C'+dI and C+dI meet the conditions of (\ref{l_diag}), and we can show that
+    $\rho(C' + dI) \geq \rho(C +dI)$ and then $\rho(C') \geq \rho(C)$  \qed    
+\end{proof}
 
-    { Example}
+\subsection{Example}
     For the following $4\times 4$ matrix
@@
     \end{pmatrix}.$$
+    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ \ref{thm_main},
     Then
@@
 
-    {Counterexample}
+\subsection{Counterexample}
     For the following two $4\times 4$ matrices
@@
     \end{pmatrix},$$ 
+    specify $n$=4, $k$=3 in $Q = I +E_{kn} = I + E_{34}$  
+$$CQ=\begin{pmatrix}
+0 & 0 & 1 & 2\\
+1 & 0 & 0 & 1\\
+1 & 1 & 0 & 0\\
+1 & 1 & 1 & 1
+\end{pmatrix},\quad C'Q=\begin{pmatrix}
+0 & 0 & 1 & 2\\
+1 & 0 & 1 & 1\\
+1 & 1 & 0 & 0\\
+1 & 1 & 1 & 1
+\end{pmatrix},$$
+
     we have $CQ\leq C'Q$, but 

### 2020-11-04 spectral radius of matrix new method/thesis/our_result.tex
proof 1.8 line cut
1104 temp saved

@@
-\documentclass[12pt]{report}%{article}
+\documentclass[12pt]{report}
 
@@
 
+\usepackage{comment}
+
 %\renewcommand {\refname} {Bibliography}
@@
 
-\begin{defn}\label{v_rooted}
+\begin{defn}[$k$-rooted vector]%\label{k_rooted}
  ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
@@
 \begin{lem}
-If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
+If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
 \begin{enumerate}
@@
 \end{enumerate} \qed
-
 \end{thm}
@@
 \begin{proof}
-The proof is based on Theorem 1.7 with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1} )  $.
+The proof is based on Theorem 1.7 with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1} )$. 
 The assumption (i) $PCQ\leq PC'Q$ of Theorem 1.7 holds by the condition (i) of this theorem. 
-Let $u = Q^{-1}v'$.
-Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and Lemma 2.2(i).
-Hence the assumption (ii) of Theorem 1.7 holds.
-The assumptions (iii) and (iv) of Theorem 1.7 clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and $v'= Qu$  Hence $\lambda \leq \lambda' $ by the conclusion of Theorem 1.7.
-Moreover $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to conditions (a),(b),(c) of this theorem.
+Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and
+ Lemma 2.2(i). Hence the assumption (ii) of Theorem 1.7 holds. The assumptions (iii) and (iv)
+  of Theorem 1.7 clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and
+   $v'= Qu$  Hence $\lambda \leq \lambda' $ by the conclusion of Theorem 1.7. Moreover
+    $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to
+     conditions (a),(b),(c) of this theorem. 
 \end{proof}
@@
 
-\begin{defn}
+\begin{defn}[(k,n)-sum]
 For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$.
@@
 Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
-$Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$
+$Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
 $C'Qu=\rho(C')Qu$.
@@
 
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on (\ref{lma_m_rooted}) ; by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has a $k$-rooted eigenvector with its spectral radius $\lambda + d$.
-C' would share the same eigenvector with $C'+dI$ and has eigenvalue $\lambda$.
-So $C'+dI$ and $C+dI$ meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and then $\rho(C') \geq \rho(C)$  \qed
+The assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on
+ (\ref{lma_m_rooted}) ; by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has
+  a $k$-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same
+   eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
+    conditions of \ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
+     then $\rho(C') \geq \rho(C)$  \qed
+\end{proof}
 
@@
 
-\end{proof}
-
 \end{document}

### 2020-11-05 spectral radius of matrix new method/thesis/article110320.tex
1105 update

--- 2020-11-04 spectral radius of matrix new method/thesis/article110320.tex
@@
 %\usepackage{colortbl}
-
+\usepackage{enumitem}% enumerate labels   roman
 % \usetikzlibrary{arrows}
@@
 \theoremstyle{plain}
-\newtheorem{thm}{Theorem}[chapter]
+\newtheorem{thm}{Theorem}[subsection]
 \newtheorem{cor}[thm]{Corollary}
@@
 
+%\renewcommand {\refname} {Bibliography}
+
 \begin{document}
+
+\section{Preliminaries}
+
+Let $\mathbb{R}$ and $\mathbb{C}$ denote the
+ field of real numbers and complex numbers respectively.
+
+\begin{defn}       
+Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a
+ nonzero column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ 
+of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
+
+%Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
+\end{defn}
+
+\begin{defn}
+    When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$
+        of $C$ is defined by 
+        $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
+    where $|\lambda|$ is the magnitude of complex number $\lambda.$
+\end{defn}
+
+\begin{thm}[Perron–Frobenius theorem]\cite{chang}
+    If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
+    eigenvalue of $C$ with a corresponding nonnogative right eigenvector and a
+    corresponding nonnegative left eigenvector.
+\end{thm}
+
+We are interested in spectral radius of the following matrix associated with a simple graph.
+
+\begin{defn} 
+    Given an undirected graph G, the$\textit{ adjacency matrix}$ of G is the square 
+    matrix $A = (a_{ij})$ indexed by vertices of G, and
+     \[a_{ij} =\begin{cases} 
+        1, \text{if $i$ is adjacent to $j$}, \\
+        0, \text{otherwise.}
+            \end{cases}
+     \]
+\end{defn}
+
+\begin{defn}
+Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
+ radius of the adjacency matrix of G.
+\end{defn}
+
+    We introduce a notation of submatrix, which is taken from some columns and some rows of a
+     matrix.
+
+\begin{defn}
+    For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column 
+    indices of $C$ respectively,  We use $C[\alpha|\beta]$ to denote the 
+    submatrix of $C$ with size $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$
+    and $j\in\beta$,
+\end{defn}
+
+We introduce two matrices $P$ and $Q$ in the following theorem, where $P$ is a permutation
+ matrix which is multiplied to the left side, and $Q$ is sum of elementary matrix and
+ certain binary matrix. In which $P$ generalize row permutation on cases of $C$
+ matrix,and $Q$ is the transform from $C'$ to C', which is the first n-1 columns
+  and sum of certain columns. We aim to find C' such that $C'$ majors $C$,i.e. $C\leq C'$
+
+The following theorem is from [].\cite{content}
+
+\begin{thm}\label{pre_thm}
+    Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
+Assume that
+\begin{enumerate}[label=(\Roman*)]
+    \item \label{pre_thm_em1}  $PCQ\leq PC'Q$;
+    \item \label{pre_thm_em2} there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a
+    scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with
+    associated eigenvector $Qu$;
+    \item \label{pre_thm_em3} there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar
+    $\lambda\in \mathbb{R}$such that $\lambda$ is an eigenvalue of $C$ with associated  left
+    eigenvector $v^TP$; and
+    \item \label{pre_thm_em4}$v^TPQu>0.$
+\end{enumerate}
+    Then $\lambda\leq \lambda'$. Moreover, $\lambda=\lambda'$ if and only if
+    \begin{equation}\label{pre0}
+        (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
+    \end{equation}
+\end{thm}
+\begin{pof}
+    Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm} assumption
+    \ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
+    \ref{pre_thm_em1},    
+    \begin{equation}\label{pre1}
+       PCQu\leq PC'Qu=\lambda'PQu.
+    \end{equation}
+    Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption
+     \ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), where $v^TP$ is
+    left eigenvector of $C$ for $\lambda$, thus we have
+    \begin{equation}\label{pre2}
+        \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
+    \end{equation}
+        Now delete the positive term $v^TPQu$ by assumption \ref{pre_thm_em4} to obtain
+        $\lambda\leq \lambda'$ and finish the proof of the first part.
+        Assume that $\lambda=\lambda'$, so the inequality in (\ref{pre2}) is an equality.
+        Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence,
+        $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with
+        $u_j\not=0.$ Conversely, (\ref{pre0}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=
+         \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so $\lambda=\lambda'$ by (\ref{pre2}).
 
@@
 We use [n-1] as notation of the set of elements from one to n-1, which is {1,2,$...$,n}.
-Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$.
-We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
+Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$. We will apply the previous theorem with $P=I$ and
+
+\begin{equation}
+Q=I+E_{kn}=\begin{pmatrix} \label{Q_1}
 1 &  & & &  & 0 \\
@@
 
-\begin{lem}
-\begin{equation}
-    \textit{vector rooted lemma}\label{v_rooted}
-\end{equation}
+\begin{lem}[vector rooted lemma]\label{lem:rt_vec}
 If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
-\begin{enumerate}
-\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
-\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
+\begin{enumerate}[label=(\Roman*)]
+\item \label{lem:rt_vec:en1}$v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
+\item $u_k>0$ if and only if $v'_k>v'_n$.
 \end{enumerate}
@@
 
-%
-
-% 
-    { Our first result}
-
-\begin{thm}\label{thm_main}
+\begin{thm}[Our first result]\label{thm_main}
     Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
 Assume that
-\begin{enumerate}
-\item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-\item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+\begin{enumerate}[label=(\Roman*)]
+\item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
+\item \label{thm_main:condition_ii} there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
 such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
-\item[(iv)] $v^Tv'>0.$
+\item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+\item $v^Tv'>0.$
 \end{enumerate}
@@
 if and only if
-\begin{enumerate}
-\item[(a)] $c_{ik}+c_{in}=c'_{ik}+c'_{in}$\qquad for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
-\item[(b)]
-$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
+\begin{enumerate}[label=(\alph*)]
+    \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
+    \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
+    \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
 \end{enumerate} \qed
@@
 
-    \begin{proof}
-        The proof is based on Theorem (\ref{pre_thm}) with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1})$. 
-        The assumption (i) $PCQ\leq PC'Q$ of Theorem (\ref{pre_thm}) holds by the condition (i) of this theorem. 
-        Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and 
-        Lemma 2.2(i).  Hence the assumption (ii) of Theorem (\ref{pre_thm}) holds. The assumptions (iii) and (iv) 
-        of Theorem (\ref{pre_thm}) clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and $v'= Qu$  
-        Hence $\lambda \leq \lambda' $ by the conclusion of Theorem (\ref{pre_thm}). Moreover $\lambda = \lambda'$ 
-        if and only if (\ref{e3}) holds, and this is equivalent to conditions (a),(b) of this theorem. 
-    \end{proof}
+\begin{pof}
+    The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q_1} )$. 
+    The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this theorem. 
+    Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and
+     Lemma~\ref{lem:rt_vec}\ref{lem:rt_vec:en1}. Hence the assumption \ref{pre_thm_em2} of Theorem~\ref{pre_thm} holds. The assumptions \ref{pre_thm_em3} and \ref{pre_thm_em4}
+      of Theorem~\ref{pre_thm} clearly hold by conditions~\ref{thm_main:condition_iii},\ref{thm_main:condition_iv} of this theorem since $P = I$ and
+       $v'= Qu$  Hence $\lambda \leq \lambda' $ by the necessary condition of Theorem~\ref{pre_thm}. Moreover
+        $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to
+         conditions \ref{thm_main:equ_cond_a},\ref{thm_main:equ_cond_b},\ref{thm_main:equ_cond_c} of this theorem. 
+    \end{pof}
 
-%
+    We are interested in the matrices $C'$ that have $k$-rooted eigenvectors.
+    Motivated by the condition (i) of theorem 2.3, we provide the following two definitions.
 
-% 
-    {\bf $k$-rooted matrix}
     \begin{defn}[(k,n)-sum]
-        For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
+        For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
     \end{defn}
+
+    Note that the last column of $C'Q$ is the $(k, n)$-{\it sum} vector of $C'$
 
@@
     \end{defn}
-%
 
-%
-
+    The following theorem shows that a $k$-rooted matrix has a $k$-rooted eigenvector.
     \begin{lem}\label{lma_m_rooted}
         Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-            \begin{enumerate}
-                \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-                \item[(ii)]Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
-                \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
+            \begin{enumerate}[label=(\Roman*)]
+                \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
+                \item Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
+                 for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
+                \item $\rho(C')$ = $\rho(Q^{-1}C'Q)$
             \end{enumerate}
@@
 
-{Remark}
-
-	\begin{proof}
+\begin{rmk}
         (i) is immediate from Definition~\ref{m_rooted} and the observation that   
@@
         \end{pmatrix},$$
-    \end{proof}
+\end{rmk}
  \end{comment}
 
-    \begin{proof}
+    \begin{pof}
         and $Q^{-1}C'Q$ is
@@
         \end{pmatrix}.$$
-    \end{proof}
+    \end{pof}
 
-    {{Continue}}
-    \begin{proof}
+    \begin{pof}
         (ii)
-            By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted.  
+            By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $k$-rooted.  
             Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
@@
 
-    \end{proof}
-
-%
+    \end{pof}
 
@@
 
-%
-
 \begin{thm}
-    Let $C$ be an $n\times n$ nonnegative Tmatrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
+    Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
     such that $c'_{ij}\geq c_{ij}$ and $c'_{kj}\geq c'_{nj}>0$, and choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, and
@@
 
-    { Proof}
+\begin{pof}
+    These assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on
+    (\ref{lma_m_rooted});\\
+    calculation:  \\
+       \\
+    by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has
+     a $k$-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same
+      eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
+       conditions of \ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
+        then $\rho(C') \geq \rho(C)$  \qed
+\end{pof}
 
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by (~\ref{v_rooted}), For certain d, if C'+dI is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
-C' would share the same eigenvector with C'+dI and has eigenvalue $\lambda$.
-So C'+dI and C+dI meet the conditions of (\ref{l_diag}), and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and then $\rho(C') \geq \rho(C)$  \qed
-
-    { Example}
+\subsection{Example}
     For the following $4\times 4$ matrix
@@
     \end{pmatrix},$$ 
+    specify $n$=4, $k$=3 in $Q = I +E_{kn} = I + E_{34}$  
+    $$CQ=\begin{pmatrix}
+    0 & 0 & 1 & 2\\
+    1 & 0 & 0 & 1\\
+    1 & 1 & 0 & 0\\
+    1 & 1 & 1 & 1
+    \end{pmatrix},\quad C'Q=\begin{pmatrix}
+    0 & 0 & 1 & 2\\
+    1 & 0 & 1 & 1\\
+    1 & 1 & 0 & 0\\
+    1 & 1 & 1 & 1
+    \end{pmatrix},$$
+
     we have $CQ\leq C'Q$, but 
@@
 
+\section{References}
 \begin{thebibliography}{20}

### 2020-11-05 spectral radius of matrix new method/thesis/our_result.tex
1105 update

@@
 %\usepackage{colortbl}
+\usepackage{enumitem}% enumerate labels   roman
 
@@
 \begin{equation}
+  \label{Q_1}
 Q=I+E_{kn}=\begin{blockarray}{cccccc}
@@
 \begin{block}{(ccccc)c}
-	\label{Q1}
+
   1 &   &   &   &   &  \\
@@
 \begin{defn}[$k$-rooted vector]%\label{k_rooted}
- ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
+ A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
 \end{defn}
@@
 
-\begin{lem}
+\begin{lem}\label{lem:rt_vec}
 If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
-\begin{enumerate}
-\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
-\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
+\begin{enumerate}[label=(\Roman*)]
+\item \label{lem:rt_vec:en1}$v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
+\item $u_k>0$ if and only if $v'_k>v'_n$.
 \end{enumerate}
@@
 Assume that
-\begin{enumerate}
-\item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-\item[(ii)] there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+\begin{enumerate}[label=(\Roman*)]
+\item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
+\item \label{thm_main:condition_ii}there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
 such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
-\item[(iv)] $v^Tv'>0.$
+\item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+\item $v^Tv'>0.$
 \end{enumerate}
@@
 if and only if
-\begin{enumerate}
-\item[(a)]    $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
-\item[(b)]  $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
-\item[(c)]   $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
+\begin{enumerate}[label=(\alph*)]
+\item  \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
+\item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
+\item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
 \end{enumerate} \qed
@@
 
-\begin{proof}
-The proof is based on Theorem 1.7 with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1} )$. 
-The assumption (i) $PCQ\leq PC'Q$ of Theorem 1.7 holds by the condition (i) of this theorem. 
-Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and
- Lemma 2.2(i). Hence the assumption (ii) of Theorem 1.7 holds. The assumptions (iii) and (iv)
-  of Theorem 1.7 clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and
-   $v'= Qu$  Hence $\lambda \leq \lambda' $ by the conclusion of Theorem 1.7. Moreover
+\begin{pof}
+The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn}$ in (\ref{Q_1} ). 
+The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this theorem. 
+Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and
+ Lemma~\ref{lem:rt_vec}\ref{lem:rt_vec:en1}. Hence the assumption \ref{pre_thm_em2} of Theorem~\ref{pre_thm} holds. The assumptions \ref{pre_thm_em3} and \ref{pre_thm_em4}
+  of Theorem~\ref{pre_thm} clearly hold by conditions~\ref{thm_main:condition_iii},\ref{thm_main:condition_iv} of this theorem since $P = I$ and
+   $v'= Qu$  Hence $\lambda \leq \lambda' $ by the necessary condition of Theorem~\ref{pre_thm}. Moreover
     $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to
-     conditions (a),(b),(c) of this theorem. 
-\end{proof}
+     conditions \ref{thm_main:equ_cond_a},\ref{thm_main:equ_cond_b},\ref{thm_main:equ_cond_c} of this theorem. 
+\end{pof}
 
@@
 \begin{defn}[(k,n)-sum]
-For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$.
+For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)-sum$ vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$.
 \end{defn}
 
-Note that the last column of $C'Q$ is the $(k, n)$-{\it sum} vector of $C'$
+Note that the last column of $C'Q$ is the $(k, n)-sum$ vector of $C'$
 
 \begin{defn}\label{m_rooted}
-A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-{\it sum} vector are all $k$-rooted except the last column of $C'$.
+A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)-sum$ vector are all $k$-rooted except the last column of $C'$.
 \end{defn}
@@
 
-\begin{thm} \label{lma_m_rooted}
+\begin{lem} \label{lma_m_rooted}
 Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-    \begin{enumerate}
-        \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-        \item[(ii)]Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
-        \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
+    \begin{enumerate}[label=(\Roman*)]
+        \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
+        \item Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
+         for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
+        \item $\rho(C')$ = $\rho(Q^{-1}C'Q)$
     \end{enumerate}
-\end{thm}
+\end{lem}
 
-\begin{proof}
+\begin{pof}
 (i) is immediate from Definition~\ref{m_rooted} and the observation that
@@
 (ii)
-By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted.
+By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $k$-rooted.
 Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
@@
 
-\end{proof}
+\end{pof}
 
@@
 \begin{thm}
-Let $C$ be an $n\times n$ nonnegative Tmatrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
+Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
 such that $c'_{ij}\geq c_{ij}$ and $c'_{kj}\geq c'_{nj}>0$, and choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, and
@@
 
-\begin{proof}
-
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on
- (\ref{lma_m_rooted}) ; by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has
+\begin{pof}
+These assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on
+ (\ref{lma_m_rooted});\\
+ calculation:  \\
+    \\
+ by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has
   a $k$-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same
@@
      then $\rho(C') \geq \rho(C)$  \qed
-\end{proof}
+\end{pof}
 
-\noindent{\bf Example}
+\section{Example}
 For the following $4\times 4$ matrix
@@
 \end{pmatrix}.$$
-Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ \ref{thm_main},   
+Check the conditions of theorem~\ref{thm_main},   
 Then
-$\rho(C)\leq \rho(C')$ by Theorem 4.8.
+$\rho(C)\leq \rho(C')$ by Theorem 4.8. % @@@@@@@@@@@
 
-{\bf Counterexample}
+\section{Counterexample}
 For the following two $4\times 4$ matrices

### 2020-11-05 spectral radius of matrix new method/thesis/preliminiaries.tex
full essay slide 1006 present
1105 update

@@
 \theoremstyle{plain}
-\newtheorem{thm}{Theorem}[chapter]
+\newtheorem{thm}{Theorem}[section]
 \newtheorem{cor}[thm]{Corollary}
@@
 
-Let $\mathbb{R}$ and $\mathbb{C}$ denote the field of real numbers and complex numbers respectively.
+Let $\mathbb{R}$ and $\mathbb{C}$ denote the
+ field of real numbers and complex numbers respectively.
 
 \begin{defn}
-    Let $C$ be an $n \times n$ real matrix, and $u \in \mathbb{R}^n$ be a nonzero column vector.
-The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
+    Let $C$ be an $n \times n$ real matrix, and $u \in \mathbb{R}^n$ be a
+     nonzero column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$
+      of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
 
@@
 
-When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$ is defined by
+When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$
+ is defined by 
  $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
@@
 
-\begin{defn} Given an undirected graph
-G, the$\textit{ adjacency matrix}$ of G is the square matrix $A = (a_{ij})$ indexed by vertices of G,
-and
+\begin{defn}
+    Given an undirected graph G, the$\textit{ adjacency matrix}$ of G is the square
+     matrix $A = (a_{ij})$ indexed by vertices of G, and
       \[a_{ij} =\begin{cases}
@@
     \]
-
 \end{defn}
@@
 \begin{defn}
-Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral radius of the adjacency matrix of G.
+Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
+ radius of the adjacency matrix of G.
 \end{defn}
 
-    We introduce a notation of submatrix, which is taken from some columns and some rows of a matrix.
+    We introduce a notation of submatrix, which is taken from some columns and some rows of a
+     matrix.
 
-\begin{defn}For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column indices of $C$ respectively,  We use $C[\alpha|\beta]$ to denote the submatrix of $C$ with size $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$ and $j\in\beta$,
-
-The following theorem is a part of Perron-Frobenius theorem \cite{'content'}.
+\begin{defn}
+    For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column
+    indices of $C$ respectively,  We use $C[\alpha|\beta]$ to denote the submatrix of $C$ with
+    size $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$
+    and $j\in\beta$,
+\end{defn}
+The following theorem is a part of Perron-Frobenius theorem %\cite{'content'}.
 \begin{comment}
@@
 
-\end{defn}
-
-%Peron Frobius theorem
-\begin{thm}
-        If $C$ is a nonnegative square matrix, then spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
+\begin{thm}[Peron Frobius theorem]
+        If $C$ is a nonnegative square matrix, then spectral radius $\rho(C)$ is an eigenvalue
+         of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative
+          left eigenvector.
 \end{thm}
 
-The following theorem is from \cite{chang}. For completeness, we also provide the proof.
+The following theorem is from \%. For completeness, we also provide the proof.  %\cite{chang}
 
-\begin{thm}
+\begin{thm}\label{pre_thm}
     Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
 Assume that
-\begin{enumerate}
-\item[(i)]    $PCQ\leq PC'Q$;
-\item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
-\item[(iii)] there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
-such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector $v^TP$; and
-\item[(iv)] $v^TPQu>0.$
+\begin{enumerate}[label=(\Roman*)]
+    \item \label{pre_thm_em1}  $PCQ\leq PC'Q$;   %
+    \item \label{pre_thm_em2}  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a
+    scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with
+    associated eigenvector $Qu$;
+    \item \label{pre_thm_em3}  there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar
+    $\lambda\in \mathbb{R}$such that $\lambda$ is an eigenvalue of $C$ with associated  left
+    eigenvector $v^TP$; and
+    \item \label{pre_thm_em4} $v^TPQu>0.$
 \end{enumerate}
- Then $\lambda\leq \lambda'$.
-    Moreover, $\lambda=\lambda'$
-if and only if
-    \begin{equation}
-        \label{pre0}
+    Then $\lambda\leq \lambda'$. Moreover, $\lambda=\lambda'$if and only if
+    \begin{equation}\label{pre0}
         (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
@@
 
-\begin{proof}
-            Multiplying the nonnegative vector $u$ in assumption (ii), where $Qu$ is eigenvector of $C'$,  to the right of both terms of  (i),
-        \begin{equation}
-            \label{pre1}
+\begin{pof}
+    Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm} assumption
+    ~\ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
+    ~\ref{pre_thm_em1},
+    \begin{equation}\label{pre1}
         PCQu\leq PC'Qu=\lambda'PQu.
     \end{equation}
-        Multiplying the nonnegative vector $v^T$  in assumption (iii) , where $v^TP$ is left eigenvector of $C$ for $\lambda$,to the left of all terms  in (\ref{pre1}), we have
-        \begin{equation}
-            \label{pre2}
+    Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption
+    ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), where $v^TP$ is
+    left eigenvector of $C$ for $\lambda$, thus we have
+    \begin{equation}\label{pre2}
         \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
     \end{equation}
-        Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
+        Now delete the positive term $v^TPQu$ by assumption \ref{pre_thm_em4} to obtain
+         $\lambda\leq \lambda'$ and finish the proof of the first part.
+    Assume that $\lambda=\lambda'$, so the inequality in (\ref{pre2}) is an equality.
+    Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence,
+    $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with
+    $u_j\not=0.$ Conversely, (\ref{pre0}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=
+    \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so $\lambda=\lambda'$ by (\ref{pre2}).
 
-        Assume that $\lambda=\lambda'$, so the inequality in (\ref{pre2}) is an equality.
-Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
-         Conversely, (\ref{pre0}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
-            $\lambda=\lambda'$ by (\ref{pre2}).
-
- \end{proof}
+ \end{pof}
 

### 2020-11-06 spectral radius of matrix new method/thesis/our_result.tex
1106 update with success labels but unknown packages

@@
 \usepackage{pgf,tikz}
-\usepackage{blkarray} %line 80-92 Q formula matrix index
+\usepackage{blkarray} %begin{equation}   Q=I+E_{kn} : Q formula matrix index
 %\usepackage{colortbl}
@@
 \chapter{Our result}
+
+\begin{rem}[theorem in previous slide]\label{pre_thm}
+  Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
+Assume that
+\begin{enumerate}[label=(\roman*)]
+  \item \label{pre_thm_em1}  $PCQ\leq PC'Q$;   %
+  \item \label{pre_thm_em2}  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a
+  scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with
+  associated eigenvector $Qu$;
+  \item \label{pre_thm_em3}  there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar
+  $\lambda\in \mathbb{R}$such that $\lambda$ is an eigenvalue of $C$ with associated  left
+  eigenvector $v^TP$; and
+  \item \label{pre_thm_em4} $v^TPQu>0.$
+\end{enumerate}
+  Then $\lambda\leq \lambda'$. Moreover, $\lambda=\lambda'$if and only if
+  \begin{equation}\label{pre0}
+      (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
+  \end{equation}
+\end{rem}
+
+\begin{pof}
+  Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm} assumption
+  ~\ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
+  ~\ref{pre_thm_em1},
+  \begin{equation}\label{pre1}
+      PCQu\leq PC'Qu=\lambda'PQu.
+  \end{equation}
+  Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption
+  ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), where $v^TP$ is
+  left eigenvector of $C$ for $\lambda$, thus we have
+  \begin{equation}\label{pre2}
+      \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
+  \end{equation}
+      Now delete the positive term $v^TPQu$ by assumption \ref{pre_thm_em4} to obtain
+       $\lambda\leq \lambda'$ and finish the proof of the first part.
+  Assume that $\lambda=\lambda'$, so the inequality in (\ref{pre2}) is an equality.
+  Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence,
+  $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with
+  $u_j\not=0.$ Conversely, (\ref{pre0}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=
+  \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so $\lambda=\lambda'$ by (\ref{pre2}).
+
+\end{pof}
+
 We will prove the main Theorems introduced in the introduction. First, we need some natations.
@@
 \begin{equation} 
-  \label{Q_1}
 Q=I+E_{kn}=\begin{blockarray}{cccccc} 
 %a & b & c & d & e \\
- &  &  & &  \\
+ &  &  & & & \\  
 \begin{block}{(ccccc)c}
-
+	% \label{Q_1}
   1 &   &   &   &   &  \\
@@
 \end{blockarray}
-\end{equation}
+\end{equation}  \label{Q_1}
 
@@
 If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
-\begin{enumerate}[label=(\Roman*)]
+\begin{enumerate}[label=(\roman*)]
 \item \label{lem:rt_vec:en1}$v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
@@
 Assume that
-\begin{enumerate}[label=(\Roman*)]
+\begin{enumerate}[label=(\roman*)]
 \item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
@@
 such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-\item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
-\item $v^Tv'>0.$
+\item \label{thm_main:condition_iii} there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+\item \label{thm_main:condition_iv} $v^Tv'>0.$
 \end{enumerate}
@@
 \begin{defn}\label{m_rooted}
-A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)-sum$ vector are all $k$-rooted except the last column of $C'$.
+A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)-sum$ vector are all $k-rooted$ except the last column of $C'$.
 \end{defn}
@@
 The following theorem shows that a $k$-rooted matrix has a $k$-rooted eigenvector. 
-
 \begin{lem} \label{lma_m_rooted}
 Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-    \begin{enumerate}[label=(\Roman*)]
+    \begin{enumerate}[label=(\roman*)]
         \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.

### 2020-11-10 spectral radius of matrix new method/paper_form/first result/root.tex

--- 2020-09-05 spectral radius of matrix new method/paper/article_struc1112.tex
@@
 
-\title{TBA}
-\author{Ke-Han Chen\\} % 作者
-%\institute[Dep. of A. Math., NCTU]{Department of Applied Mathematics\\National Chiao Tung University}
-\date{October 18th, 2018}
-\date{\today} % 日期
-
-\maketitle
-\begin{abstract}
-    This is my abstract.
-\end{abstract}
-
-\section{Preliminaries}
-
-\begin{defn}
-Spectral radius of a matrix $C$ is the largest absolute value of real eigenvalue of $C$. And here we are interested in spectral radius of the adjacency matrix for some simple graph.
-\end{defn}
-\begin{defn}
-    Eigenvalue of a matrix $C$ corresponds to an eigenvector $u$, where $u$ and its eigenvalue $\lambda $  satisfies $Cu = \lambda u$. 
-\end{defn}
-    We introduce a notation of sub-matrix, which is taken from some columns and some rows of a matrix. 
-    \begin{defn}We use $C[\alpha|\beta]$ to denote the sub-matrix of rows $\alpha$ of $C$ and columns $\beta$ of $C$ and $C(\alpha|\beta)$ is the sub-matrix of rows $[n]$ - $\alpha$ of $C$ and columns $[n] - \beta$ of $C$.
-    The bracket [] and parentheses () can be used together is the notation of sub-matrix, such as $C[k|e)$ or $C(k|e]$. 
-\end{defn}
-
-\thm
-        If $C$ is nonnegative square matrix, then the following holds. \\
-        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
-
-The following theorem is from [].
-
-\begin{thm}
- Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
-Assume that
-\begin{enumerate}
-\item[(i)]    $PCQ\leq PC'Q$;
-\item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
-\item[(iii)] there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
-such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector $v^TP$; and
-\item[(iv)] $v^TPQu>0.$
-\end{enumerate}
- Then $\lambda\leq \lambda'$.
-    Moreover, $\lambda=\lambda'$ 
-if and only if
-    \begin{equation*}
-        \label{e3}
-(PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
-\end{equation*}
-\end{thm}
-
-\begin{pf}
-            Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
-        \begin{equation}
-            \label{e1}
-            PCQu\leq PC'Qu=\lambda'PQu.
-        \end{equation}
-        Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
-        \begin{equation}
-            \label{e2}
-            \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
-        \end{equation}
-        Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
-
-        Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.
-Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
-         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
-            $\lambda=\lambda'$ by (\ref{e2}). \qed
-
- \end{pf}
-
- Throughout fix $k\in [n-1]$.
-Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the  position $k,n$ of $E_{kn}$.
-We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
-1 &  & & &  & 0 \\
- & 1 &  &      &  &  \\
- &  & \ddots & &  & 1 \\
- &  &        & &  &  \\
-  &  & & & 1 &  \\
-0 &  & & &  & 1 \\
-\end{pmatrix}.$$
-\begin{defn}\label{v_rooted}
- ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
-\end{defn}
-\bigskip
-
-The following Lemma is immediate from the above definition.
-\bigskip
-
-\begin{lem}
-If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
-\begin{enumerate}
-\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
-\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
-\end{enumerate}
-\qed
-\end{lem}
-
 \section{Our first result}
@@
 \subsection{}
-(i) is immediate from Definition~\ref{m_rooted} and the observation that 
+is immediate from Definition~\ref{d_rooted} and the observation that 
 $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
@@
 
-By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted. 
+By Lemma~\ref{l1.4} $v'=Qu$ is $k$-rooted. 
 Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have 
@@
 
-\section{Conclusion}
-
-\begin{thm}
-Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
-such that $c'_{ij}\geq c_{ij}$, and then choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$ and $c'_{kj}\geq c'_{nj}>0$, and 
-let $c'_{in}:=r'_i-c'_{ik}$ with $r'_k \geq r'_n$.
-Whereas $c'_{kk}\geq c'_{nk}$ is not necessary.
-Then the $n\times n$ matrix $C'=(c'_{ij})$ has a positive $k$-rooted eigenvector for $\rho(C')$ and $\rho(C)\leq \rho(C')$.
-\end{thm}
-
-{\bf Proof}
-
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by \ref{l_diag}, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
-C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$.
-So C'+d*I and C+d*I meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed
-
-{Example}
-For the following $4\times 4$ matrix
-$$C=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 0 & 1\\
-1 & 1 & 0 & 1\\
-1 & 1 & 1 & 0
-\end{pmatrix},$$
-we choose
-$$C'=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 1 &  0\\
-1 & 1 & 0 & 1\\
-1 & 1 & 1 & 0
-\end{pmatrix}.$$
-Then
-$\rho(C)\leq \rho(C')$ by previous theorem.
-
-{\bf Counterexample}
-For the following two $4\times 4$ matrices
-$$C=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 0 & 1\\
-1 & 1 & 0 & 0\\
-1 & 1 & 1 & 0
-\end{pmatrix},\quad C'=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 1 &  0\\
-1 & 1 & 0 & 0\\
-1 & 1 & 1 & 0
-\end{pmatrix},$$ 
-we have $CQ\leq C'Q$, but 
-$\rho(C)=2.234\not\leq 2.148= \rho(C')$. 
-This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.
-
 \end{document}

### 2020-11-10 spectral radius of matrix new method/slides/slide102020.tex

--- 2020-11-04 spectral radius of matrix new method/slides/slide101320.tex
@@
-\documentclass[]{beamer}
+\documentclass{beamer}
 %\usetheme{Warsaw}
 \usepackage{times}  % fonts are up to you
-\usepackage{amssymb, amsmath, mathrsfs}
+\usepackage{amssymb, amsmath,amsthm, mathrsfs}
 \usepackage{multicol}
@@
 The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
-        Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
+        %Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
     \end{defn}
@@
     \end{defn}
+\end{frame}
+
+\begin{frame}{\bf Preliminaries}
+    \begin{thm} 
+        %\bf{Perron–Frobenius theorem} \\
+        If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnogative right eigenvector and a corresponding nonnegative left eigenvector.
+    \end{thm}
 \end{frame}
@@
 
-% \begin{frame}
+\begin{frame}
 
@@
     \end{thm}%
-% \end{frame}
+\end{frame}
 
-% \begin{frame}
+\begin{frame}
     % \frametitle{ Proof}
@@
         Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
-% \end{frame}
+\end{frame}
 
@@
 
+\begin{frame}
+\begin{thebibliography}{20}
+\normalsize
+\addcontentsline{toc}{chapter}{Bibliography}
+
+\bibitem{chang}
+Yen-Jen Cheng, {\it  A matrix realization of spectral bounds
+of the spectral radius of a nonnegative matrix}, Ph.D. Thesis, NCTU, 2018.
+
+\bibitem{prn_fros1}
+A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012
+
+\bibitem{prn_fros2}
+R. A. Horn , C. R. Johnson, {\it Matrix analysis}, Cambrigde University Press, 1985.
+
+\end{thebibliography}
+\end{frame}
+
 \end{document}

### 2020-11-10 spectral radius of matrix new method/thesis/article110320.tex

@@
 
-% \topmargin 0pt
+\topmargin 0pt
 
-% \topmargin=-1.5cm
-% \oddsidemargin=0.7cm
-% \textheight=23.5cm
-% \textwidth=15cm
-% \setlength{\baselineskip}{24pt}
-% \renewcommand{\baselinestretch}{1.5} %行距
+\topmargin=-1.5cm
+\oddsidemargin=0.7cm
+\textheight=23.5cm
+\textwidth=15cm
+\setlength{\baselineskip}{24pt}
+\renewcommand{\baselinestretch}{1.5} %行距
 
@@
 \usepackage{ulem}
-% \usepackage{amsfonts}
+\usepackage{amsfonts}
 \usepackage{mathrsfs}
-% \usepackage{tabularx,array}
-% \usepackage{pgf,tikz}
-% \usepackage{blkarray} %line 80-92 Q formula matrix index
+\usepackage{tabularx,array}
+\usepackage{pgf,tikz}
+ \usepackage{blkarray} %line 80-92 Q formula matrix index
 %\usepackage{colortbl}
 \usepackage{enumitem}% enumerate labels   roman
-% \usetikzlibrary{arrows}
+\usetikzlibrary{arrows}
 \setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
-% \XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
-% \XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
-% \title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
-% \author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
-% \date{} %不要日期
+\XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
+\XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
+\title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
+\author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
+\date{} %不要日期
 
@@
 
-\begin{thm}[Perron–Frobenius theorem]\cite{chang}
+\begin{thm}[Perron–Frobenius theorem],\cite{chang}
     If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
@@
 
-The following theorem is from [].\cite{content}
+The following theorem is from [\cite{content}].
 
@@
 Assume that
-\begin{enumerate}[label=(\Roman*)]
+\begin{enumerate}[label=(\roman*)]
     \item \label{pre_thm_em1}  $PCQ\leq PC'Q$;
@@
     eigenvector $v^TP$; and
-    \item \label{pre_thm_em4}$v^TPQu>0.$
+    \item \label{pre_thm_em4} $v^TPQu>0.$
 \end{enumerate}
@@
 \end{thm}
+
 \begin{pof}
     Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm} assumption
-    \ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
-    \ref{pre_thm_em1},    
+    ~\ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
+    ~\ref{pre_thm_em1},    
     \begin{equation}\label{pre1}
@@
     Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption
-     \ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), where $v^TP$ is
+     ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), where $v^TP$ is
     left eigenvector of $C$ for $\lambda$, thus we have
@@
          \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so $\lambda=\lambda'$ by (\ref{pre2}).
+\end{pof}
 
@@
 
-\begin{equation}
-Q=I+E_{kn}=\begin{pmatrix} \label{Q_1}
+\begin{equation} \label{Q_1}
+Q=I+E_{kn}=\begin{pmatrix} 
 1 &  & & &  & 0 \\
@@
 such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-\item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
-\item $v^Tv'>0.$
+\item \label{thm_main:condition_iii}there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+\item \label{thm_main:condition_iv}$v^Tv'>0.$
 \end{enumerate}
@@
 \begin{pof}
-    The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q_1} )$. 
+    The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn}$ in (\ref{Q_1} ). 
     The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this theorem. 
@@
 \begin{defn}[(k,n)-sum]
-        For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
+    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)-sum$ vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
 \end{defn}
 
-    Note that the last column of $C'Q$ is the $(k, n)$-{\it sum} vector of $C'$
+Note that the last column of $C'Q$ is the $(k, n)-sum$ vector of $C'$
 
 \begin{defn}[k-rooted matrix]\label{m_rooted}
-        A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-sum vector are all $k$-rooted except the last column of $C'$.
+    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)-sum$ vector are all $k-rooted$ except the last column of $C'$.
 \end{defn}
@@
     Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-            \begin{enumerate}[label=(\Roman*)]
+        \begin{enumerate}[label=(\roman*)]
             \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
@@
 
-\begin{rmk}
+\begin{rem}
         (i) is immediate from Definition~\ref{m_rooted} and the observation that   
@@
         \end{pmatrix},$$
-\end{rmk}
+\end{rem}
 \end{comment}
@@
     \end{pmatrix}.$$
-    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ \ref{thm_main},
+    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ of theorem~\ref{thm_main},
     Then
@@
 
+\bibitem{content}
+Just as before, {\it What a book}, Fuckes, 2020.
+
 \bibitem{prn_fros1}

### 2020-11-12 spectral radius of matrix new method/thesis/article111720.tex
1112 correct errors on the meeting 1110

--- 2020-11-10 spectral radius of matrix new method/thesis/article110320.tex
@@
 \theoremstyle{plain}
-\newtheorem{thm}{Theorem}[subsection]
+\newtheorem{thm}{Theorem}[section]
 \newtheorem{cor}[thm]{Corollary}
@@
 \newtheorem{ques}[thm]{Question}
-\newtheorem{pof}[thm]{Proof.}
+% \newtheorem{pof}[thm]{Proof.}
 
@@
 
-\begin{defn}
+\begin{defn} \cite{prn_fros1}
     When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$
@@
 
-\begin{thm}[Perron–Frobenius theorem],\cite{chang}
+Perron–Frobenius theorem
+\begin{thm} \cite{chang} \cite{prn_fros2}
     If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
@@
 
-The following theorem is from [\cite{content}].
+The following theorem is from \cite{chang}.
 
@@
 
-\begin{pof}
+\begin{proof}
     Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm} assumption
@@
          \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so $\lambda=\lambda'$ by (\ref{pre2}).
-\end{pof}
+\end{proof}
 
@@
 We use [n-1] as notation of the set of elements from one to n-1, which is {1,2,$...$,n}.
-Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$. We will apply the previous theorem with $P=I$ and
+Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$.
+We will apply the previous theorem \ref{pre_thm} with $P=I$ and
 
@@
 
-\begin{defn}[$k$-rooted vector]
+\begin{defn}%[$k$-rooted vector]
 ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
@@
 
-The following Lemma is immediate from the above definition.
+The following Lemma is immediate from the above definition.%[vector rooted lemma]
 \bigskip
 
-\begin{lem}[vector rooted lemma]\label{lem:rt_vec}
+\begin{lem}\label{lem:rt_vec}
 If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
@@
 \end{enumerate}
-\qed
+% \qed
 \end{lem}
 
-\begin{thm}[Our first result]\label{thm_main}
+Below is our first result, in which the first condition implies the first n-1 columns of C major to
+ the columns of C', and the (k,n)-sum column of C is also major to C'. The second and the third condition
+ suggest that C and C' have nonnegative eigenvectors which are k-rooted. And the forth condition is simplier
+  but with the same meaning with theorem (\ref{pre_thm})
+\begin{thm}\label{thm_main}
     Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
@@
     \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
-\end{enumerate} \qed
+\end{enumerate} %\qed
 \end{thm}
@@
 
-\begin{pof}
-    The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn}$ in (\ref{Q_1} ). 
+\begin{proof}
+    The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn}$ in (\ref{Q_1}). 
     The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this theorem. 
@@
          conditions \ref{thm_main:equ_cond_a},\ref{thm_main:equ_cond_b},\ref{thm_main:equ_cond_c} of this theorem. 
-\end{pof}
+\end{proof}
 
@@
 Motivated by the condition (i) of theorem 2.3, we provide the following two definitions. 
-
-\begin{defn}[(k,n)-sum]
-    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)-sum$ vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
+This is the definition of (k,n)-sum.
+\begin{defn}
+    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-sum vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
 \end{defn}
 
-Note that the last column of $C'Q$ is the $(k, n)-sum$ vector of $C'$
-
-\begin{defn}[k-rooted matrix]\label{m_rooted}
-    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)-sum$ vector are all $k-rooted$ except the last column of $C'$.
+Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$
+Below is the definition of k-rooted matrix.
+\begin{defn}\label{m_rooted}
+    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)$-sum vector are all $k-rooted$ except the last column of $C'$.
 \end{defn}
-
-The following theorem shows that a $k$-rooted matrix has a $k$-rooted eigenvector.
-\begin{lem}\label{lma_m_rooted}
-    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-        \begin{enumerate}[label=(\roman*)]
-            \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-            \item Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
-                for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
-            \item $\rho(C')$ = $\rho(Q^{-1}C'Q)$
-        \end{enumerate}
-\end{lem}
-
-%
 
@@
 
+The following theorem shows that a $k$-rooted matrix has a $k$-rooted eigenvector.
+\begin{lem}\label{lma_m_rooted}
+    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
+        \begin{enumerate}[label=(\roman*)]
+            \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
+            \item Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
+                for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
+            \item $\rho(C')$ = $\rho(Q^{-1}C'Q)$
+        \end{enumerate}
+\end{lem}
+
 \begin{comment}
@@
 \end{comment}   
-
-    \begin{pof}
+\begin{proof}
+    (i)
     and $Q^{-1}C'Q$ is
@@
     \end{pmatrix}.$$
-    \end{pof}
-
-    \begin{pof}
     (ii)
@@
 
-    \end{pof}
+\end{proof}
 
@@
 
-\begin{pof}
+\begin{proof}
     These assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on
@@
        conditions of \ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
-        then $\rho(C') \geq \rho(C)$  \qed
-\end{pof}
+        then $\rho(C') \geq \rho(C)$  %\qed
+\end{proof}
 
@@
 
-\section{References}
+%\section*{References}
 \begin{thebibliography}{20}
@@
 of the spectral radius of a nonnegative matrix}, Ph.D. Thesis, NCTU, 2018.
-
-\bibitem{content}
-Just as before, {\it What a book}, Fuckes, 2020.
 

### 2020-12-02 spectral radius of matrix new method/thesis/matlabData/data_gen.m
120120 update

@@ -1,0 +1,46 @@
+
+out6=cell(1,64);
+for ii = 1:64
+    swr=zeros(1,6);
+    num = ii-1;
+    for jj = 1:6
+        if num < 2
+            swr(jj) = num;
+            break;
+        else
+            swr(jj) = rem(num,2);
+            num = floor(num/2);
+        end
+    end
+    coc = zeros(1,6);
+    for kk = 1:length(swr)
+        coc(7-kk)=swr(kk);
+    end
+    out6{ii} = coc;
+end
+
+for ii = 1:64
+    out6{ii}
+end
+
+box = cell(64,3);
+rads = zeros(2,64);
+for kk = 1:64
+    mode =  [ 0 0 0 0 ; 1 0 0 0 ; 1 1 0 0 ; 1 1 1 0 ];
+    we = 0;
+    for ii = 1:3
+        for jj = ii+1:4
+            we = we + 1;
+            mode(ii,jj) = out6{kk}(we);
+        end
+    end
+    
+    [wr wu] = eig(mode);
+    
+    [rad nthei ] = max(abs(diag(wu)));
+    rads(:,kk)=[rad nthei]';
+    box{kk}{1} = mode;
+    box{kk}{2} = wr;
+    box{kk}{3} = wu;
+    
+end

### 2020-12-02 spectral radius of matrix new method/thesis/matlabData/generate_mat.m

@@ -1,0 +1,87 @@
+%add zero to the matries
+%eigen vec and value calculated, so wrong
+%find some P(row permutation) and Q(column operation)
+
+%10 for each classes
+%C matrix
+C_data3=zeros(3,3,30);
+C_data4=zeros(4,4,30);
+for i = 1:30
+    tmp = randi(15,3);
+    C_data3(:,:,i)=tmp;
+    tmp = randi(15,4);
+    C_data4(:,:,i)=tmp;
+end
+
+%C_big matrix
+C_big3=C_data3;
+C_big4=C_data4;
+%decide how many indices to increase
+%might repeat
+for i = 1:30
+    if i<11
+        N_inc = randi(3); %N_inc : num of increasing indices
+        P_inc = randperm(9,N_inc); %P_inc : place to increase
+        A = C_data3(:,:,i);
+        for k = P_inc
+            A(k)=A(k)+0.3;
+        end
+        C_big3(:,:,i)=A;
+    end
+    if i>10 && i<21
+        N_inc = randi(3)+3; %N_inc : num of increasing indices
+        P_inc = randperm(9,N_inc); %P_inc : place to increase
+        A = C_data3(:,:,i);
+        for k = P_inc
+            A(k)=A(k)+0.3;
+        end
+        C_big3(:,:,i)=A;
+    end
+    if i>20
+        N_inc = randi(3)+6; %N_inc : num of increasing indices
+        P_inc = randperm(9,N_inc); %P_inc : place to increase
+        A = C_data3(:,:,i);
+        for k = P_inc
+            A(k)=A(k)+0.3;
+        end
+        C_big3(:,:,i)=A;
+    end
+end
+
+for i = 1:30
+    if i<11
+        N_inc = randi(4);
+        P_inc = randperm(16,N_inc); %P_inc : place to increase
+        A = C_data4(:,:,i);
+        for k = P_inc
+            A(k)=A(k)+0.3;
+        end
+        C_big4(:,:,i)=A;
+    end
+    if i>10 && i<21
+        N_inc = randi(4)+6;
+        P_inc = randperm(16,N_inc); %P_inc : place to increase
+        A = C_data4(:,:,i);
+        for k = P_inc
+            A(k)=A(k)+0.3;
+        end
+        C_big4(:,:,i)=A;
+    end
+    if i>20
+        N_inc = randi(4)+12;
[…]

### 2020-12-02 spectral radius of matrix new method/thesis/matlabData/temp.m

@@ -1,0 +1,1 @@
+Q=zeros(5,5,20);count = 1;for ii =1:5    for jj = 1:5        Q(:,:,count)=eye(5);        if ii~=jj            Q(ii,jj,count)=1;            count = count + 1;        end    end end

### 2020-12-03 article120120.tex
120320 update on topic and intro

--- 2020-11-12 spectral radius of matrix new method/thesis/article111720.tex
@@
 \usepackage{enumitem}% enumerate labels   roman
+\usepackage{graphicx}
+\graphicspath{{images/}}
 \usetikzlibrary{arrows}
@@
 
-\begin{defn} \cite{prn_fros1}
+\begin{defn} \cite{spec_rad}
     When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$
@@
 
-Perron–Frobenius theorem
-\begin{thm} \cite{chang} \cite{prn_fros2}
+The next theorem is Perron–Frobenius Theorem, which provides a feature of
+ nonnegative eigenvector to nonnegative matrices.
+\begin{thm} \cite{chang} \cite{prn_fros2} \label{thm:Perron_Frobenius}
     If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
-    eigenvalue of $C$ with a corresponding nonnogative right eigenvector and a
+    eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a
     corresponding nonnegative left eigenvector.
@@
 \begin{defn} 
-    Given an undirected graph G, the$\textit{ adjacency matrix}$ of G is the square 
+    Given an directed graph G, the$\textit{ adjacency matrix}$ of G is the square 
     matrix $A = (a_{ij})$ indexed by vertices of G, and
@@
 
-We introduce two matrices $P$ and $Q$ in the following theorem, where $P$ is a permutation
+We introduce two matrices $P$ and $Q$ in the following Theorem, where $P$ is a permutation
  matrix which is multiplied to the left side, and $Q$ is sum of elementary matrix and
@@
 
-The following theorem is from \cite{chang}.
+The following Theorem is from \cite{chang}.
 
@@
 \begin{proof}
-    Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm} assumption
+    Multiplying the nonnegative vector $u$ in Theorem~\ref{pre_thm} assumption
     ~\ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
@@
 \section{Our Method}
-We use [n-1] as notation of the set of elements from one to n-1, which is {1,2,$...$,n}.
-Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$.
-We will apply the previous theorem \ref{pre_thm} with $P=I$ and
+We use $[n-1]$ as notation of the set of elements from one to $n-1$, which is ${1,2,...,n}$.
+Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ 
+appearing in the position $k,n$ of $E_{kn}$. We will apply the previous Theorem \ref{pre_thm} with $P=I$ and
 
@@
 
-\begin{defn}%[$k$-rooted vector]
-~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
+\begin{defn}%[$K$-rooted vector]
+~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $K$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
 \end{defn}
@@
 \begin{enumerate}[label=(\roman*)]
-\item \label{lem:rt_vec:en1}$v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
+\item \label{lem:rt_vec:en1}$v'$ is $K$-rooted  if and only if  $u$ is nonnegative;
 \item $u_k>0$ if and only if $v'_k>v'_n$.
@@
  suggest that C and C' have nonnegative eigenvectors which are k-rooted. And the forth condition is simplier
-  but with the same meaning with theorem (\ref{pre_thm})
+  but with the same meaning with Theorem (\ref{pre_thm})
 \begin{thm}\label{thm_main}
@@
 \item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-\item \label{thm_main:condition_ii} there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+\item \label{thm_main:condition_ii} there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
 such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
@@
 
-% {}
-
 \begin{proof}
     The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn}$ in (\ref{Q_1}). 
-    The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this theorem. 
+    The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this Theorem. 
     Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and
      Lemma~\ref{lem:rt_vec}\ref{lem:rt_vec:en1}. Hence the assumption \ref{pre_thm_em2} of Theorem~\ref{pre_thm} holds. The assumptions \ref{pre_thm_em3} and \ref{pre_thm_em4}
-      of Theorem~\ref{pre_thm} clearly hold by conditions~\ref{thm_main:condition_iii},\ref{thm_main:condition_iv} of this theorem since $P = I$ and
+      of Theorem~\ref{pre_thm} clearly hold by conditions~\ref{thm_main:condition_iii},\ref{thm_main:condition_iv} of this Theorem since $P = I$ and
        $v'= Qu$  Hence $\lambda \leq \lambda' $ by the necessary condition of Theorem~\ref{pre_thm}. Moreover
         $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to
-         conditions \ref{thm_main:equ_cond_a},\ref{thm_main:equ_cond_b},\ref{thm_main:equ_cond_c} of this theorem. 
+         conditions \ref{thm_main:equ_cond_a},\ref{thm_main:equ_cond_b},\ref{thm_main:equ_cond_c} of this Theorem. 
 \end{proof}
 
-We are interested in the matrices $C'$ that have $k$-rooted eigenvectors.
-Motivated by the condition (i) of theorem 2.3, we provide the following two definitions. 
+We are interested in the matrices $C'$ that have $K$-rooted eigenvectors.
+Motivated by the condition (i) of Theorem 2.3, we provide the following two definitions. 
 This is the definition of (k,n)-sum.
@@
 \begin{defn}\label{m_rooted}
-    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)$-sum vector are all $k-rooted$ except the last column of $C'$.
+    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)$-sum vector are all $K$-rooted except the last column of $C'$.
 \end{defn}
@@
 
-The following theorem shows that a $k$-rooted matrix has a $k$-rooted eigenvector.
+The following Theorem shows that a $K$-rooted matrix has a $K$-rooted eigenvector.
 \begin{lem}\label{lma_m_rooted}
@@
         \begin{enumerate}[label=(\roman*)]
-            \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-            \item Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
-                for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
-            \item $\rho(C')$ = $\rho(Q^{-1}C'Q)$
+            \item \label{lma_m_rooted_cond1} $C'$ is a $K$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
+            \item \label{lma_m_rooted_cond2}Assume that $C'$ is $K$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
+                for $\rho(C')$. Then  $C'$ has a $K$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
+            \item \label{lma_m_rooted_cond3}$\rho(C')$ = $\rho(Q^{-1}C'Q)$
         \end{enumerate}
@@
     (ii)
-        By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $k$-rooted.  
+        By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $K$-rooted.  
         Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
@@
 
-\begin{thm}
+\begin{thm}\label{thm:conclusion}
     Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
@@
 \begin{proof}
-    These assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on
-    (\ref{lma_m_rooted});\\
-    calculation:  \\
-       \\
-    by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has
-     a $k$-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same
+    These assumptions are necessary that $PCQ \leq PC'Q$ where $P = I$,$Q = I+E_{kn}$. And $C'$ is $K$-rooted,based on Lemma
+     (\ref{lma_m_rooted}),\\
+    $Q^{-1}C'Q$ = 
+    $$\begin{pmatrix}
+        c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
+        \vdots \\
+        c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
+        c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
+        c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
+        \vdots              & \vdots & \ddots              & \vdots & \vdots \\
+        c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
+    \end{pmatrix}.$$
+    $Q^{-1}C'Q \geq 0$ for that $c'_{kj}\geq c'_{nj}>0$ when $1\leq j\leq n-1$ , $c'_{ij}\geq c_{ij}$ where $C$ is nonnegative,
+    and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$\\
+
+    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$, \\
+    which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ \\
+    And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, \\
+    which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$ ;\\
+    $C'$ is $K$-rooted matrix, then by Lemma (\ref{lma_m_rooted}) Conditions \ref{lma_m_rooted_cond2} and \ref{lma_m_rooted_cond3}, there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+    such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;\\
+    And since $C$ is nonnegative, by Theorem~(\ref{thm:Perron_Frobenius}), which is Perron–Frobenius theorem, we claim there exists
+    $v^T = w^{T}P$, such that $v^T$ is nonnegative left eigenvector of $C$, and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ 
+    is an eigenvalue of $C$ with associated left eigenvector $v^T$; \\
+    Due to $v'$ and $v^T$ are nonnegative, $v^Tv'>0.$, unless they are orthogonal, i.e, $v^Tv'=0$.\\[1ex]
+    Here we can summerize the facts we know so far as the following: \\
+    \begin{enumerate}[label=(\roman*)]
+        \item  $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
+        \item  there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+        such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
+        \item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+        \item $v^Tv'>0.$
+    \end{enumerate}
+    which come from Theorem~(\ref{thm_main}).\\
+    By Lemma~(\ref{l_diag}), for certain $d$, if $C'+dI$ is $K$-rooted, then it has
+    a $K$-rooted eigenvector with its spectral radius $\lambda + d$. $C'$ would share the same
     eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
-       conditions of \ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
+    conditions of Theorem~(\ref{thm_main}), and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
     then $\rho(C') \geq \rho(C)$  %\qed
@@
     \end{pmatrix},$$
+    And its corresponding graph,\cite[sage]{sage}\\
+    \includegraphics{graph_C.PNG} \\
     we choose
@@
     \end{pmatrix}.$$
-    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ of theorem~\ref{thm_main},
+    also, graph,\cite[sage]{sage}\\
+    \includegraphics{graph_Cprime.PNG} \\
+    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ of Theorem~\ref{thm_main},
     Then
-    $\rho(C)\leq \rho(C')$ by previous theorem.
+    $\rho(C)\leq \rho(C')$ by previous Theorem~\ref{thm:conclusion}.
 
@@
 
-\bibitem{prn_fros1}
+\bibitem{spec_rad}
 A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012
@@
 
+\bibitem{sage}
+[Sage] SageMath, the Sage Mathematics Software System (Version 8.7),
+       The Sage Developers, 2019, https://www.sagemath.org.  %sage tutorial
+
 \end{thebibliography}

### 2020-12-03 spectral radius of matrix new method/thesis/introduction&front.tex
120320 update on topic and intro

--- 2020-09-05 spectral radius of matrix new method/thesis/thesis_form.tex
@@
 \begin{document}
+
 %封面
@@
 
-{ \Huge TBA}~\\~\\
+{ \Huge TBA有向圖譜半徑之簡易估算方法}~\\~\\
 
@@
 \begin{tabular}{rcl}
-研究生&：&XXX\\
+研究生&：&陳科翰\\
 指導教授&：&翁志文~教授
@@
 \bigskip\bigskip
-{ \Large 中~~華~~民~~國~~一~~百~~零~~八~~年~~一~~月 }
+{ \Large 中~~華~~民~~國~~一~~百~~ㄧ~~十~~年~~一~~月 }
 \large
@@
 \Large
-TBA\\
+TBA A simple method on estimating spectral radius for some direted graphs\\
 待輸入 \\~\\
 \begin{tabular}{lccr}
-Student: XXX  &&~~~& Advisor: Chih-Wen Weng\\
+Student: Ko-Han Chen  &&~~~& Advisor: Chih-Wen Weng\\
 研究生:陳科翰　 &&~~~& 指導教授：翁志文~教授
@@
 
-January 2019
+January 2021
 
@@
 
- 中~~華~~民~~國~~一~~百~~零~~八~~年~~一~~月 }
+ 中~~華~~民~~國~~一~~百~~ㄧ~~十~~年~~一~~月 }
 \end{center}
 \pagebreak
+
+\label{abstract}
+
 %中文摘要
@@
 { \large
-Student: XXX  ~~~~~ Advisor: Chih-Wen Weng \\
+Student: Ko-Han Chen  ~~~~~ Advisor: Chih-Wen Weng \\
 \Large
@@
 \pagebreak
+
 \renewcommand{\baselinestretch}{1.2}
@@
 \pagebreak
+
+\label{Introduction}
 % Introduction
@@
 \pagenumbering{arabic}
-
-\chapter{Preliminaries}
-
-\begin{defn}
-Spectral radius of a matrix $C$ is the largest absolute value of real eigenvalue of $C$. And here we are interested in spectral radius of the adjacency matrix for some simple graph.
-\end{defn}
-
-\begin{defn}
-    Eigenvalue of a matrix $C$ corresponds to an eigenvector $u$, where $u$ and its eigenvalue $\lambda $  satisfies $Cu = \lambda u$.
-\end{defn}
-
-    We introduce a notation of sub-matrix, which is taken from some columns and some rows of a matrix.
-
-    \begin{defn}We use $C[\alpha|\beta]$ to denote the sub-matrix of rows $\alpha$ of $C$ and columns $\beta$ of $C$ and $C(\alpha|\beta)$ is the sub-matrix of rows $[n]$ - $\alpha$ of $C$ and columns $[n] - \beta$ of $C$.
-    The bracket [] and parentheses () can be used together is the notation of sub-matrix, such as $C[k|e)$ or $C(k|e]$.
-\end{defn}
-
-\begin{thm}
-        If $C$ is nonnegative square matrix, then the following holds. \\
-        The spectral radius $\rho(C)$ is an eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a corresponding nonnegative left eigenvector.
-\end{thm}
-
-The following theorem is from [].
-
-\begin{thm}
- Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n\times n$ matrices.
-Assume that
-\begin{enumerate}
-\item[(i)]    $PCQ\leq PC'Q$;
-\item[(ii)]  there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $Qu$;
-\item[(iii)] there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$
-such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector $v^TP$; and
-\item[(iv)] $v^TPQu>0.$
-\end{enumerate}
- Then $\lambda\leq \lambda'$.
-    Moreover, $\lambda=\lambda'$
-if and only if
-    \begin{equation*}
-        \label{e3}
-(PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n \hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
-\end{equation*}
-\end{thm}
-
-\begin{proof}
-            Multiplying the nonnegative vector $u$ in (ii) to the right of both terms of  (i),
-        \begin{equation}
-            \label{e1}
-            PCQu\leq PC'Qu=\lambda'PQu.
-        \end{equation}
-        Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the left of all terms  in (\ref{e1}), we have
-        \begin{equation}
-            \label{e2}
-            \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
-        \end{equation}
-        Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $\lambda\leq \lambda'$ and finish the proof of the first part.
-
-        Assume that $\lambda=\lambda'$, so the inequality in (\ref{e2}) is an equality.
-Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with $u_j\not=0.$
-         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
-            $\lambda=\lambda'$ by (\ref{e2}). \qed
-
- \end{proof}
-
-\chapter{Our result}
-
- Throughout fix $k\in [n-1]$.
-Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the  position $k,n$ of $E_{kn}$.
-We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
-1 &  & & &  & 0 \\
- & 1 &  &      &  &  \\
- &  & \ddots & &  & 1 \\
- &  &        & &  &  \\
-  &  & & & 1 &  \\
-0 &  & & &  & 1 \\
-\end{pmatrix}.$$
-\begin{defn}\label{v_rooted}
- ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
-\end{defn}
-\bigskip
-
-The following Lemma is immediate from the above definition.
-\bigskip
-
-\begin{lem}
-If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
-\begin{enumerate}
-\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
-\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
-\end{enumerate}
-\qed
-\end{lem}
-
-\begin{thm} \label{thm_main}
-    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
-Assume that
-\begin{enumerate}
-\item[(i)]   $C[-|n)\leq C'[-|n)$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-\item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
-such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
-\item[(iv)] $v^Tv'>0.$
-\end{enumerate}
- Then $\lambda\leq \lambda'$.
-Moreover, $\lambda=\lambda'$
-if and only if
-\begin{enumerate}
-\item[(a)] $c_{ik}+c_{in}=c'_{ik}+c'_{in}$\qquad for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
-\item[(b)]
-$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
-\end{enumerate} \qed
-\end{thm}
-
-\begin{defn}
-For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
-\end{defn}
-
-\begin{defn}\label{m_rooted}
-A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if its  columns and its $(k, n)$-sum vector are all $k$-rooted except the last column of $C'$.
-\end{defn}
-
-\begin{thm}
-Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-    \begin{enumerate}
-        \item[(i)]$C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-        \item[(ii)]$C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$ as an eigenvalue. $u$ is a nonnegative eigenvector of $Q^{-1}C'Q$ for $\rho(C')$.
-        \item[(iii)] $\rho(C')$ = $\rho(Q^{-1}C'Q)$
-    \end{enumerate}
-\end{thm}
-
-\begin{proof}
-(i) is immediate from Definition~\ref{m_rooted} and the observation that
-$$Q^{-1}=I-E_{kn}=\begin{pmatrix}
-1 &  & & &  & 0 \\
- & 1 &  &      &  &  \\
- &  & \ddots & &  & -1 \\
- &  &        & &  &  \\
-  &  & & & 1 &  \\
-0 &  & & &  & 1 \\
-\end{pmatrix},$$
-and $Q^{-1}C'Q$ is
-$$\begin{pmatrix}
-c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
-\vdots \\
-c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
-c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
-c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
-\vdots              & \vdots & \ddots              & \vdots & \vdots \\
-c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
-\end{pmatrix}.
-$$
-
-(ii)
-By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted.
-Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
-$C'Qu=\rho(C')Qu$.
-
-(iii)
-Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.
-
-\end{proof}
-
-\begin{lem}\label{l_diag}
-If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
-the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
-\end{lem}
-
-\chapter{Conclusion}
-
-\begin{thm}
-Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
-such that $c'_{ij}\geq c_{ij}$, and then choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$ and $c'_{kj}\geq c'_{nj}>0$, and
-let $c'_{in}:=r'_i-c'_{ik}$ with $r'_k \geq r'_n$.
-Whereas $c'_{kk}\geq c'_{nk}$ is not necessary.
-Then the $n\times n$ matrix $C'=(c'_{ij})$ has a positive $k$-rooted eigenvector for $\rho(C')$ and $\rho(C)\leq \rho(C')$.
-\end{thm}
-
-{\bf Proof}
-
-The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by \ref{l_diag}, For certain d, if C'+d*I is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$.
-C' would share the same eigenvector with C'+d*I and has eigenvalue $\lambda$.
-So C'+d*I and C+d*I meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + d*I) \geq \rho(C +d*I)$ and then $\rho(C') \geq \rho(C)$  \qed
-
-{Example}
-For the following $4\times 4$ matrix
-$$C=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 0 & 1\\
-1 & 1 & 0 & 1\\
-1 & 1 & 1 & 0
-\end{pmatrix},$$
-we choose
-$$C'=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 1 &  0\\
-1 & 1 & 0 & 1\\
-1 & 1 & 1 & 0
-\end{pmatrix}.$$
-Then
-$\rho(C)\leq \rho(C')$ by previous theorem.
-
-{\bf Counterexample}
-For the following two $4\times 4$ matrices
-$$C=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 0 & 1\\
-1 & 1 & 0 & 0\\
-1 & 1 & 1 & 0
-\end{pmatrix},\quad C'=\begin{pmatrix}
-0 & 0 & 1 & 1\\
-1 & 0 & 1 &  0\\
-1 & 1 & 0 & 0\\
-1 & 1 & 1 & 0
-\end{pmatrix},$$
-we have $CQ\leq C'Q$, but
-$\rho(C)=2.234\not\leq 2.148= \rho(C')$.
-This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.
-
-\newpage
-\begin{thebibliography}{20}
-\normalsize
-\addcontentsline{toc}{chapter}{Bibliography}
-\bibitem{catalan}
-\newblock{James Haglund, The $q$,$t$-Catalan Numbers and the Space of Diagonal Harmonics: With an Appendix on the Combinatorics of Macdonald Polynomials},
-\newblock{\it University Lectures Series}, vol. 41, 2008
-
-\bibitem{combinatorics}
-\newblock{J.H. van Lint and R.M. Wilson, A Course in Combinatorics, second edition},
-\newblock{\it} Cambridge University Press, New York, 2001.
-
-\bibitem{euler}
-\newblock{H. W. Gould, Euler's formula nth differences of powers},
-\newblock{\it The American Mathematical Monthly }, vol. 85, No. 6, 450-467,1978
-
-\bibitem{rook}
-\newblock{Feryal Alayomt and Nicholas Krzywonos, Rook polynomials in three and higher dimensions},
-\newblock{\it }, 2009
-
-\bibitem{brualdi}
-\newblock{Richard A. Brualdi, Introductory Combinatorics, fifth edition},
-\newblock{\it },  Prentice Hall, New Jersey, 2009.
-
-\bibitem{qanalogue}
-\newblock{Bruce E. Sagan, Congruence Properties of $q$-Analogs},
-\newblock{\it Advances in Mathematics}, 95, 127-143,1992
-
-\bibitem{lagrange}
-\newblock{Eric W. Weisstein, Lagrange Interpolating Polynomial}, \newblock{MathWorld}
-
-\bibitem{9}
-\newblock{郭子翔,一個新恆等式的發現與研究}, preprint.
-
-\end{thebibliography}
+Based on the theory and try to lease on the condition and find out the corresponding condition to the theory and adopt the theory and condition.
 

### 2020-12-04 spectral radius of matrix new method/thesis/article120420.tex
checked update 120420

--- 2020-12-03 article120120.tex
@@
 \begin{document}
+
+%封面
+
+\thispagestyle{empty}
+\begin{center}
+{ \Huge 國~~~~立~~~~交~~~~通~~~~大~~~~學}~\\~\\
+
+\bigskip
+
+{ \Huge 應~用~數~學~系}~\\~\\
+
+\bigskip
+
+{ \Huge 碩~~士~~論~~文}~\\~\\
+
+\bigskip \bigskip\bigskip\bigskip\bigskip\bigskip
+
+{ \Huge 有向圖譜半徑之簡易估算方法}~\\~\\
+
+\bigskip
+
+{ \Huge A simple method on estimating spectral radius for some direted graphs}~\\~\\
+~\\~\\~\\~\\~\\
+\bigskip \bigskip\bigskip\bigskip\bigskip\bigskip
+\bigskip \bigskip\bigskip\bigskip\bigskip\bigskip
+\bigskip\bigskip\bigskip
+
+{ \Large
+\begin{tabular}{rcl}
+研究生&：&陳科翰\\
+指導教授&：&翁志文~教授
+\end{tabular} }
+
+\bigskip\bigskip
+{ \Large 中~~華~~民~~國~~一~~百~~ㄧ~~十~~年~~一~~月 }
+\large
+\end{center}
+\pagebreak
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\renewcommand{\baselinestretch}{2} %行距
+\thispagestyle{empty}
+\begin{center}
+{
+\Large
+有向圖譜半徑之簡易估算方法\\
+A simple method on estimating spectral radius for some direted graphs\\~\\
+\begin{tabular}{lccr}
+Student: Ko-Han Chen  &&~~~& Advisor: Chih-Wen Weng\\
+研究生:陳科翰　 &&~~~& 指導教授：翁志文~教授
+\end{tabular}
+}~\\
+
+\bigskip
+
+\renewcommand{\baselinestretch}{1} %行距
+
+{ \LARGE 國~~~~立~~~~交~~~~通~~~~大~~~~學}\\~\\
+{ \LARGE 應~用~數~學~系}\\~\\
+{ \LARGE 碩~~士~~論~~文}\\~\\~\\~\\~\\
+\renewcommand{\baselinestretch}{1} %行距
+{ \large A Thesis
+
+Submitted to Department of Applied Mathematics
+
+College of Science
+
+National Chiao Tung University
+
+in Partial Fulfillment of Requirements
+
+for the Degree of Master
+
+in Applied Mathematics
+\bigskip \medskip
+
+January 2021
+
+Hsinchu, Taiwan, Republic of China \bigskip \medskip
+
+ 中~~華~~民~~國~~一~~百~~ㄧ~~十~~年~~一~~月 }
+\end{center}
+\pagebreak
+
+\label{abstract}
+
+%中文摘要
+\pagenumbering{roman}
+\begin{center}
+{  \LARGE
+有向圖譜半徑之簡易估算方法
+\bigskip\bigskip\bigskip
+
+研究生：陳科翰  ~~~~~~~~~~ 指導教授：翁志文~教授 \\
+國立交通大學  \\
+\bigskip
+應用數學系
+\bigskip\bigskip\bigskip\bigskip
+} \\~\\~\\~\\
+\addcontentsline{toc}{section}{Abstract (in Chinese)}
+{\large 摘~要}
+\end{center}
+ \bigskip
+
+ 找到一個簡單而且傑出的方法來估算譜半徑，試著縮小誤差，必定存在一個方法理性地證明它。我知道譜半徑是區分
+ 圖中點連線關係的重要指標，所以找一個簡單的方法來估算譜半徑是很有意義的。有了穩固的證明，我們可以估計連
+ 接矩陣的最小誤差譜半徑，並且找出存在這樣的上下界的充分條件。\\
+\bigskip
+
+\noindent 關鍵詞：譜半徑，簡易方法，有向圖，估算。
+\pagebreak
+
+%英文摘要
+\begin{center}{\LARGE
+A simple method on estimating spectral radius for some direted graphs
+\bigskip\bigskip\bigskip}
+
+{ \large
+Student: Ko-Han Chen  ~~~~~ Advisor: Chih-Wen Weng \\
+\Large
+
+Department ~of~ Applied ~Mathematics
+\bigskip
+
+National~ Chiao ~Tung~ University
+\bigskip\bigskip\bigskip\bigskip}\\
+{\large Abstract}
+\end{center}
+
+%\begin{abstract}
+\addcontentsline{toc}{section}{Abstract (in English)}
+Find a simple and excellent executable method
+ to estimate spectral radius, try to minimize the bios and there is a way to prove it sensible.
+ I know that spectral radius is an important index to specify the relation of connected vertices in
+  the graphs, so it is meanful to find a simple method to estimate spectral readius. With a solid proof,
+   we can estimate the spectral radius of an adjacent matrix with minimal error and find out the sufficent
+  condition on the existence of such bound.
+
+\bigskip
+
+\noindent {\bf Keywords}: spectral radius, simple method, directed graphs, estimation
+%\end{abstract}
+\pagebreak
+
+\renewcommand{\baselinestretch}{1.2}
+% 目錄
+\large
+\tableofcontents
+
+\pagebreak
+
+\label{Introduction}
+% Introduction
+
+\section{Introduction}
+\normalsize
+\pagenumbering{arabic}
 
@@
 \normalsize
-\addcontentsline{toc}{chapter}{Bibliography}
+\addcontentsline{toc}{section}{Bibliography}
 
@@
 \bibitem{sage}
-[Sage] SageMath, the Sage Mathematics Software System (Version 8.7),
-       The Sage Developers, 2019, https://www.sagemath.org.  %sage tutorial
+[Sage] SageMath, the Sage Mathematics Software System (Version 9.2),
+       The Sage Developers, 2020, https://www.sagemath.org.  %sage tutorial
 

### 2020-12-04 spectral radius of matrix new method/thesis/introduction&front.tex
checked update 120420

@@
 
-{ \Huge TBA有向圖譜半徑之簡易估算方法}~\\~\\
+{ \Huge 有向圖譜半徑之簡易估算方法}~\\~\\
 
@@
 
-{ \Huge 待輸入}~\\~\\
+{ \Huge A simple method on estimating spectral radius for some direted graphs}~\\~\\
 ~\\~\\~\\~\\~\\
@@
 \Large
-TBA A simple method on estimating spectral radius for some direted graphs\\
-待輸入 \\~\\
+有向圖譜半徑之簡易估算方法\\
+A simple method on estimating spectral radius for some direted graphs\\~\\
 \begin{tabular}{lccr}
@@
 {  \LARGE
-待輸入
+有向圖譜半徑之簡易估算方法
 \bigskip\bigskip\bigskip
@@
 
-待輸入\\
+ 找到一個簡單而且傑出的方法來估算譜半徑，試著縮小誤差，必定存在一個方法理性地證明它。我知道譜半徑是區分
+ 圖中點連線關係的重要指標，所以找一個簡單的方法來估算譜半徑是很有意義的。有了穩固的證明，我們可以估計連
+ 接矩陣的最小誤差譜半徑，並且找出存在這樣的上下界的充分條件。\\
 \bigskip
 
-\noindent 關鍵詞：待輸入。
+\noindent 關鍵詞：譜半徑，簡易方法，有向圖，估算。
 \pagebreak
@@
 \begin{center}{\LARGE
-TBA
+A simple method on estimating spectral radius for some direted graphs
 \bigskip\bigskip\bigskip}
@@
 \addcontentsline{toc}{chapter}{Abstract (in English)}
+Find a simple and excellent executable method
+ to estimate spectral radius, try to minimize the bios and there is a way to prove it sensible.
+ I know that spectral radius is an important index to specify the relation of connected vertices in
+  the graphs, so it is meanful to find a simple method to estimate spectral readius. With a solid proof,
+   we can estimate the spectral radius of an adjacent matrix with minimal error and find out the sufficent
+  condition on the existence of such bound.
 
-TBA
 \bigskip
 
-\noindent {\bf Keywords}: TBA
+\noindent {\bf Keywords}: spectral radius, simple method, directed graphs, estimation
 %\end{abstract}
@@
 \pagenumbering{arabic}
-Based on the theory and try to lease on the condition and find out the corresponding condition to the theory and adopt the theory and condition.
 

### 2020-12-08 spectral radius of matrix new method/thesis/mistake_testing.tex

--- 2020-11-12 spectral radius of matrix new method/thesis/article111720.tex
@@
 
-\section{Preliminaries}
-
-Let $\mathbb{R}$ and $\mathbb{C}$ denote the
- field of real numbers and complex numbers respectively.
-
-\begin{defn}       
-Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a
- nonzero column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ 
-of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
-
-%Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
-\end{defn}
-
-\begin{defn} \cite{prn_fros1}
-    When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$
-        of $C$ is defined by 
-        $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
-    where $|\lambda|$ is the magnitude of complex number $\lambda.$
-\end{defn}
-
-Perron–Frobenius theorem
-\begin{thm} \cite{chang} \cite{prn_fros2}
-    If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
-    eigenvalue of $C$ with a corresponding nonnogative right eigenvector and a
-    corresponding nonnegative left eigenvector.
-\end{thm}
-
-We are interested in spectral radius of the following matrix associated with a simple graph.
-
-\begin{defn} 
-    Given an undirected graph G, the$\textit{ adjacency matrix}$ of G is the square 
-    matrix $A = (a_{ij})$ indexed by vertices of G, and
-     \[a_{ij} =\begin{cases} 
-        1, \text{if $i$ is adjacent to $j$}, \\
-        0, \text{otherwise.}
-            \end{cases}
-     \]
-\end{defn}
-
-\begin{defn}
-Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
- radius of the adjacency matrix of G.
-\end{defn}
-
-    We introduce a notation of submatrix, which is taken from some columns and some rows of a
-     matrix.
-
-\begin{defn}
-    For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column 
-    indices of $C$ respectively,  We use $C[\alpha|\beta]$ to denote the 
-    submatrix of $C$ with size $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$
-    and $j\in\beta$,
-\end{defn}
-
-We introduce two matrices $P$ and $Q$ in the following theorem, where $P$ is a permutation
- matrix which is multiplied to the left side, and $Q$ is sum of elementary matrix and
- certain binary matrix. In which $P$ generalize row permutation on cases of $C$
- matrix,and $Q$ is the transform from $C'$ to C', which is the first n-1 columns
-  and sum of certain columns. We aim to find C' such that $C'$ majors $C$,i.e. $C\leq C'$
-
-The following theorem is from \cite{chang}.
-
 \begin{thm}\label{pre_thm}
@@
 
-\begin{proof}
-    Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm} assumption
-    ~\ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
-    ~\ref{pre_thm_em1},    
-    \begin{equation}\label{pre1}
-       PCQu\leq PC'Qu=\lambda'PQu.
-    \end{equation}
-    Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption
-     ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), where $v^TP$ is
-    left eigenvector of $C$ for $\lambda$, thus we have
-    \begin{equation}\label{pre2}
-        \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
-    \end{equation}
-        Now delete the positive term $v^TPQu$ by assumption \ref{pre_thm_em4} to obtain
-        $\lambda\leq \lambda'$ and finish the proof of the first part.
-        Assume that $\lambda=\lambda'$, so the inequality in (\ref{pre2}) is an equality.
-        Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence,
-        $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with
-        $u_j\not=0.$ Conversely, (\ref{pre0}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=
-         \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so $\lambda=\lambda'$ by (\ref{pre2}).
-\end{proof}
-
 \section{Our Method}
@@
 We will apply the previous theorem \ref{pre_thm} with $P=I$ and
-
-\begin{equation} \label{Q_1}
-Q=I+E_{kn}=\begin{pmatrix} 
-1 &  & & &  & 0 \\
- & 1 &  &      &  &  \\
- &  & \ddots & &  & 1 \\
- &  &        & &  &  \\
-  &  & & & 1 &  \\
-0 &  & & &  & 1 \\
-\end{pmatrix}.  
-\end{equation}
-
-\begin{defn}%[$k$-rooted vector]
-~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
-\end{defn}
-\bigskip
-
-The following Lemma is immediate from the above definition.%[vector rooted lemma]
-\bigskip
-
-\begin{lem}\label{lem:rt_vec}
-If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
+\begin{lem}\label{lma_m_rooted}
+    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
         \begin{enumerate}[label=(\roman*)]
-\item \label{lem:rt_vec:en1}$v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
-\item $u_k>0$ if and only if $v'_k>v'_n$.
+            \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
+            \item Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
+                for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
+            \item $\rho(C')$ = $\rho(Q^{-1}C'Q)$
         \end{enumerate}
-% \qed
 \end{lem}
 
-Below is our first result, in which the first condition implies the first n-1 columns of C major to
- the columns of C', and the (k,n)-sum column of C is also major to C'. The second and the third condition
- suggest that C and C' have nonnegative eigenvectors which are k-rooted. And the forth condition is simplier
-  but with the same meaning with theorem (\ref{pre_thm})
+\begin{lem}\label{l_diag}   %end of label
+    If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
+    the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
+    \end{lem}
+
 \begin{thm}\label{thm_main}
@@
 \end{thm}
-%
-
-% {}
-
-\begin{proof}
-    The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn}$ in (\ref{Q_1}). 
-    The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this theorem. 
-    Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and
-     Lemma~\ref{lem:rt_vec}\ref{lem:rt_vec:en1}. Hence the assumption \ref{pre_thm_em2} of Theorem~\ref{pre_thm} holds. The assumptions \ref{pre_thm_em3} and \ref{pre_thm_em4}
-      of Theorem~\ref{pre_thm} clearly hold by conditions~\ref{thm_main:condition_iii},\ref{thm_main:condition_iv} of this theorem since $P = I$ and
-       $v'= Qu$  Hence $\lambda \leq \lambda' $ by the necessary condition of Theorem~\ref{pre_thm}. Moreover
-        $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to
-         conditions \ref{thm_main:equ_cond_a},\ref{thm_main:equ_cond_b},\ref{thm_main:equ_cond_c} of this theorem. 
-\end{proof}
-
-We are interested in the matrices $C'$ that have $k$-rooted eigenvectors.
-Motivated by the condition (i) of theorem 2.3, we provide the following two definitions. 
-This is the definition of (k,n)-sum.
-\begin{defn}
-    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-sum vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
-\end{defn}
-
-Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$
-Below is the definition of k-rooted matrix.
-\begin{defn}\label{m_rooted}
-    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)$-sum vector are all $k-rooted$ except the last column of $C'$.
-\end{defn}
-
-\begin{rem}
-
-    $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
-    1 &  & & &  & 0 \\
-    & 1 &  &      &  &  \\
-    &  & \ddots & &  & -1 \\
-    &  &        & &  &  \\
-    &  & & & 1 &  \\
-    0 &  & & &  & 1 \\
-    \end{pmatrix}.$$
-
-    The matrix $C'Q$ is
-    $$\begin{pmatrix}
-    c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
-    \vdots \\
-    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
-    c'_{k1} & c'_{k2} &\cdots      & c'_{kn-1} & c'_{kk}+c'_{kn}\\
-    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
-    \vdots              & \vdots & \ddots              & \vdots & \vdots \\
-    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
-    \end{pmatrix}.
-    $$
-\end{rem}
-
-The following theorem shows that a $k$-rooted matrix has a $k$-rooted eigenvector.
-\begin{lem}\label{lma_m_rooted}
-    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-        \begin{enumerate}[label=(\roman*)]
-            \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-            \item Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
-                for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
-            \item $\rho(C')$ = $\rho(Q^{-1}C'Q)$
-        \end{enumerate}
-\end{lem}
-
-\begin{comment}
-
-\begin{rem}
-        (i) is immediate from Definition~\ref{m_rooted} and the observation that   
-        $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
-        1 &  & & &  & 0 \\
-         & 1 &  &      &  &  \\
-         &  & \ddots & &  & -1 \\
-         &  &        & &  &  \\
-          &  & & & 1 &  \\
-        0 &  & & &  & 1 \\
-        \end{pmatrix},$$
-\end{rem}
-\end{comment}   
-\begin{proof}
-    (i)
-    and $Q^{-1}C'Q$ is
-    $$\begin{pmatrix}
-    c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
-    \vdots \\
-    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
-    c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
-    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
-    \vdots              & \vdots & \ddots              & \vdots & \vdots \\
-    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
-    \end{pmatrix}.$$
-    (ii)
-        By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $k$-rooted.  
-        Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
-        $Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
-        $C'Qu=\rho(C')Qu$.
-
-    (iii)
-    Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.
-
-\end{proof}
-
-\begin{lem}\label{l_diag}   %end of label
-If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
-the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
-\end{lem}
 
@@
 \begin{proof}
-    These assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on
+    These assumptions are necessary that $PCQ \leq PC'Q$, and C' is $K$-rooted,based on Lemma
     (\ref{lma_m_rooted});\\
-    calculation:  \\
-       \\
+    where $Q^{-1}C'Q$ = 
+    $$\begin{pmatrix}
+    c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
+    \vdots \\
+    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
+    c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-c'_{nn}\\
+    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
+    \vdots              & \vdots & \ddots              & \vdots & \vdots \\
+    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
+    \end{pmatrix}.$$
+    $Q^{-1}C'Q \geq 0$ for that $c'_{kj}\geq c'_{nj}>0$ when $1\leq j\leq n-1$ , $c'_{ij}\geq c_{ij}$ where $C$ is nonnegative,
+    and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$\\2ed
+
+    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$, \\
+    which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ \\
+    And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, \\
+    which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$ \\2ed
+    C' is $K$-rooted matrix, then by Lemma (\ref{lma_m_rooted}), there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+    such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
+
+    \begin{enumerate}[label=(\roman*)]
+        \item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
+        \item \label{thm_main:condition_ii} there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+        such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
+        \item \label{thm_main:condition_iii}there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+        \item \label{thm_main:condition_iv}$v^Tv'>0.$
+        \end{enumerate}
     by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has
@@
 
-\subsection{Example}
-    For the following $4\times 4$ matrix
-    $$C=\begin{pmatrix}
-    0 & 0 & 1 & 1\\
-    1 & 0 & 0 & 1\\
-    1 & 1 & 0 & 1\\
-    1 & 1 & 1 & 0
-    \end{pmatrix},$$
-    we choose
-    $$C'=\begin{pmatrix}
-    0 & 0 & 1 & 1\\
-    1 & 0 & 1 &  0\\
-    1 & 1 & 0 & 1\\
-    1 & 1 & 1 & 0
-    \end{pmatrix}.$$
-    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ of theorem~\ref{thm_main},
-    Then
-    $\rho(C)\leq \rho(C')$ by previous theorem.
-
-\subsection{Counterexample}
-    For the following two $4\times 4$ matrices
-    $$C=\begin{pmatrix}
-    0 & 0 & 1 & 1\\
-    1 & 0 & 0 & 1\\
-    1 & 1 & 0 & 0\\
-    1 & 1 & 1 & 0
-    \end{pmatrix},\quad C'=\begin{pmatrix}
-    0 & 0 & 1 & 1\\
-    1 & 0 & 1 &  0\\
-    1 & 1 & 0 & 0\\
-    1 & 1 & 1 & 0
-    \end{pmatrix},$$ 
-    specify $n$=4, $k$=3 in $Q = I +E_{kn} = I + E_{34}$  
-    $$CQ=\begin{pmatrix}
-    0 & 0 & 1 & 2\\
-    1 & 0 & 0 & 1\\
-    1 & 1 & 0 & 0\\
-    1 & 1 & 1 & 1
-    \end{pmatrix},\quad C'Q=\begin{pmatrix}
-    0 & 0 & 1 & 2\\
-    1 & 0 & 1 & 1\\
-    1 & 1 & 0 & 0\\
-    1 & 1 & 1 & 1
-    \end{pmatrix},$$
-
-    we have $CQ\leq C'Q$, but 
-    $\rho(C)=2.234\not\leq 2.148= \rho(C')$. 
-    This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.
-
-%\section*{References}
-\begin{thebibliography}{20}
-\normalsize
-\addcontentsline{toc}{chapter}{Bibliography}
-
-\bibitem{chang}
-Yen-Jen Cheng, {\it  A matrix realization of spectral bounds
-of the spectral radius of a nonnegative matrix}, Ph.D. Thesis, NCTU, 2018.
-
-\bibitem{prn_fros1}
-A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012
-
-\bibitem{prn_fros2}
-R. A. Horn , C. R. Johnson, {\it Matrix analysis}, Cambrigde University Press, 1985.
-
-\end{thebibliography}
-
 \end{document}

### 2020-12-09 spectral radius of matrix new method/thesis/article120920.tex
120920 whole article

--- 2020-12-04 spectral radius of matrix new method/thesis/article120420.tex
@@
 
- 找到一個簡單而且傑出的方法來估算譜半徑，試著縮小誤差，必定存在一個方法理性地證明它。我知道譜半徑是區分
- 圖中點連線關係的重要指標，所以找一個簡單的方法來估算譜半徑是很有意義的。有了穩固的證明，我們可以估計連
- 接矩陣的最小誤差譜半徑，並且找出存在這樣的上下界的充分條件。\\
+ 我知道譜半徑是區分圖中點連線關係的重要指標，所以找一個簡單的方法來估算譜半徑
+ 是很有意義的。一個簡單而且傑出估算譜半徑的方法有一些特徵。首先，誤差被極小化
+ ，第二必定存在一個方法正確理性地證明它。列舉這些方法並正確證明會讓這方法穩固
+ 且可信靠。在估計的領域裡，最好思考過所有的因素，再根據目標，取用估計譜半徑的
+ 方法，以利之後分析圖的連接矩陣，與其連通性有關的矩陣。
+ \\
 \bigskip
@@
 \addcontentsline{toc}{section}{Abstract (in English)}
-Find a simple and excellent executable method
- to estimate spectral radius, try to minimize the bios and there is a way to prove it sensible.
 I know that spectral radius is an important index to specify the relation of connected vertices in
-  the graphs, so it is meanful to find a simple method to estimate spectral readius. With a solid proof,
-   we can estimate the spectral radius of an adjacent matrix with minimal error and find out the sufficent
-  condition on the existence of such bound.
+ the graphs, so it is meanful to find a simple method to estimate spectral readius. A simple and excellent
+ executable method to estimate spectral radius has some features. First, the bios is minimized, and second
+ there must be a way to prove it sensible. Enumerate these factors and prove it correctly would make this method
+ solid and reliable. In the field of estimation, it's better to go through all the factors, and base on one's goal
+ to apply the methods of estimating spectral radius before analyzing the adjacency matrix of the graphs, which is
+ related to the connectness of the graph.
 
@@
 
-\section{Preliminaries}
-
 Let $\mathbb{R}$ and $\mathbb{C}$ denote the
@@
 of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
-
 %Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
@@
 \end{defn}
-
-The next theorem is Perron–Frobenius Theorem, which provides a feature of
- nonnegative eigenvector to nonnegative matrices.
-\begin{thm} \cite{chang} \cite{prn_fros2} \label{thm:Perron_Frobenius}
-    If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
-    eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a
-    corresponding nonnegative left eigenvector.
-\end{thm}
 
@@
 \begin{defn}
-Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
+    Given a directed graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
      radius of the adjacency matrix of G.
 \end{defn}
+
+\section{Preliminaries}
+
+The next theorem is Perron–Frobenius Theorem, which provides a feature of
+ nonnegative eigenvector to nonnegative matrices.
+\begin{thm} \cite{chang} \cite{prn_fros2} \label{thm:Perron_Frobenius}
+    If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
+    eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a
+    corresponding nonnegative left eigenvector.
+\end{thm}
 

### 2020-12-09 spectral radius of matrix new method/slides/conclusion_dec.tex

@@
 
+Let $\mathbb{R}$ and $\mathbb{C}$ denote the field of real numbers and complex numbers respectively.
+
+\begin{defn}
+    Let $C$ be an $n \times n$ real matrix, and $u \in \mathbb{R}^n$ be a nonzero column vector.
+The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
+
+\end{defn}
+
+\begin{defn}
+
+When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$ of $C$ is defined by
+$$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
+where $|\lambda|$ is the magnitude of complex number $\lambda.$
+\end{defn}
+
 \end{frame}

### 2020-12-15 spectral radius of matrix new method/thesis/article121420.tex
121620 update

--- 2020-12-04 spectral radius of matrix new method/thesis/article120420.tex
@@
-\documentclass{article}
+\documentclass[12pt, a4paper]{article}
 
-\topmargin 0pt
-
-\topmargin=-1.5cm
-\oddsidemargin=0.7cm
-\textheight=23.5cm
-\textwidth=15cm
-\setlength{\baselineskip}{24pt}
-\renewcommand{\baselinestretch}{1.5} %行距
+\setlength{\textwidth}{160mm} \setlength{\textheight}{220mm}
+\topmargin=-0.0cm \oddsidemargin=-0.1cm \setcounter{page}{1}
 
@@
 \usepackage{graphicx}
+
 \graphicspath{{images/}}
@@
 
-{ \Huge A simple method on estimating spectral radius for some direted graphs}~\\~\\
+{ \Huge A simple method on estimating spectral radius for some directed graphs}~\\~\\
 ~\\~\\~\\~\\~\\
@@
 有向圖譜半徑之簡易估算方法\\
-A simple method on estimating spectral radius for some direted graphs\\~\\
+A simple method on estimating spectral radius for some directed graphs\\~\\
 \begin{tabular}{lccr}
@@
 
- 找到一個簡單而且傑出的方法來估算譜半徑，試著縮小誤差，必定存在一個方法理性地證明它。我知道譜半徑是區分
- 圖中點連線關係的重要指標，所以找一個簡單的方法來估算譜半徑是很有意義的。有了穩固的證明，我們可以估計連
- 接矩陣的最小誤差譜半徑，並且找出存在這樣的上下界的充分條件。\\
+ 矩陣的譜半徑為其特徵值絕對值的最大值，而一有向圖的譜半徑則定義為其鄰接矩陣之譜半徑。本論文給出一個尋找方陣譜半徑上界的方法，將此方法應用於有向圖的鄰接矩陣，我們可以簡易估算出此圖的譜半徑。
+ \\
 \bigskip
 
-\noindent 關鍵詞：譜半徑，簡易方法，有向圖，估算。
+\noindent 關鍵詞：譜半徑、鄰接矩陣
 \pagebreak
@@
 \begin{center}{\LARGE
-A simple method on estimating spectral radius for some direted graphs
+A simple method on estimating spectral radius for some directed graphs
 \bigskip\bigskip\bigskip}
@@
 \addcontentsline{toc}{section}{Abstract (in English)}
-Find a simple and excellent executable method
- to estimate spectral radius, try to minimize the bios and there is a way to prove it sensible.
- I know that spectral radius is an important index to specify the relation of connected vertices in
-  the graphs, so it is meanful to find a simple method to estimate spectral readius. With a solid proof,
-   we can estimate the spectral radius of an adjacent matrix with minimal error and find out the sufficent
-  condition on the existence of such bound.
+The spectral radius of a square matrix is the largest magnitude of its eigenvalues.
+And the spectral radius of a directed graph is defined as the spectral radius of the corresponding adjacency matrix.
+In this paper, we give an approach to obtain an upper bound for the spectral radius of a square matrix.
+By applying this method on the adjacency matrix of a directed graph, we can estimate the spectral radius of this directed graph simply.
 
@@
 
-\noindent {\bf Keywords}: spectral radius, simple method, directed graphs, estimation
+\noindent {\bf Keywords}: spectral radius, adjacency matrix
 %\end{abstract}
@@
 
-\pagebreak
+\clearpage
+\pagenumbering{arabic}
+\linespread{1.5}
 
-\label{Introduction}
-% Introduction
+\setcounter{page}{1}
+%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Introduction}
-\normalsize
-\pagenumbering{arabic}
-
-\section{Preliminaries}
-
-Let $\mathbb{R}$ and $\mathbb{C}$ denote the
- field of real numbers and complex numbers respectively.
+Let $\mathbb{R}$ and $\mathbb{C}$ denote the field of real numbers and complex numbers, respectively.
+Let $C$ be an $n\times n$ real square matrix.
+If there is a nonzero column vector $u\in\mathbb{R}^n$ such that $Cu=\lambda u$ for some scalar $\lambda\in\mathbb{C}$, then the scalar $\lambda$ is called the eigenvalue of $C$ with corresponding eigenvector $u$.
+And the spectral radius of a matrix $C$ is the largest magnitude (or complex modulus) of its eigenvalues, denoted by $\rho(C)$.
+We are interested in the spectral radius of the following matrix associated with a simple directed graph.
 
 \begin{defn}
-Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a
- nonzero column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ 
-of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
-
-%Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
-\end{defn}
-
-\begin{defn} \cite{spec_rad}
-    When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$
-        of $C$ is defined by 
-        $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
-    where $|\lambda|$ is the magnitude of complex number $\lambda.$
-\end{defn}
-
-The next theorem is Perron–Frobenius Theorem, which provides a feature of
- nonnegative eigenvector to nonnegative matrices.
-\begin{thm} \cite{chang} \cite{prn_fros2} \label{thm:Perron_Frobenius}
-    If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
-    eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a
-    corresponding nonnegative left eigenvector.
-\end{thm}
-
-We are interested in spectral radius of the following matrix associated with a simple graph.
-
-\begin{defn} 
-    Given an directed graph G, the$\textit{ adjacency matrix}$ of G is the square 
-    matrix $A = (a_{ij})$ indexed by vertices of G, and
+    Given an directed graph $G$, the $\textit{adjacency matrix}$ of $G$ is the square
+    matrix $A = (a_{ij})$ indexed by vertices of $G$, and
      \[a_{ij} =\begin{cases}
@@
 
-\begin{defn}
-Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
- radius of the adjacency matrix of G.
-\end{defn}
+Given a directed graph $G$, the spectral radius of $G$ is the spectral radius of the adjacency matrix of $G$, denoted by $\rho(G)$.
+Note that the spectral radius $\rho(G)$ is independent of the ordering of the vertex set of $G$.
 
-    We introduce a notation of submatrix, which is taken from some columns and some rows of a
-     matrix.
+The spectral radius is an important indicator to specify the relation of connected vertices in a graph, so it is meaningful to find a simple method to estimate the spectral radius.
+A simple and excellent executable method to estimate the spectral radius has some features, first, the bios is minimized, and second, there must be a way to prove it sensible.
+Enumerate these factors and prove it correctly would make this method reliable.
+
+In \cite{chang}, Cheng and Weng give many bounds of the spectral radius of a nonnegative square matrix.
+And based on their theory and Perron-Frobenius theorem, we give another approach to obtain an upper bound of the spectral radius and apply it on the adjacency matrix of a directed graph.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+\section{Preliminaries}
+%%%%%%%%%%%%%%%%%%%%%%%
+
+The following is Perron–Frobenius theorem, which provides a feature of
+ nonnegative eigenvector to nonnegative matrices.
+
+\begin{thm} \cite{prn_fros2} \label{thm:Perron_Frobenius}
+    If $C$ is a nonnegative square matrix, then the spectral radius $\rho(C)$ is an
+    eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a
+    corresponding nonnegative left eigenvector.
+\end{thm}
+
+We introduce a notation of submatrix, which is taken from some columns and some rows of a matrix.
 
@@
     For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column
-    indices of $C$ respectively,  We use $C[\alpha|\beta]$ to denote the 
+    indices of $C$, respectively, we use $C[\alpha|\beta]$ to denote the
     submatrix of $C$ with size $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$
-    and $j\in\beta$,
+    and $j\in\beta$.
 \end{defn}
 
-We introduce two matrices $P$ and $Q$ in the following Theorem, where $P$ is a permutation
- matrix which is multiplied to the left side, and $Q$ is sum of elementary matrix and
- certain binary matrix. In which $P$ generalize row permutation on cases of $C$
- matrix,and $Q$ is the transform from $C'$ to C', which is the first n-1 columns
-  and sum of certain columns. We aim to find C' such that $C'$ majors $C$,i.e. $C\leq C'$
-
-The following Theorem is from \cite{chang}.
+Our theory is based on the following theorem, which is from \cite{chang}, and we introduce two square matrices $P$ and $Q$ in the following theorem first.
+The matrix $P$ is a permutation matrix which is multiplied to the left side, and the matrix $Q$ is the sum of an elementary matrix and a certain binary matrix.
+In which $P$ generalize row permutation on cases of $C$ matrix, and $Q$ is the transform from $C'$ to $C'$, which is the first $n-1$ columns and sum of certain columns.
+We aim to find $C'$ such that $C'$ majors $C$, i.e.
+$C\leq C'$.
 
@@
 \begin{proof}
-    Multiplying the nonnegative vector $u$ in Theorem~\ref{pre_thm} assumption
-    ~\ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
+    Multiplying the nonnegative vector $u$ in assumption~\ref{pre_thm_em2}, where $Qu$ is eigenvector of $C'$, to the right of both terms of
     ~\ref{pre_thm_em1},
@@
 
+%%%%%%%%%%%%%%%%%%%%
 \section{Our Method}
-We use $[n-1]$ as notation of the set of elements from one to $n-1$, which is ${1,2,...,n}$.
-Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ 
-appearing in the position $k,n$ of $E_{kn}$. We will apply the previous Theorem \ref{pre_thm} with $P=I$ and
+%%%%%%%%%%%%%%%%%%%%
+
+We use $[n-1]$ as notation of the set of elements from one to $n-1$, which is $\{1,2,...,n-1\}$.
+Throughout fix $k\in [n-1]$, let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$
+appearing in the position $k,n$ of $E_{kn}$. Now we apply the previous Theorem \ref{pre_thm} with $P=I$ and
 
@@
 Q=I+E_{kn}=\begin{pmatrix}
-1 &  & & &  & 0 \\
- & 1 &  &      &  &  \\
- &  & \ddots & &  & 1 \\
- &  &        & &  &  \\
-  &  & & & 1 &  \\
-0 &  & & &  & 1 \\
-\end{pmatrix}.  
+1 &   &         &   & 0 \\
+  & 1 &         &   &   \\
+  &   & \ddots  &   & 1 \\
+  &   &         & 1 &  \\
+0 &   &         &     & 1
+\end{pmatrix},
 \end{equation}
+so the matrix $PC'Q$ in assumption~\ref{pre_thm_em1} of Theorem~\ref{pre_thm} is
+
+\begin{equation}\label{PC'Q}
+  PC'Q=\begin{pmatrix}
+         c'_{11} & c'_{12} & \cdots &  c'_{1k}+c'_{1n} \\
+         c'_{21} & c'_{22} & \cdots &  c'_{2k}+c'_{2n} \\
+         \vdots & \vdots & \ddots &  \vdots \\
+         c'_{n1} & c'_{n2} & \cdots &  c'_{nk}+c'_{nn}
+       \end{pmatrix},
+\end{equation}
+where $c'_{ij}$ denote the $(i,j)$-entry of $C$.
 
 \begin{defn}%[$K$-rooted vector]
-~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $K$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
+A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $K$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
 \end{defn}
-\bigskip
 
 The following Lemma is immediate from the above definition.%[vector rooted lemma]
-\bigskip
 
@@
 \begin{enumerate}[label=(\roman*)]
-\item \label{lem:rt_vec:en1}$v'$ is $K$-rooted  if and only if  $u$ is nonnegative;
+\item \label{lem:rt_vec:en1}$v'$ is $k$-rooted  if and only if $u$ is nonnegative;
 \item $u_k>0$ if and only if $v'_k>v'_n$.
@@
 
-Below is our first result, in which the first condition implies the first n-1 columns of C major to
- the columns of C', and the (k,n)-sum column of C is also major to C'. The second and the third condition
- suggest that C and C' have nonnegative eigenvectors which are k-rooted. And the forth condition is simplier
-  but with the same meaning with Theorem (\ref{pre_thm})
+Below is our first result, in which the first condition implies the first $n-1$ columns of $C$ major to
+ the columns of $C'$, and the $(k,n)$-sum column of $C$ is also major to $C'$. The second and the third condition
+ suggest that $C$ and $C'$ have nonnegative eigenvectors which are $K$-rooted. And the forth condition is simpler
+  but with the same meaning with Theorem~\ref{pre_thm}
 \begin{thm}\label{thm_main}
@@
     The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn}$ in (\ref{Q_1}).
-    The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this Theorem. 
-    Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and
-     Lemma~\ref{lem:rt_vec}\ref{lem:rt_vec:en1}. Hence the assumption \ref{pre_thm_em2} of Theorem~\ref{pre_thm} holds. The assumptions \ref{pre_thm_em3} and \ref{pre_thm_em4}
-      of Theorem~\ref{pre_thm} clearly hold by conditions~\ref{thm_main:condition_iii},\ref{thm_main:condition_iv} of this Theorem since $P = I$ and
-       $v'= Qu$  Hence $\lambda \leq \lambda' $ by the necessary condition of Theorem~\ref{pre_thm}. Moreover
-        $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to
-         conditions \ref{thm_main:equ_cond_a},\ref{thm_main:equ_cond_b},\ref{thm_main:equ_cond_c} of this Theorem. 
+    The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this theorem.
+    Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and \ref{lem:rt_vec:en1} in
+     Lemma~\ref{lem:rt_vec}. Hence the assumption \ref{pre_thm_em2} of Theorem~\ref{pre_thm} holds. The assumptions \ref{pre_thm_em3} and \ref{pre_thm_em4}
+      of Theorem~\ref{pre_thm} clearly hold by conditions~\ref{thm_main:condition_iii}, \ref{thm_main:condition_iv} of this theorem since $P = I$ and
+       $v'= Qu$. Hence $\lambda \leq \lambda' $ by the necessary condition of Theorem~\ref{pre_thm}. Moreover,
+        $\lambda = \lambda'$ if and only if (\ref{pre0}) holds, and this is equivalent to
+         conditions \ref{thm_main:equ_cond_a}, \ref{thm_main:equ_cond_b} and \ref{thm_main:equ_cond_c} of this theorem.
 \end{proof}
@@
 Motivated by the condition (i) of Theorem 2.3, we provide the following two definitions.
-This is the definition of (k,n)-sum.
+This is the definition of $(k,n)$-sum.
 \begin{defn}
@@
 
-Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$
-Below is the definition of k-rooted matrix.
+Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$.
+Below is the definition of $K$-rooted matrix.
 \begin{defn}\label{m_rooted}
-    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)$-sum vector are all $K$-rooted except the last column of $C'$.
+    A  matrix $C'=(c'_{ij})$ is called {\it $K$-rooted} if its first $n-1$ columns and its $(k,n)$-sum vector are all $K$-rooted.
 \end{defn}
@@
     $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
-    1 &  & & &  & 0 \\
-    & 1 &  &      &  &  \\
-    &  & \ddots & &  & -1 \\
-    &  &        & &  &  \\
-    &  & & & 1 &  \\
-    0 &  & & &  & 1 \\
+    1 &  & &   & 0 \\
+    & 1 &        &  &  \\
+    &  & \ddots  &  & -1 \\
+    &  & &  1 &  \\
+    0 &  &  &  & 1
     \end{pmatrix}.$$
 
-    The matrix $C'Q$ is
-    $$\begin{pmatrix}
-    c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
-    \vdots \\
-    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
-    c'_{k1} & c'_{k2} &\cdots      & c'_{kn-1} & c'_{kk}+c'_{kn}\\
-    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
-    \vdots              & \vdots & \ddots              & \vdots & \vdots \\
-    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
-    \end{pmatrix}.
-    $$
 \end{rem}
 
-The following Theorem shows that a $K$-rooted matrix has a $K$-rooted eigenvector.
+The following lemma shows that a $K$-rooted matrix has a $K$-rooted eigenvector.
 \begin{lem}\label{lma_m_rooted}
@@
         \begin{enumerate}[label=(\roman*)]
-            \item \label{lma_m_rooted_cond1} $C'$ is a $K$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
-            \item \label{lma_m_rooted_cond2}Assume that $C'$ is $K$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
-                for $\rho(C')$. Then  $C'$ has a $K$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
-            \item \label{lma_m_rooted_cond3}$\rho(C')$ = $\rho(Q^{-1}C'Q)$
+            \item \label{lma_m_rooted_cond1} $C'$ is a $K$-rooted matrix if and only if $Q^{-1}C'Q$ is nonnegative,
+            \item \label{lma_m_rooted_cond2}Assume that $C'$ is $K$-rooted and let $u$ be the nonnegative eigenvector of $Q^{-1}C'Q$
+                corresponding to $\rho(C')$. Then  $C'$ has a $K$-rooted eigenvector $v'=Qu$ for $\rho(C')$,
+            \item \label{lma_m_rooted_cond3}$\rho(C')$ = $\rho(Q^{-1}C'Q)$.
         \end{enumerate}
@@
 \begin{comment}
-
 \begin{rem}
@@
 \begin{proof}
-    (i)
-    and $Q^{-1}C'Q$ is
+\begin{enumerate}
+  \item[(i)] The matrix $Q^{-1}C'Q$ is
         $$\begin{pmatrix}
             c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
-    \vdots \\
-    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
-    c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
-    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
+            \vdots      & \vdots  & \vdots     & \vdots      & \vdots\\
+            c'_{(k-1) 1}   & c'_{(k-1)  2}           & \cdots     & c'_{(k-1) (n-1)} & c'_{(k-1) k}+c'_{(k-1) n} \\
+            c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{k (n-1)}-c'_{n (k-1)}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
+            c'_{(k+1) 1}   & c'_{(k+1) 2}           & \cdots     & c'_{(k+1) (n-1)} & c'_{(k+1) k}+c'_{(k+1)
+             n} \\
             \vdots              & \vdots & \ddots              & \vdots & \vdots \\
-    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
-    \end{pmatrix}.$$
-    (ii)
-        By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $K$-rooted.  
-        Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
-        $Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
-        $C'Qu=\rho(C')Qu$.
+            c'_{n1}     & c'_{n2} & \cdots             & c'_{n (n-1)} & c'_{nk}+c'_{nn} \\
+        \end{pmatrix},$$
 
-    (iii)
-    Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly $\rho(C')$ = $\rho(Q^{-1}C'Q)$.
-
+        which is nonnegative if and only if $C'$ is $K$-rooted by the definition of nonnegative matrix and $K$-rooted matrix.
+  \item[(ii)] By Lemma~\ref{lem:rt_vec}, $v'=Qu$ is $K$-rooted. Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
+      $$Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u,$$
+      which implies
+        $$C'Qu=\rho(C')Qu.$$
+  \item[(iii)] Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly
+  $$\rho(C') = \rho(Q^{-1}C'Q).$$
+\end{enumerate}
 \end{proof}
@@
 \begin{lem}\label{l_diag}   %end of label
-If a square matrix $C'$ has a rooted eigenvector for $\lambda'$, then $C'+dI$ also has
-the same rooted eigenvector for $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
+If a square matrix $C'$ has a $K$-rooted eigenvector corresponding to $\lambda'$, then $C'+dI$ also has
+the same $K$-rooted eigenvector corresponding to $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
 \end{lem}
@@
 \begin{proof}
-    These assumptions are necessary that $PCQ \leq PC'Q$ where $P = I$,$Q = I+E_{kn}$. And $C'$ is $K$-rooted,based on Lemma
-     (\ref{lma_m_rooted}),\\
-    $Q^{-1}C'Q$ = 
-    $$\begin{pmatrix}
-        c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
+    These assumptions are necessary that $PCQ \leq PC'Q$, where $P=I$, $Q=I+E_{kn}$ and $C'$ is $K$-rooted. Based on Lemma~\ref{lma_m_rooted},
+    $$Q^{-1}C'Q=
+        \begin{pmatrix}
+        c'_{11}     & c'_{12} & \cdots     & c'_{1 (n-1)} & c'_{1k}+c'_{1n} \\
         \vdots \\
-        c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
-        c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
-        c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
+        c'_{(k-1)1}     & c'_{(k-1) 2}           & \cdots     & c'_{(k-1) (n-1)} & c'_{(k-1)k}+c'_{(k-1)n} \\
+        c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{k(n-1)}-c'_{n(k-1)}& c'_{kk}+c'_{kn}-c'_{nk}-c'_{nn}\\
+        c'_{(k+1)1}     & c'_{(k+1)2}           & \cdots     & c'_{(k+1) (n-1)} & c'_{(k+1)k}+c'_{(k+1)n} \\
         \vdots              & \vdots & \ddots              & \vdots & \vdots \\
-        c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
+        c'_{n1}             & c'_{n2} & \cdots             & c'_{n (n-1)} & c'_{nk}+c'_{nn}
     \end{pmatrix}.$$
-    $Q^{-1}C'Q \geq 0$ for that $c'_{kj}\geq c'_{nj}>0$ when $1\leq j\leq n-1$ , $c'_{ij}\geq c_{ij}$ where $C$ is nonnegative,
-    and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$\\
+    Then $Q^{-1}C'Q$ is nonnegative when $c'_{kj}\geq c'_{nj}>0$ for $1\leq j\leq n-1$ and $c'_{ij}\geq c_{ij}$, where $C$ is nonnegative, and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$.
 
-    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$, \\
-    which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ \\
-    And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, \\
-    which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$ ;\\
-    $C'$ is $K$-rooted matrix, then by Lemma (\ref{lma_m_rooted}) Conditions \ref{lma_m_rooted_cond2} and \ref{lma_m_rooted_cond3}, there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
-    such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;\\
-    And since $C$ is nonnegative, by Theorem~(\ref{thm:Perron_Frobenius}), which is Perron–Frobenius theorem, we claim there exists
-    $v^T = w^{T}P$, such that $v^T$ is nonnegative left eigenvector of $C$, and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ 
-    is an eigenvalue of $C$ with associated left eigenvector $v^T$; \\
-    Due to $v'$ and $v^T$ are nonnegative, $v^Tv'>0.$, unless they are orthogonal, i.e, $v^Tv'=0$.\\[1ex]
-    Here we can summerize the facts we know so far as the following: \\
+    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$, which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$.
+And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$; $C'$ is $K$-rooted matrix, then by conditions \ref{lma_m_rooted_cond2} and \ref{lma_m_rooted_cond3} in Lemma~\ref{lma_m_rooted}, there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+    such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$.
+   Since $C$ is nonnegative, by Theorem~\ref{thm:Perron_Frobenius}, we claim there exists $v^T = w^{T}P$, such that $v^T$ is nonnegative left eigenvector of $C$, and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$.
+    Due to $v'$ and $v^T$ are nonnegative, $v^Tv'>0$, unless they are orthogonal, i.e, $v^Tv'=0$.
+
+    Here we can summarize the facts we know so far as the following:
     \begin{enumerate}[label=(\roman*)]
@@
         \item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
-        \item $v^Tv'>0.$
+        \item $v^Tv'>0,$
     \end{enumerate}
-    which come from Theorem~(\ref{thm_main}).\\
-    By Lemma~(\ref{l_diag}), for certain $d$, if $C'+dI$ is $K$-rooted, then it has
+    which come from Theorem~\ref{thm_main}.
+
+    By Lemma~\ref{l_diag}, for certain $d$, if $C'+dI$ is $K$-rooted, then it has
     a $K$-rooted eigenvector with its spectral radius $\lambda + d$. $C'$ would share the same
     eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
-    conditions of Theorem~(\ref{thm_main}), and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
+    conditions of Theorem~\ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
     then $\rho(C') \geq \rho(C)$  %\qed
@@
     \end{pmatrix},$$
-    And its corresponding graph,\cite[sage]{sage}\\
-    \includegraphics{graph_C.PNG} \\
-    we choose
+    and corresponding directed graph, \cite[sage]{sage}
+    \begin{center}
+    \includegraphics{graph_C.PNG}
+    \end{center}
+    we choose the matrix
     $$C'=\begin{pmatrix}
@@
     1 & 1 & 1 & 0
-    \end{pmatrix}.$$
-    also, graph,\cite[sage]{sage}\\
-    \includegraphics{graph_Cprime.PNG} \\
-    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ of Theorem~\ref{thm_main},
-    Then
-    $\rho(C)\leq \rho(C')$ by previous Theorem~\ref{thm:conclusion}.
+    \end{pmatrix},$$
+    which satisfies the assumptions in Theorem~\ref{thm:conclusion}.
+Hence $\rho(C)\leq\rho(C')$.
+Actually, both of the values of $\rho(C)$ and $\rho(C')$ are close to 2.511547, and we have $\rho(C')-\rho(C)>0$ by calculating on computer.
+    Moreover, the corresponding directed graph of matrix $C'$ is, \cite[sage]{sage}
+    \begin{center}
+    \includegraphics{graph_Cprime.PNG}
+    \end{center}
 
@@
     \end{pmatrix},$$
-    specify $n$=4, $k$=3 in $Q = I +E_{kn} = I + E_{34}$  
+    specify $n$=4, $k$=3 in $Q = I +E_{kn} = I + E_{34}$, then
     $$CQ=\begin{pmatrix}
@@
 
-    we have $CQ\leq C'Q$, but 
+    and we have $CQ\leq C'Q$, but
     $\rho(C)=2.234\not\leq 2.148= \rho(C')$.

### 2020-12-24 spectral radius of matrix new method/thesis/article121420.tex
122420 adoption

@@
 \item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-\item \label{thm_main:condition_ii} there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
-such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-\item \label{thm_main:condition_iii}there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+\item \label{thm_main:condition_ii} there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar
+ $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
+\item \label{thm_main:condition_iii}there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar
+ $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
 \item \label{thm_main:condition_iv}$v^Tv'>0.$
@@
     \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
-    \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
+    \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $ with $v_i\ne 0 $;
     \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$
@@
 
-    Here we can summarize the facts we know so far as the following:
+    Here we can summarize the facts we know in theorem \ref{thm_main} so far as the following:
     \begin{enumerate}[label=(\roman*)]
@@
         such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-        \item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+        \item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$
+         such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
         \item $v^Tv'>0,$
@@
     conditions of Theorem~\ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
-    then $\rho(C') \geq \rho(C)$  %\qed
+    then $\rho(C') \geq \rho(C)$
+
+    As the same reason, we have $\lambda=\lambda'$ such case
+    if and only if
+    \begin{enumerate}[label=(\alph*)]
+        \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$
+         and $v'_n\not=0;$
+        \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $
+         with $v_i\ne 0 $;
+        \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$
+    \end{enumerate} %\qed
+
 \end{proof}
@@
     \end{center}
-    we choose the matrix
+    we choose the matrix and fix $k = 3$
     $$C'=\begin{pmatrix}
@@
     \end{pmatrix},$$
-    which satisfies the assumptions in Theorem~\ref{thm:conclusion}.
-Hence $\rho(C)\leq\rho(C')$.
-Actually, both of the values of $\rho(C)$ and $\rho(C')$ are close to 2.511547, and we have $\rho(C')-\rho(C)>0$ by calculating on computer.
+    Based on condition of theorem \ref{thm:conclusion},
+    \begin{enumerate}[label=(\roman*)]
+        \item  $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
+        \item  there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+        such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
+        \item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ 
+        such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+        \item $v^Tv'>0.$
+    \end{enumerate}
+    Here $n=4,k=3$ so rewrite the condition of theorem \ref{thm_main} as following:
+    \begin{enumerate}[label=(\roman*)]
+        \item  $C[[4]|[3]]\leq C'[[4]|[3]]$ and $c_{i3}+c_{i4}\leq c'_{i3}+c'_{i4}$ for all $1\leq i\leq 4$;
+        \item  there exists a $K$-rooted vector $v'=(v'_1, v'_2, v'_3, v'_4)^T$ and a scalar $\lambda'\in \mathbb{R}$
+        such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
+        \item there exists a nonnegative vector $v^T=(v_1, v_2, v_3, v_4)$ and a scalar $\lambda\in \mathbb{R}$ 
+        such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+        \item $v^Tv'>0.$
+    \end{enumerate}
+    Then we check these conditions one by one,
+    \begin{enumerate}[label=(\roman*)]
+    \item 
+    $$C[[4]|[3]]=\begin{pmatrix}
+        0 & 0 & 1\\
+        1 & 0 & 0\\
+        1 & 1 & 0\\
+        1 & 1 & 1
+        \end{pmatrix},$$
+    $$C'[[4]|[3]]=\begin{pmatrix}
+        0 & 0 & 1\\
+        1 & 0 & 1\\
+        1 & 1 & 0\\
+        1 & 1 & 1
+        \end{pmatrix},$$
+    thus,$C[[4]|[3]]\leq C'[[4]|[3]].$
+    Write $c_{i3}+c_{i4}$ and $c'_{i3}+c'_{i4}$, for $1\leq i\leq 4$, as two row vectors $v_c$ and $v_{c'}$.
+    $v_c = (s_1, s_2, s_3, s_4), s_i = c_{i3}+c_{i4},$ so $v_c = (2,1,1,1)$
+    $v'_c = (s'_1, s'_2, s'_3, s'_4), s'_i = c'_{i3}+c'_{i4},$ so $v'_c = (2,1,1,1),$
+    so $c_{i3}+c_{i4} \leq c'_{i3}+c'_{i4}.$
+    \item 
+    Let $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$.
+    Then $\lambda' = 2.511547141694532$ and associated eigenvector $v'=(1, 0.8981609516297208, 1.255773570847266, 1.255773570847266)^T$.
+    \item 
+    Let  $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$.
+    Then $\lambda = 2.511547141694532$ and associated left eigenvector $v^T=(1, 0.715225238435091, 1, 0.7963219032594416)$.
+    \item 
+    $v^T * v' = (1, 0.715225238435091, 1, 0.7963219032594416) \\
+    * (1, 0.8981609516297208, 1.255773570847266, 1.255773570847266)^T
+    \\ = 3.89816095162972 >0.$
+
+    \end{enumerate}
+
+    These facts satisfy the assumptions in Theorem~\ref{thm:conclusion}. Hence $\rho(C)\leq\rho(C')$. Actually, both of
+     the values of $\rho(C)$ and $\rho(C')$ are close to 2.511547, and we have $\rho(C')-\rho(C)>0$ by calculating on
+     computer.\cite[sage]{sage}
     Moreover, the corresponding directed graph of matrix $C'$ is, \cite[sage]{sage}

### 2021-01-07 spectral radius of matrix new method/thesis/article120920.tex
121620 update
010721 read

@@
 \usepackage{graphicx}
+%\usepackage{indentfirst}
 \graphicspath{{images/}}
@@
 \begin{defn} 
-    Given an directed graph G, the$\textit{ adjacency matrix}$ of G is the square 
-    matrix $A = (a_{ij})$ indexed by vertices of G, and
+    Given an directed graph $G$, the$\textit{adjacency matrix}$ of $G$ is the square 
+    matrix $A = (a_{ij})$ indexed by vertices of $G$, and
      \[a_{ij} =\begin{cases} 
@@
 \begin{defn}
-    Given a directed graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
-     radius of the adjacency matrix of G.
+    Given a directed graph $G$, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
+     radius of the adjacency matrix of $G$.
 \end{defn}
@@
 \begin{thm} \cite{chang} \cite{prn_fros2} \label{thm:Perron_Frobenius}
-    If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
+    If $C$ is a nonnegative square matrix, then the spectral radius $\rho(C)$ is an
     eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a
@@
 \section{Our Method}
-We use $[n-1]$ as notation of the set of elements from one to $n-1$, which is ${1,2,...,n}$.
-Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ 
+We use $[n-1]$ as notation of the set of elements from one to $n-1$, which is $\{1,2,...,n-1\}$.
+Throughout fix $k\in [n-1]$. Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ 
 appearing in the position $k,n$ of $E_{kn}$. We will apply the previous Theorem \ref{pre_thm} with $P=I$ and
@@
 \begin{defn}%[$K$-rooted vector]
-~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $K$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
+A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $K$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
 \end{defn}
@@
 
-Below is our first result, in which the first condition implies the first n-1 columns of C major to
- the columns of C', and the (k,n)-sum column of C is also major to C'. The second and the third condition
- suggest that C and C' have nonnegative eigenvectors which are k-rooted. And the forth condition is simplier
-  but with the same meaning with Theorem (\ref{pre_thm})
+Below is our first result, in which the first condition implies the first $n-1$ columns of $C$ major to
+ the columns of $C'$, and the $(k,n)$-sum column of $C$ is also major to $C'$. The second and the third condition
+ suggest that $C$ and $C'$ have nonnegative eigenvectors which are $k$-rooted. And the forth condition is simpler
+  but with the same meaning with Theorem~(\ref{pre_thm})
 \begin{thm}\label{thm_main}
@@
 Motivated by the condition (i) of Theorem 2.3, we provide the following two definitions. 
-This is the definition of (k,n)-sum.
+This is the definition of $(k,n)$-sum.
 \begin{defn}
@@
 
-Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$
-Below is the definition of k-rooted matrix.
+Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$.
+Below is the definition of $k$-rooted matrix.
 \begin{defn}\label{m_rooted}
-    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)$-sum vector are all $K$-rooted except the last column of $C'$.
+    A  matrix $C'=(c'_{ij})$ is called $k-rooted$ if its columns and its $(k,n)$-sum vector are all $K$-rooted except the last column of $C'$.
 \end{defn}
@@
 
-The following Theorem shows that a $K$-rooted matrix has a $K$-rooted eigenvector.
+The following lemma shows that a $K$-rooted matrix has a $K$-rooted eigenvector.
 \begin{lem}\label{lma_m_rooted}
@@
 \begin{proof}
-    These assumptions are necessary that $PCQ \leq PC'Q$ where $P = I$,$Q = I+E_{kn}$. And $C'$ is $K$-rooted,based on Lemma
+    These assumptions are necessary that $PCQ \leq PC'Q$ where $P=I$,$Q=I+E_{kn}$. And $C'$ is $K$-rooted,based on Lemma
      (\ref{lma_m_rooted}),\\
@@
     Due to $v'$ and $v^T$ are nonnegative, $v^Tv'>0.$, unless they are orthogonal, i.e, $v^Tv'=0$.\\[1ex]
-    Here we can summerize the facts we know so far as the following: \\
+    Here we can summarize the facts we know so far as the following: \\
     \begin{enumerate}[label=(\roman*)]
@@
     \end{pmatrix}.$$
+
     also, graph,\cite[sage]{sage}\\

### 2021-01-07 spectral radius of matrix new method/thesis/article121420.tex
010721 read

--- 2020-12-15 spectral radius of matrix new method/thesis/article121420.tex
@@
 
- 矩陣的譜半徑為其特徵值絕對值的最大值，而一有向圖的譜半徑則定義為其鄰接矩陣之譜半徑。本論文給出一個尋找方陣譜半徑上界的方法，將此方法應用於有向圖的鄰接矩陣，我們可以簡易估算出此圖的譜半徑。
+ 矩陣的譜半徑為其特徵值絕對值的最大值，而一有向圖的譜半徑則定義為其鄰接矩陣之
+ 譜半徑。本論文給出一個尋找方陣譜半徑上界的方法，將此方法應用於有向圖的鄰接矩
+ 陣，我們可以簡易估算出此圖的譜半徑。
  \\
@@
 \addcontentsline{toc}{section}{Abstract (in English)}
-The spectral radius of a square matrix is the largest magnitude of its eigenvalues.
-And the spectral radius of a directed graph is defined as the spectral radius of the corresponding adjacency matrix.
-In this paper, we give an approach to obtain an upper bound for the spectral radius of a square matrix.
-By applying this method on the adjacency matrix of a directed graph, we can estimate the spectral radius of this directed graph simply.
+The spectral radius of a square matrix is the largest magnitude of its eigenvalues. And the
+ spectral radius of a directed graph is defined as the spectral radius of the corresponding
+ adjacency matrix. In this paper, we give an approach to obtain an upper bound for the
+ spectral radius of a square matrix. By applying this method on the adjacency matrix of a
+ directed graph, we can estimate the spectral radius of this directed graph simply.
 
@@
 
-Let $\mathbb{R}$ and $\mathbb{C}$ denote the field of real numbers and complex numbers, respectively.
-Let $C$ be an $n\times n$ real square matrix.
-If there is a nonzero column vector $u\in\mathbb{R}^n$ such that $Cu=\lambda u$ for some scalar $\lambda\in\mathbb{C}$, then the scalar $\lambda$ is called the eigenvalue of $C$ with corresponding eigenvector $u$.
-And the spectral radius of a matrix $C$ is the largest magnitude (or complex modulus) of its eigenvalues, denoted by $\rho(C)$.
-We are interested in the spectral radius of the following matrix associated with a simple directed graph.
+Let $\mathbb{R}$ and $\mathbb{C}$ denote the
+ field of real numbers and complex numbers, respectively.
+ Let $C$ be an $n\times n$ real square matrix. If there is
+ a nonzero column vector $u\in\mathbb{R}^n$ such that
+ $Cu=\lambda u$ for some scalar $\lambda\in\mathbb{C}$,
+ then the scalar $\lambda$ is called the eigenvalue of
+ $C$ with corresponding eigenvector $u$. And the spectral
+ radius of a matrix $C$ is the largest magnitude (or complex
+ modulus) of its eigenvalues, denoted by $\rho(C)$. We are
+ interested in the spectral radius of the following matrix
+ associated with a simple directed graph.
 
 \begin{defn}
-    Given an directed graph $G$, the $\textit{adjacency matrix}$ of $G$ is the square
+Given an directed graph $G$, the $\textit{adjacency matrix}$ of
+ $G$ is the square
  matrix $A = (a_{ij})$ indexed by vertices of $G$, and
@@
 
-Given a directed graph $G$, the spectral radius of $G$ is the spectral radius of the adjacency matrix of $G$, denoted by $\rho(G)$.
-Note that the spectral radius $\rho(G)$ is independent of the ordering of the vertex set of $G$.
+Given a directed graph $G$, the spectral radius of $G$ is the
+ spectral radius of the adjacency matrix of $G$, denoted by
+ $\rho(G)$. Note that the spectral radius $\rho(G)$ is
+ independent of the ordering of the vertex set of $G$.
 
-The spectral radius is an important indicator to specify the relation of connected vertices in a graph, so it is meaningful to find a simple method to estimate the spectral radius.
-A simple and excellent executable method to estimate the spectral radius has some features, first, the bios is minimized, and second, there must be a way to prove it sensible.
-Enumerate these factors and prove it correctly would make this method reliable.
+The spectral radius is an important indicator to specify the relation
+ of connected vertices in a graph, so it is meaningful to find a simple
+ method to estimate the spectral radius. A simple and excellent
+ executable method to estimate the spectral radius has some features,
+ first, the bios is minimized, and second, there must be a way to prove
+ it sensible. Enumerate these factors and prove it correctly would make this method reliable.
 
@@
 
-We introduce a notation of submatrix, which is taken from some columns and some rows of a matrix.
+We introduce a notation of submatrix, which is taken from some columns and some rows of a
+ matrix.
 
@@
 
-Our theory is based on the following theorem, which is from \cite{chang}, and we introduce two square matrices $P$ and $Q$ in the following theorem first.
-The matrix $P$ is a permutation matrix which is multiplied to the left side, and the matrix $Q$ is the sum of an elementary matrix and a certain binary matrix.
-In which $P$ generalize row permutation on cases of $C$ matrix, and $Q$ is the transform from $C'$ to $C'$, which is the first $n-1$ columns and sum of certain columns.
-We aim to find $C'$ such that $C'$ majors $C$, i.e.
-$C\leq C'$.
+Our theory is based on the following theorem, which is from \cite{chang}, and we introduce two square matrices
+ $P$ and $Q$ in the following theorem first. The matrix $P$ is a permutation
+ matrix which is multiplied to the left side, and the matrix $Q$ is the sum of an elementary matrix and a
+ certain binary matrix. In which $P$ generalize row permutation on cases of $C$ matrix, and $Q$ is the transform
+ from $C'$ to $C'$, which is the first $n-1$ columns and sum of certain columns. We aim to find $C'$ such that
+ $C'$ majors $C$, i.e. $C\leq C'$.
 
@@
 \begin{proof}
-    Multiplying the nonnegative vector $u$ in assumption~\ref{pre_thm_em2}, where $Qu$ is eigenvector of $C'$, to the right of both terms of
-    ~\ref{pre_thm_em1},
+    Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm}
+     assumption~\ref{pre_thm_em1},
+     where $Qu$ is eigenvector of $C'$, 
+     to the right of both terms of~\ref{pre_thm_em1},
     \begin{equation}\label{pre1}
@@
     \end{equation}
+
     Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption
-     ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), where $v^TP$ is
-    left eigenvector of $C$ for $\lambda$, thus we have
+     ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}),
+      where $v^TP$ is left eigenvector of $C$ for $\lambda$, thus we have
     \begin{equation}\label{pre2}
@@
 so the matrix $PC'Q$ in assumption~\ref{pre_thm_em1} of Theorem~\ref{pre_thm} is
-
 \begin{equation}\label{PC'Q}
@@
 \end{equation}
-where $c'_{ij}$ denote the $(i,j)$-entry of $C$.
+where $c'_{ij}$ denotes the $(i,j)$-entry of $C'$.
 
@@
     The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this theorem.
-    Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and \ref{lem:rt_vec:en1} in
+    Let $u = Q^{-1}v'$. Then $u$ is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and \ref{lem:rt_vec:en1} in
      Lemma~\ref{lem:rt_vec}. Hence the assumption \ref{pre_thm_em2} of Theorem~\ref{pre_thm} holds. The assumptions \ref{pre_thm_em3} and \ref{pre_thm_em4}
@@
 \begin{defn}
-    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-sum vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
+    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-sum vector of $C'$ is the vector
+     of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
 \end{defn}
@@
 \begin{defn}\label{m_rooted}
-    A  matrix $C'=(c'_{ij})$ is called {\it $K$-rooted} if its first $n-1$ columns and its $(k,n)$-sum vector are all $K$-rooted.
+    A  matrix $C'=(c'_{ij})$ is called {\it $K$-rooted} if its
+     first $n-1$ columns and its $(k,n)$-sum vector are all $K$-rooted.
 \end{defn}
@@
     \end{pmatrix}.$$
-    Then $Q^{-1}C'Q$ is nonnegative when $c'_{kj}\geq c'_{nj}>0$ for $1\leq j\leq n-1$ and $c'_{ij}\geq c_{ij}$, where $C$ is nonnegative, and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$.
+    Then $Q^{-1}C'Q$ is nonnegative when $c'_{kj}\geq c'_{nj}>0$ for $1\leq j\leq n-1$ and $c'_{ij}\geq c_{ij}$, where $C$ is nonnegative,
+     and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$.
 
-    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$, which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$.
-And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$; $C'$ is $K$-rooted matrix, then by conditions \ref{lma_m_rooted_cond2} and \ref{lma_m_rooted_cond3} in Lemma~\ref{lma_m_rooted}, there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
+    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$,
+    which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$.
+    And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$,
+    which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$;
+    $C'$ is $K$-rooted matrix, then by conditions \ref{lma_m_rooted_cond2} and \ref{lma_m_rooted_cond3} in Lemma~\ref{lma_m_rooted}, there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
     such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$.
-   Since $C$ is nonnegative, by Theorem~\ref{thm:Perron_Frobenius}, we claim there exists $v^T = w^{T}P$, such that $v^T$ is nonnegative left eigenvector of $C$, and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$.
+    Since $C$ is nonnegative, by Theorem~\ref{thm:Perron_Frobenius}, we claim there exists
+    $v^T = w^{T}P$, such that $v^T$ is nonnegative left eigenvector of $C$, and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$
+    is an eigenvalue of $C$ with associated left eigenvector $v^T$.
     Due to $v'$ and $v^T$ are nonnegative, $v^Tv'>0$, unless they are orthogonal, i.e, $v^Tv'=0$.
@@
     \end{pmatrix},$$
-    which satisfies the assumptions in Theorem~\ref{thm:conclusion}.
-Hence $\rho(C)\leq\rho(C')$.
-Actually, both of the values of $\rho(C)$ and $\rho(C')$ are close to 2.511547, and we have $\rho(C')-\rho(C)>0$ by calculating on computer.
+    which satisfies the assumptions in Theorem~\ref{thm:conclusion}. Hence $\rho(C)\leq\rho(C')$.
+     Actually, both of the values of $\rho(C)$ and $\rho(C')$ are close to 2.511547, and we have
+      $\rho(C')-\rho(C)>0$ by calculating on computer.
     Moreover, the corresponding directed graph of matrix $C'$ is, \cite[sage]{sage}

### 2021-01-07 spectral radius of matrix new method/thesis/version_12_28_2020.tex
010721 read

--- 2021-01-07 spectral radius of matrix new method/thesis/article121420.tex
@@
 
-{ \Huge 有向圖譜半徑之簡易估算方法}~\\~\\
+{ \Huge 有向圖譜半徑之簡易比較方法}~\\~\\
 
@@
 
-{ \Huge A simple method on estimating spectral radius for some directed graphs}~\\~\\
+{ \Huge A simple method on comparison between spectral radii of two directed graphs}~\\~\\
 ~\\~\\~\\~\\~\\
@@
 \Large
-有向圖譜半徑之簡易估算方法\\
-A simple method on estimating spectral radius for some directed graphs\\~\\
+有向圖譜半徑之簡易比較方法\\
+A simple method on comparison between spectral radii of two directed graphs\\~\\
 \begin{tabular}{lccr}
@@
 {  \LARGE
-有向圖譜半徑之簡易估算方法
+有向圖譜半徑之簡易比較方法
 \bigskip\bigskip\bigskip
@@
  矩陣的譜半徑為其特徵值絕對值的最大值，而一有向圖的譜半徑則定義為其鄰接矩陣之
- 譜半徑。本論文給出一個尋找方陣譜半徑上界的方法，將此方法應用於有向圖的鄰接矩
- 陣，我們可以簡易估算出此圖的譜半徑。
+ 譜半徑。本論文給出一個比較方陣譜半徑的方法，將此方法應用於有向圖的鄰接矩
+ 陣， 我們可以簡易比較有向圖的譜半徑。
  \\
@@
 \begin{center}{\LARGE
-A simple method on estimating spectral radius for some directed graphs
+A simple method on comparison between spectral radii of two directed graphs
 \bigskip\bigskip\bigskip}
@@
  spectral radius of a directed graph is defined as the spectral radius of the corresponding
- adjacency matrix. In this paper, we give an approach to obtain an upper bound for the
- spectral radius of a square matrix. By applying this method on the adjacency matrix of a
- directed graph, we can estimate the spectral radius of this directed graph simply.
+ adjacency matrix. In this paper, we give an approach to compare the spectral radii of two
+ nonnegative matrices. By applying this method on the adjacency matrix of a
+ directed graph, we can compare the spectral radii of two directed graphs simply.
 
@@
  Let $C$ be an $n\times n$ real square matrix. If there is
- a nonzero column vector $u\in\mathbb{R}^n$ such that
+ a nonzero column vector $u\in\mathbb{C}^n$ such that
  $Cu=\lambda u$ for some scalar $\lambda\in\mathbb{C}$,
@@
 \begin{defn}
-Given an directed graph $G$, the $\textit{adjacency matrix}$ of
- $G$ is the square
+    Given a directed graph $G$, the $\textit{adjacency matrix}$ of $G$ is the square
     matrix $A = (a_{ij})$ indexed by vertices of $G$, and
      \[a_{ij} =\begin{cases}
-        1, \text{if $i$ is adjacent to $j$}, \\
+        1, \text{if $ji$ is an arc in $G$}, \\
         0, \text{otherwise.}
@@
  independent of the ordering of the vertex set of $G$.
+
+Conversely, we can also define a directed graph $G$ from a given
+ nonnegative $n\times n$ matrix $C=(c_{ij})$  by setting the vertex
+ set $\{1, 2, \ldots, n\}$ and edge set $\{ij~\colon~c_{ij}>0\}$.
+ The matrix $C$ is {\it irreducible} if the defined graph $G$ from
+ $C$ is strongly connected.
 
@@
 The following is Perron–Frobenius theorem, which provides a feature of
- nonnegative eigenvector to nonnegative matrices.
+ nonnegative eigenvectors to nonnegative matrices.
 
@@
     corresponding nonnegative left eigenvector.
+    Moreover if $C$ is irreducible the above eigenvectors can be chosen to be positive. 
 \end{thm}
 
-We introduce a notation of submatrix, which is taken from some columns and some rows of a
- matrix.
-
-\begin{defn}
-    For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column
-    indices of $C$, respectively, we use $C[\alpha|\beta]$ to denote the
-    submatrix of $C$ with size $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$
-    and $j\in\beta$.
-\end{defn}
-
-Our theory is based on the following theorem, which is from \cite{chang}, and we introduce two square matrices
- $P$ and $Q$ in the following theorem first. The matrix $P$ is a permutation
- matrix which is multiplied to the left side, and the matrix $Q$ is the sum of an elementary matrix and a
- certain binary matrix. In which $P$ generalize row permutation on cases of $C$ matrix, and $Q$ is the transform
- from $C'$ to $C'$, which is the first $n-1$ columns and sum of certain columns. We aim to find $C'$ such that
- $C'$ majors $C$, i.e. $C\leq C'$.
+ A well-known application of Theorem~\ref{thm:Perron_Frobenius}
+ show that if matrix  $C'$ {\it majors} $C$ (in notation $C\leq C'$),
+ i.e. $c_{ij}\leq c'_{ij}$ for all $ij,j$, then $\rho(C)\leq \rho(C')$.
+Our main result shows that the assumption $C\leq C'$ can be a little loosen. 
+Our theory is based on the following theorem, which is from \cite{chang}.
 
 \begin{thm}\label{pre_thm}
-    Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be $n\times n$ matrices.
-Assume that
+    Let $C=(c_{ij})$, $C'=(c'_{ij})$  be $n\times n$ real matrices
+     with real eigenvalues $\lambda$, $\lambda'$ respectively such
+     that there exist $n\times n$ matrices $P$ and $Q$   satisfying the following (i)-(iv).
 \begin{enumerate}[label=(\roman*)]
     \item \label{pre_thm_em1}  $PCQ\leq PC'Q$;
-    \item \label{pre_thm_em2} there exist a nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a
-    scalar $\lambda'\in \mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with
-    associated eigenvector $Qu$;
-    \item \label{pre_thm_em3}  there exist a nonnegative row vector $v^T=(v_1, v_2, \ldots, v_n)$  and a scalar
-    $\lambda\in \mathbb{R}$such that $\lambda$ is an eigenvalue of $C$ with associated  left
-    eigenvector $v^TP$; and
+    \item \label{pre_thm_em2} an eigenvector $Qu$ of $C'$  associated with
+     eigenvalue $\lambda'$ exists for some nonnegative column vector
+      $u=(u_1, u_2, \ldots, u_n)^T$.
+    \item \label{pre_thm_em3} a left eigenvector $v^TP$ of $C'$ associated
+     with eigenvalue $\lambda$ exists for some nonnegative row vector
+     $v^T=(v_1, v_2, \ldots, v_n)$; and
     \item \label{pre_thm_em4} $v^TPQu>0.$
@@
 \begin{proof}
-    Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm}
-     assumption~\ref{pre_thm_em1},
-     where $Qu$ is eigenvector of $C'$, 
+    Multiplying the nonnegative vector $u$ in assumption~\ref{pre_thm_em2}
+
     to the right of both terms of~\ref{pre_thm_em1},
     \begin{equation}\label{pre1}
-       PCQu\leq PC'Qu=\lambda'PQu.
+       PCQu\leq PC'Qu=\lambda'PQu,
     \end{equation}
-
-    Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption
-     ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}),
-      where $v^TP$ is left eigenvector of $C$ for $\lambda$, thus we have
+ where the above equality follows by $Qu$ being eigenvector of $C'$ for $\lambda'$.
+    Multiplying the nonnegative vector $v^T$ of $C$ in assumption
+     ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), we have
     \begin{equation}\label{pre2}
-        \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
+        \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu,
     \end{equation}
+    where the above first equality follows by $v^TP$ being
+    left eigenvector of $C$ for $\lambda$.
     Now delete the positive term $v^TPQu$ by assumption \ref{pre_thm_em4} to obtain
@@
         $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with
-        $u_j\not=0.$ Conversely, (\ref{pre0}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=
-         \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so $\lambda=\lambda'$ by (\ref{pre2}).
+        $u_j\not=0.$ Conversely, (\ref{pre0}) implies
+        \begin{align*} &\lambda v^TPCQu=v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j\\ =&
+         \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu=\lambda'v^TPC'Qu,
+         \end{align*} so $\lambda=\lambda'$ by (\ref{pre2}).
 \end{proof}
@@
 
-We use $[n-1]$ as notation of the set of elements from one to $n-1$, which is $\{1,2,...,n-1\}$.
-Throughout fix $k\in [n-1]$, let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$
+We will apply Theorem~\ref{pre_thm} by using two particular square matrices $P$ and $Q$ to obtain our main result. 
+We use $[n-1]$ as notation of the set of integers from $1$ to $n-1$, which is $\{1,2,\cdots,n-1\}$.
+Throughout this thesis we fix $k\in [n-1]$, let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$
 appearing in the position $k,n$ of $E_{kn}$. Now we apply the previous Theorem \ref{pre_thm} with $P=I$ and
@@
 Q=I+E_{kn}=\begin{pmatrix}
-1 &   &         &   & 0 \\
-  & 1 &         &   &   \\
-  &   & \ddots  &   & 1 \\
-  &   &         & 1 &  \\
-0 &   &         &     & 1
+1 &   &        &       &        &   & 0 \\
+  & 1 &        &       &        &   &   \\
+  &   & \ddots &       &        &   &   \\
+  &   &        & 1     &        &   & 1 \\
+  &   &        &       &\ddots  &   &  \\
+  &   &        &       &        &1  & 0 \\
+0 &   &        &       &        &0  & 1
 \end{pmatrix},
@@
 
-\begin{defn}%[$K$-rooted vector]
-A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $K$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
+\begin{defn}%[$k$-rooted vector]
+A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted} if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n$.
 \end{defn}
 
-The following Lemma is immediate from the above definition.%[vector rooted lemma]
+The following Lemma is immediate from the above definition.
 
 \begin{lem}\label{lem:rt_vec}
-If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
+If $u=(u_1, u_2, \ldots, u_n)^T$, then
 \begin{enumerate}[label=(\roman*)]
-\item \label{lem:rt_vec:en1}$v'$ is $k$-rooted  if and only if $u$ is nonnegative;
-\item $u_k>0$ if and only if $v'_k>v'_n$.
+\item \label{lem:rt_vec:en1} $Qu$ is $k$-rooted  if and only if $u$ is nonnegative;
+\item $u_k>0$ if and only if $(Qu)_k>(Qu)_n$.
 \end{enumerate}
@@
 
-Below is our first result, in which the first condition implies the first $n-1$ columns of $C$ major to
- the columns of $C'$, and the $(k,n)$-sum column of $C$ is also major to $C'$. The second and the third condition
- suggest that $C$ and $C'$ have nonnegative eigenvectors which are $K$-rooted. And the forth condition is simpler
-  but with the same meaning with Theorem~\ref{pre_thm}
+\begin{proof}
+(i), (ii) follow immediate from the definition of $k$-rooted and
+ $Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$.
+\end{proof}
+
+Below is our first result, in which the first condition implies the first $n-1$ columns of $C'$ major
+ the same columns of $C$, and the sum of $k$-th and $n$-th columns of $C'$ also majors that of $C$. The second and the third condition
+ suggest that $C$ and $C'$ have nonnegative $k$-rooted eigenvectors. And the forth condition is simpler
+  but with the same meaning in Theorem~\ref{pre_thm}
+
+We need a notation of submatrix, which is taken from some columns and some rows of a matrix.
+
+\begin{defn}
+    For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column
+    indices of $C$, respectively, we use $C[\alpha|\beta]$ to denote the
+    submatrix of $C$ with size $ |\alpha| \times |\beta| $ that has entries $c_{ij}$ for $i\in \alpha$
+    and $j\in\beta$. We use the notation $C[i|j]$ for short of $C[[i]|[j]].$
+\end{defn}
+
 \begin{thm}\label{thm_main}
-    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
+    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ real matrices with real eigenvalues $\lambda$ and $\lambda'$ respectively.
 Assume that
 \begin{enumerate}[label=(\roman*)]
-\item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-\item \label{thm_main:condition_ii} there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
-such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-\item \label{thm_main:condition_iii}there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
+\item \label{thm_main:condition_i} $C[n|n-1]\leq C'[n|n-1]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
+\item \label{thm_main:condition_ii} there exists a $k$-rooted eigenvector vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ of $C'$ for $\lambda'$;
+\item \label{thm_main:condition_iii}there exists a nonnegative eigenvector vector $v^T=(v_1, v_2, \ldots, v_n)$ of $C$ for $\lambda$;
  \item \label{thm_main:condition_iv}$v^Tv'>0.$
@@
 \begin{enumerate}[label=(\alph*)]
-    \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
-    \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
-    \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$
-\end{enumerate} %\qed
+    \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i>0$ and $v'_n>0;$
+    \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1,$ $j \neq k$ with $v_i\ne 0 $ and $v'_j>0$;
+    \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ with  $v_i>0$ and $ v'_{k}>v'_n$
+\end{enumerate} 
 \end{thm}
-%
 
@@
 
-We are interested in the matrices $C'$ that have $K$-rooted eigenvectors.
+We are interested in the matrices $C'$ that have $k$-rooted eigenvectors.
 Motivated by the condition (i) of Theorem 2.3, we provide the following two definitions.
-This is the definition of $(k,n)$-sum.
+The first is the definition of $(k,n)$-sum.
 \begin{defn}
-    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-sum vector of $C'$ is the vector
-     of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
+    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum vector} of $C'$ is the vector
+     obtained from the sum of the $k$-th and  $n$-th columns of $C'$.
 \end{defn}
@@
 Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$.
-Below is the definition of $K$-rooted matrix.
+Below is the definition of $k$-rooted matrix.
 \begin{defn}\label{m_rooted}
-    A  matrix $C'=(c'_{ij})$ is called {\it $K$-rooted} if its
-     first $n-1$ columns and its $(k,n)$-sum vector are all $K$-rooted.
+    A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if for
+     each $i\not=k, n$ the  $i$-th column of $C'$  is $k$-rooted
+     and the $(k,n)$-sum vector of $C'$ is $k$-rooted.
 \end{defn}
 
-\begin{rem}
+We need a simple lemma for later use.
 
-    $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
-    1 &  & &   & 0 \\
-    & 1 &        &  &  \\
-    &  & \ddots  &  & -1 \\
-    &  & &  1 &  \\
-    0 &  &  &  & 1
-    \end{pmatrix}.$$
-
-\end{rem}
-
-The following lemma shows that a $K$-rooted matrix has a $K$-rooted eigenvector.
-\begin{lem}\label{lma_m_rooted}
-    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
-        \begin{enumerate}[label=(\roman*)]
-            \item \label{lma_m_rooted_cond1} $C'$ is a $K$-rooted matrix if and only if $Q^{-1}C'Q$ is nonnegative,
-            \item \label{lma_m_rooted_cond2}Assume that $C'$ is $K$-rooted and let $u$ be the nonnegative eigenvector of $Q^{-1}C'Q$
-                corresponding to $\rho(C')$. Then $C'$ has a $K$-rooted eigenvector $v'=Qu$ for $\rho(C')$,
-            \item \label{lma_m_rooted_cond3}$\rho(C')$ = $\rho(Q^{-1}C'Q)$.
-        \end{enumerate}
+\begin{lem}
+$Q^{-1}=I-E_{kn}.$
 \end{lem}
 
-\begin{comment}
-\begin{rem}
-        (i) is immediate from Definition~\ref{m_rooted} and the observation that
-        $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
-        1 &  & & &  & 0 \\
-         & 1 &  &      &  &  \\
-         &  & \ddots & &  & -1 \\
-         &  &        & &  &  \\
-          &  & & & 1 &  \\
-        0 &  & & &  & 1 \\
+\begin{proof}
+Since $$Q(I-E_{kn}=(I+E_{kn})(I-E_{kn})=I-E_{kn}+E_{kn}-E_{kn}E_{kn}=I,$$ we have
+$Q^{-1}=I-E_{kn}$.
+\end{proof}
+
+The matrix $Q^{-1}$ is explicitly written as
+    $$Q^{-1}=I-E_{kn}=
+\begin{pmatrix}
+1 &   &        &       &        &   & 0 \\
+  & 1 &        &       &        &   &   \\
+  &   & \ddots &       &        &   &   \\
+  &   &        & 1     &        &   & -1 \\
+  &   &        &       &\ddots  &   &  \\
+  &   &        &       &        &1  & 0 \\
+0 &   &        &       &        &0  & 1
 \end{pmatrix},$$ 
-\end{rem}
-\end{comment}
-\begin{proof}
-\begin{enumerate}
-  \item[(i)] The matrix $Q^{-1}C'Q$ is
-        $$\begin{pmatrix}
+and if $C'=(c'_{ij})$ then $Q^{-1}C'Q$ has the form 
+\begin{equation}\label{e6}
+\begin{pmatrix}
             c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
@@
             c'_{n1}     & c'_{n2} & \cdots             & c'_{n (n-1)} & c'_{nk}+c'_{nn} \\
-        \end{pmatrix},$$
+        \end{pmatrix}.\end{equation}
 
-        which is nonnegative if and only if $C'$ is $K$-rooted by the definition of nonnegative matrix and $K$-rooted matrix.
-  \item[(ii)] By Lemma~\ref{lem:rt_vec}, $v'=Qu$ is $K$-rooted. Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
-      $$Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u,$$
-      which implies
-        $$C'Qu=\rho(C')Qu.$$
-  \item[(iii)] Since $C'$ and $Q^{-1}C'Q$ have the same set of eigenvalues, clearly
-  $$\rho(C') = \rho(Q^{-1}C'Q).$$
+The following lemma shows that a $k$-rooted matrix has a $k$-rooted eigenvector.
+
+\begin{lem}\label{lma_m_rooted}
+    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(ii) hold.
+        \begin{enumerate}[label=(\roman*)]
+            \item \label{lma_m_rooted_cond1} $C'$ is a $k$-rooted matrix if and only if $Q^{-1}(C'+dI)Q$ is nonnegative for some $d\geq 0$, where $I$ is the $n\times n$ identity matrix. 
+            \item \label{lma_m_rooted_cond2} If $C'$ is $k$-rooted then there exists a  $k$-rooted eigenvector $v'$ of $C'$  for $\rho(C')$.
+        \end{enumerate}
+\end{lem}
+
+\begin{proof}
+\begin{enumerate}
+  \item[(i)] The matrix $Q^{-1}C'Q$ has $ij$ entry
+$$(Q^{-1}C'Q)_{ij}=\left\{
+                     \begin{array}{ll}
+                       c'_{ij}, & \hbox{if $i\not=k$ and $j\not=n$;} \\
+                       c'_{kj}-c'_{nj}, & \hbox{if $i=k$ and $j\not=n$;} \\
+                       c'_{ik}+c'_{in}, & \hbox{if $i\not=k$ and $j=n$;} \\ 
+                       c'_{kk}+c'_{kn}-c'_{nk}-c'_{nn}, & \hbox{if $i=k$ and $j=n$},
+                     \end{array}
+                   \right.$$
+as shown in (\ref{e6}). 
+Hence $Q^{-1}(C'+dI)Q$ is nonnegative if and only if $C'$ is $k$-rooted by the definition of nonnegative matrix and $k$-rooted matrix.
+  \item[(ii)] Suppose $C'$ is $k$-rooted. Choose $d\geq 0$ such that $Q^{-1}(C'+dI)Q$ is nonnegative.  
+Let $u$ be a nonnegative eigenvector of $Q^{-1}(C'+dI)Q=Q^{-1}C'Q+I$ for $\rho(C'+dI)=\rho(C')+d.$
+Note that $Q^{-1}C'Qu=\rho(C')u,$ and $Qu$ is $k$-rooted by Lemma~\ref{lem:rt_vec}. Hence $v'=Qu$ is what we want. 
 \end{enumerate}
@@
 
-\begin{lem}\label{l_diag}   %end of label
-If a square matrix $C'$ has a $K$-rooted eigenvector corresponding to $\lambda'$, then $C'+dI$ also has
-the same $K$-rooted eigenvector corresponding to $\lambda'+d,$ where $d$ is a constant and $I$ is the identity matrix with the same size of $C'$.
-\end{lem}
+Note that Theorem~\ref{thm_main} depends on eigenvectors. The following is an eigenvector-free Theorem.
 
 \begin{thm}\label{thm:conclusion}
-    Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
-    such that $c'_{ij}\geq c_{ij}$ and $c'_{kj}\geq c'_{nj}>0$, and choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, and
-    $r'_k \geq r'_n$. Moreover choose $c'_{in}:=r'_i-c'_{ik}$. Then $\rho(C)\leq \rho(C')$, when $C'=(c'_{ij})$.
+    Let $C$ be an $n\times n$ nonnegative irreducible matrix and $C'$ be an $n\times n$ $k$-rooted matrix such that $C'Q$ majorizes $CQ$. 
+ Then $\rho(C)\leq \rho(C')$. 
 \end{thm}
 
-\begin{proof}
-    These assumptions are necessary that $PCQ \leq PC'Q$, where $P=I$, $Q=I+E_{kn}$ and $C'$ is $K$-rooted. Based on Lemma~\ref{lma_m_rooted},
-    $$Q^{-1}C'Q=
-        \begin{pmatrix}
-        c'_{11}     & c'_{12} & \cdots     & c'_{1 (n-1)} & c'_{1k}+c'_{1n} \\
-        \vdots \\
-        c'_{(k-1)1}     & c'_{(k-1) 2}           & \cdots     & c'_{(k-1) (n-1)} & c'_{(k-1)k}+c'_{(k-1)n} \\
-        c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{k(n-1)}-c'_{n(k-1)}& c'_{kk}+c'_{kn}-c'_{nk}-c'_{nn}\\
-        c'_{(k+1)1}     & c'_{(k+1)2}           & \cdots     & c'_{(k+1) (n-1)} & c'_{(k+1)k}+c'_{(k+1)n} \\
-        \vdots              & \vdots & \ddots              & \vdots & \vdots \\
-        c'_{n1}             & c'_{n2} & \cdots             & c'_{n (n-1)} & c'_{nk}+c'_{nn}
-    \end{pmatrix}.$$
-    Then $Q^{-1}C'Q$ is nonnegative when $c'_{kj}\geq c'_{nj}>0$ for $1\leq j\leq n-1$ and $c'_{ij}\geq c_{ij}$, where $C$ is nonnegative,
-     and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$.
-
-    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$,
-    which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$.
-    And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$,
-    which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$;
-    $C'$ is $K$-rooted matrix, then by conditions \ref{lma_m_rooted_cond2} and \ref{lma_m_rooted_cond3} in Lemma~\ref{lma_m_rooted}, there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
-    such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$.
-    Since $C$ is nonnegative, by Theorem~\ref{thm:Perron_Frobenius}, we claim there exists
-    $v^T = w^{T}P$, such that $v^T$ is nonnegative left eigenvector of $C$, and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$
-    is an eigenvalue of $C$ with associated left eigenvector $v^T$.
-    Due to $v'$ and $v^T$ are nonnegative, $v^Tv'>0$, unless they are orthogonal, i.e, $v^Tv'=0$.
-
-    Here we can summarize the facts we know so far as the following:
-    \begin{enumerate}[label=(\roman*)]
-        \item  $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
-        \item  there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
-        such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
-        \item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
-        \item $v^Tv'>0,$
-    \end{enumerate}
-    which come from Theorem~\ref{thm_main}.
-
-    By Lemma~\ref{l_diag}, for certain $d$, if $C'+dI$ is $K$-rooted, then it has
-    a $K$-rooted eigenvector with its spectral radius $\lambda + d$. $C'$ would share the same
-    eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
-    conditions of Theorem~\ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
-    then $\rho(C') \geq \rho(C)$  %\qed
+\begin{proof} Referring to (\ref{PC'Q}), the assumption \ref{thm_main:condition_i} in  Theorem~\ref{thm_main} holds. 
+By Lemma~\ref{lma_m_rooted} \ref{lma_m_rooted_cond2}, there exists a  $k$-rooted eigenvector $v'$ of $C'$  for $\rho(C')$. 
+Since $C$ is irreducible and nonnegative, there exists a positive eigenvector $v^T$ of $C$ for $\rho(C).$ 
+Thus $v^Tv'>0$. Hence Theorem~\ref{thm_main} \ref{thm_main:condition_i}-\ref{thm_main:condition_iv} hold.
+Hence  $\rho(C) \leq \rho(C')$ by   Theorem~\ref{thm_main}.
 \end{proof}
 
-\subsection{Example}
-    For the following $4\times 4$ matrix
-    $$C=\begin{pmatrix}
+% proof shortened
+
+\begin{exam}
+
+Let $G$ be the digraph depicted below. 
+\bigskip
+
+\begin{center}
+\begin{tikzpicture}
+
+\tikzset{vertex/.style = {shape=circle,draw,minimum size=0.5em}}
+\tikzset{edge/.style = {->,> = latex'}}
+% vertices
+\node[vertex] (1) at  (0,5) {$1$};
+\node[vertex] (2) at  (6,10) {$2$};
+\node[vertex] (3) at  (12,5) {$3$};
+\node[vertex] (4) at  (6,5) {$4$};
+
+%edges
+\draw[edge] (1) to (2);
+\draw[edge] (1) to[bend left] (3);
+\draw[edge] (1) to[bend left] (4);
+\draw[edge] (2) to (3);
+\draw[edge] (2) to[bend left] (4);
+\draw[edge] (3) to[bend left] (1);
+\draw[edge] (3) to[bend left] (4); 
+\draw[edge] (4)[bend left] to (1); 
+\draw[edge] (4)[bend left] to (2); 
+\draw[edge] (4)[bend left] to (3); 
+\end{tikzpicture}
+\end{center}
+
+The following $4\times 4$ matrix is the adjacency matrix of $G$. 
+    $$A=\begin{pmatrix}
     0 & 0 & 1 & 1\\
@@
     1 & 1 & 1 & 0
-    \end{pmatrix},$$
-    and corresponding directed graph, \cite[sage]{sage}
-    \begin{center}
-    \includegraphics{graph_C.PNG}
-    \end{center}
-    we choose the matrix
-    $$C'=\begin{pmatrix}
+    \end{pmatrix}.$$ 
+We choose another matrix 
+    $$A'=\begin{pmatrix}
     0 & 0 & 1 & 1\\
@@
     \end{pmatrix},$$
-    which satisfies the assumptions in Theorem~\ref{thm:conclusion}. Hence $\rho(C)\leq\rho(C')$.
-     Actually, both of the values of $\rho(C)$ and $\rho(C')$ are close to 2.511547, and we have
-      $\rho(C')-\rho(C)>0$ by calculating on computer.
-    Moreover, the corresponding directed graph of matrix $C'$ is, \cite[sage]{sage}
+which is the adjacency matrix of $G'$ depicted below. 
+\bigskip
+
 \begin{center}
-    \includegraphics{graph_Cprime.PNG}
+\begin{tikzpicture}
+
+\tikzset{vertex/.style = {shape=circle,draw,minimum size=0.5em}}
+\tikzset{edge/.style = {->,> = latex'}}
+% vertices
+\node[vertex] (1) at  (0,5) {$1$};
+\node[vertex] (2) at  (6,10) {$2$};
+\node[vertex] (3) at  (12,5) {$3$};
+\node[vertex] (4) at  (6,5) {$4$};
+
+%edges
+\draw[edge] (1) to (2);
+\draw[edge] (1) to[bend left] (3);
+\draw[edge] (1) to[bend left] (4);
+\draw[edge] (2) to (3);
+\draw[edge] (2) to (4);
+\draw[edge] (3) to[bend left] (1);
+\draw[edge] (3) to (2);
+\draw[edge] (3) to[bend left] (4);
+\draw[edge] (4)[bend left] to (1);
+\draw[edge] (4)[bend left] to (3);
+\end{tikzpicture}
 \end{center}
 
-\subsection{Counterexample}
-    For the following two $4\times 4$ matrices
+Note that both $G$ and $G'$ have the same number of edges, 
+neither $A$ majories $A'$ nor $A'$ majories $A$. Our main result still can do comparison between 
+$\rho(A)$ and $\rho(A')$. 
+We first observe that $A$ is irreducible and $A'$ is $k$-rooted for $k=3$. Moreover 
+$A'Q=\begin{pmatrix}
+    0 & 0 & 1 & 2\\
+    1 & 0 & 1 & 1\\
+    1 & 1 & 0 & 1\\
+    1 & 1 & 1 & 1
+    \end{pmatrix}\geq \begin{pmatrix}
+    0 & 0 & 1 & 2\\
+    1 & 0 & 0 & 1\\
+    1 & 1 & 0 & 1\\
+    1 & 1 & 1 & 1
+    \end{pmatrix}=AQ$. 
+Hence Hence $\rho(A)\leq\rho(A')$ by Theorem~\ref{thm:conclusion} with $C=A$ and $C'=A'$. 
+Both of the values of $\rho(C)$ and $\rho(C')$ are close to $2.511547$ by  calculating on computer. 
+\end{exam}
+
+To finish the thesis, we provide an example to show that the `$k$-rooted' assumption of $C'$ is necessary in Theorem~\ref{thm:conclusion}.
+
+\begin{exam}
+    Consider the following two $4\times 4$ matrices
     $$C=\begin{pmatrix}
@@
     1 & 1 & 1 & 0
-    \end{pmatrix},$$
-    specify $n$=4, $k$=3 in $Q = I +E_{kn} = I + E_{34}$, then
+    \end{pmatrix}.$$
+    With $n=4$ and $k=3$, we have  
     $$CQ=\begin{pmatrix}
@@
     1 & 1 & 1 & 1
-    \end{pmatrix},\quad C'Q=\begin{pmatrix}
+    \end{pmatrix}\leq \begin{pmatrix}
     0 & 0 & 1 & 2\\
@@
     1 & 1 & 1 & 1
-    \end{pmatrix},$$
+    \end{pmatrix}=C'Q.$$
+Using computer, 
+    $$\rho(C)\approx 2.234\not\leq 2.148\approx \rho(C').$$
+    This is because $C'$ is not $k$-rooted as $c'_{33}+c'_{34}=0\not\geq 1=c'_{43}+c'_{44}$.
 
-    and we have $CQ\leq C'Q$, but
-    $\rho(C)=2.234\not\leq 2.148= \rho(C')$.
-    This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.
+\end{exam}
 
@@
 
-\bibitem{spec_rad}
-A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012
-
 \bibitem{prn_fros2}
 R. A. Horn , C. R. Johnson, {\it Matrix analysis}, Cambrigde University Press, 1985.
-
-\bibitem{sage}
-[Sage] SageMath, the Sage Mathematics Software System (Version 9.2),
-       The Sage Developers, 2020, https://www.sagemath.org.  %sage tutorial
-
 \end{thebibliography}

### 2021-01-20 spectral radius of matrix new method/thesis/article012121.tex
0121 final check and sending

--- 2021-01-07 spectral radius of matrix new method/thesis/version_12_28_2020.tex
@@
 And based on their theory and Perron-Frobenius theorem, we give another approach to obtain an upper bound of the spectral radius and apply it on the adjacency matrix of a directed graph.
+All theorems come from continuous discussions between C.W. Weng and K.H. Chen. These were all documented.\cite{src_files}
 
@@
 \begin{proof}
-    Multiplying the nonnegative vector $u$ in assumption~\ref{pre_thm_em2}
+    Multiplying the nonnegative vector $u$ in assumption~\ref{pre_thm_em1}
 
@@
 %edges
-\draw[edge] (1) to (2);
-\draw[edge] (1) to[bend left] (3);
-\draw[edge] (1) to[bend left] (4);
-\draw[edge] (2) to (3);
-\draw[edge] (2) to[bend left] (4);
-\draw[edge] (3) to[bend left] (1);
-\draw[edge] (3) to[bend left] (4); 
-\draw[edge] (4)[bend left] to (1); 
-\draw[edge] (4)[bend left] to (2); 
-\draw[edge] (4)[bend left] to (3); 
+
+\draw[edge] (1) to[bend right] (3);
+\draw[edge] (1) to[bend right] (4);
+\draw[edge] (2) to (1);
+\draw[edge] (2) to[bend right] (4);
+\draw[edge] (3) to (2);
+\draw[edge] (3) to[bend right] (1);
+\draw[edge] (3) to[bend right] (4); 
+\draw[edge] (4)[bend right] to (1); 
+\draw[edge] (4)[bend right] to (2); 
+\draw[edge] (4)[bend right] to (3); 
 \end{tikzpicture}
@@
 %edges
-\draw[edge] (1) to (2);
-\draw[edge] (1) to[bend left] (3);
-\draw[edge] (1) to[bend left] (4);
+
+\draw[edge] (1) to[bend right] (3);
+\draw[edge] (1) to[bend right] (4);
+\draw[edge] (2) to (1);
 \draw[edge] (2) to (3);
-\draw[edge] (2) to (4);
-\draw[edge] (3) to[bend left] (1);
+\draw[edge] (3) to[bend right] (1);
 \draw[edge] (3) to (2);
-\draw[edge] (3) to[bend left] (4);
-\draw[edge] (4)[bend left] to (1);
-\draw[edge] (4)[bend left] to (3);
+\draw[edge] (3) to[bend right] (4);
+\draw[edge] (4)[bend right] to (1);
+\draw[edge] (4) to (2);
+\draw[edge] (4)[bend right] to (3);
 \end{tikzpicture}
@@
 Hence Hence $\rho(A)\leq\rho(A')$ by Theorem~\ref{thm:conclusion} with $C=A$ and $C'=A'$. 
-Both of the values of $\rho(C)$ and $\rho(C')$ are close to $2.511547$ by  calculating on computer. 
+Both of the values of $\rho(C)$ and $\rho(C')$ are close to $2.511547$ by  calculating on computer. \cite[sage]{sage}
 \end{exam}
@@
     \end{pmatrix}=C'Q.$$
-Using computer, 
+Using computer, \cite[sage]{sage}
     $$\rho(C)\approx 2.234\not\leq 2.148\approx \rho(C').$$
     This is because $C'$ is not $k$-rooted as $c'_{33}+c'_{34}=0\not\geq 1=c'_{43}+c'_{44}$.
+
+All theorems come from continuous discussions between C.W. Weng and K.H. Chen. These were all documented.\cite{src_files}
 
@@
 
+\bibitem{spec_rad}
+A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012
 \bibitem{prn_fros2}
 R. A. Horn , C. R. Johnson, {\it Matrix analysis}, Cambrigde University Press, 1985.
+\bibitem{sage}
+[Sage] SageMath, the Sage Mathematics Software System (Version 9.2),
+       The Sage Developers, 2020, https://www.sagemath.org.  %sage tutorial
+\bibitem{src_files}
+[github] K. H. Chen, C. W. Weng, source files to the essay, A simple method on comparison between spectral radii of two directed graphs,
+     2021, https://reurl.cc/6yy32Z. % https://github.com/Urbaner3/NCTU_weng.
+
 \end{thebibliography}

### 2021-01-20 spectral radius of matrix new method/thesis/article121420.tex
0121 final check and sending

--- 2020-12-24 spectral radius of matrix new method/thesis/article121420.tex
@@
 
-Given a directed graph $G$, the spectral radius of $G$ is the spectral radius of the adjacency matrix of $G$, denoted by $\rho(G)$.
-Note that the spectral radius $\rho(G)$ is independent of the ordering of the vertex set of $G$.
+Given a directed graph $G$, the spectral radius of $G$ ,\cite{spec_rad}, is the
+ spectral radius of the adjacency matrix of $G$, denoted by
+ $\rho(G)$. Note that the spectral radius $\rho(G)$ is
+ independent of the ordering of the vertex set of $G$.
 
-The spectral radius is an important indicator to specify the relation of connected vertices in a graph, so it is meaningful to find a simple method to estimate the spectral radius.
-A simple and excellent executable method to estimate the spectral radius has some features, first, the bios is minimized, and second, there must be a way to prove it sensible.
-Enumerate these factors and prove it correctly would make this method reliable.
+The spectral radius is an important indicator to specify the relation
+ of connected vertices in a graph, so it is meaningful to find a simple
+ method to estimate the spectral radius. A simple and excellent
+ executable method to estimate the spectral radius has some features,
+ first, the bios is minimized, and second, there must be a way to prove
+ it sensible. Enumerate these factors and prove it correctly would make this method reliable.
 
@@
     \end{pmatrix},$$
+
+    which satisfies the assumptions in Theorem~\ref{thm:conclusion}. Hence $\rho(C)\leq\rho(C')$.
+     Actually, both of the values of $\rho(C)$ and $\rho(C')$ are close to 2.511547, and we have
+      $\rho(C')-\rho(C)>0$ by calculating on computer.
+
     Based on condition of theorem \ref{thm:conclusion},
@@
      computer.\cite[sage]{sage}
+
     Moreover, the corresponding directed graph of matrix $C'$ is, \cite[sage]{sage}
@@
 R. A. Horn , C. R. Johnson, {\it Matrix analysis}, Cambrigde University Press, 1985.
-
 \bibitem{sage}

### 2021-01-24 spectral radius of matrix new method/slides/oral0125.tex
before oral0125

--- 2021-01-20 spectral radius of matrix new method/thesis/article012121.tex
@@
-\documentclass[12pt, a4paper]{article}
+\documentclass{beamer}
 
-\setlength{\textwidth}{160mm} \setlength{\textheight}{220mm}
-\topmargin=-0.0cm \oddsidemargin=-0.1cm \setcounter{page}{1}
+\usepackage{graphicx}
+\usetheme{Berlin}
+\usecolortheme{wolverine}
 
-\usepackage{fontspec}   %加這個就可以設定字體
-\usepackage{xeCJK}       %讓中英文字體分開設置
-%\usepackage{times}
-\usepackage{amssymb}
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{ulem}
-\usepackage{amsfonts}
-\usepackage{mathrsfs}
-\usepackage{tabularx,array}
-\usepackage{pgf,tikz}
- \usepackage{blkarray} %line 80-92 Q formula matrix index
-%\usepackage{colortbl}
-\usepackage{enumitem}% enumerate labels   roman
-\usepackage{graphicx}
+\graphicspath{{graphs/}}
 
-\graphicspath{{images/}}
-\usetikzlibrary{arrows}
-\setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
-\XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
-\XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
-\title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
-\author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
-\date{} %不要日期
-
-\def\UrlFont{\rm}
-
-\theoremstyle{plain}
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{remark}[thm]{Remark}
-\newtheorem{eg}[thm]{Example}
-\newtheorem{conj}[thm]{Conjecture}
-
-\theoremstyle{definition}
-\newtheorem{defn}[thm]{Definition}
-\newtheorem{ex}[thm]{Exercise}
-\newtheorem{prob}[thm]{Problem}
-\newtheorem{exam}[thm]{Example}
-\newtheorem{nota}[thm]{Notation}
-\newtheorem{rem}[thm]{Remark}
-\newtheorem{ques}[thm]{Question}
-% \newtheorem{pof}[thm]{Proof.}
-
-\usepackage{comment}
-
-%\renewcommand {\refname} {Bibliography}
+%Information to be included in the title page:
+\title{A simple method on comparison between spectral
+radii of two directed graphs}
+\author{陳科翰}
+\institute{Mathematic department, NCTU}
+\date{2021.01.25}
 
@@
 
-%封面
+\frame{\titlepage}
 
-\thispagestyle{empty}
-\begin{center}
-{ \Huge 國~~~~立~~~~交~~~~通~~~~大~~~~學}~\\~\\
+\begin{frame}
+    \frametitle{References}
+    \begin{thebibliography}{20}
+        \normalsize
+        \addcontentsline{toc}{section}{Bibliography}
 
-\bigskip
+        \bibitem{chang}
+        Yen-Jen Cheng, {\it  A matrix realization of spectral bounds
+        of the spectral radius of a nonnegative matrix}, Ph.D. Thesis, NCTU, 2018.
 
-{ \Huge 應~用~數~學~系}~\\~\\
+        \bibitem{spec_rad}
+        A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012
+        \bibitem{prn_fros2}
+        R. A. Horn , C. R. Johnson, {\it Matrix analysis}, Cambrigde University Press, 1985.
+        \bibitem{sage}
+        [Sage] SageMath, the Sage Mathematics Software System (Version 9.2),
+               The Sage Developers, 2020, https://www.sagemath.org.  %sage tutorial
+        \bibitem{src_files}
+        [github] K. H. Chen, C. W. Weng, source files to the essay, A simple method on comparison between spectral radii of two directed graphs,
+             2021, https://reurl.cc/6yy32Z. % https://github.com/Urbaner3/NCTU_weng.
 
-\bigskip
+        \end{thebibliography}
+\end{frame}
 
-{ \Huge 碩~~士~~論~~文}~\\~\\
-
-\bigskip \bigskip\bigskip\bigskip\bigskip\bigskip
-
-{ \Huge 有向圖譜半徑之簡易比較方法}~\\~\\
-
-\bigskip
-
-{ \Huge A simple method on comparison between spectral radii of two directed graphs}~\\~\\
-~\\~\\~\\~\\~\\
-\bigskip \bigskip\bigskip\bigskip\bigskip\bigskip
-\bigskip \bigskip\bigskip\bigskip\bigskip\bigskip
-\bigskip\bigskip\bigskip
-
-{ \Large
-\begin{tabular}{rcl}
-研究生&：&陳科翰\\
-指導教授&：&翁志文~教授
-\end{tabular} }
-
-\bigskip\bigskip
-{ \Large 中~~華~~民~~國~~一~~百~~ㄧ~~十~~年~~一~~月 }
-\large
-\end{center}
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\renewcommand{\baselinestretch}{2} %行距
-\thispagestyle{empty}
-\begin{center}
-{
-\Large
-有向圖譜半徑之簡易比較方法\\
-A simple method on comparison between spectral radii of two directed graphs\\~\\
-\begin{tabular}{lccr}
-Student: Ko-Han Chen  &&~~~& Advisor: Chih-Wen Weng\\
-研究生:陳科翰　 &&~~~& 指導教授：翁志文~教授
-\end{tabular}
-}~\\
-
-\bigskip
-
-\renewcommand{\baselinestretch}{1} %行距
-
-{ \LARGE 國~~~~立~~~~交~~~~通~~~~大~~~~學}\\~\\
-{ \LARGE 應~用~數~學~系}\\~\\
-{ \LARGE 碩~~士~~論~~文}\\~\\~\\~\\~\\
-\renewcommand{\baselinestretch}{1} %行距
-{ \large A Thesis
-
-Submitted to Department of Applied Mathematics
-
-College of Science
-
-National Chiao Tung University
-
-in Partial Fulfillment of Requirements
-
-for the Degree of Master
-
-in Applied Mathematics
-\bigskip \medskip
-
-January 2021
-
-Hsinchu, Taiwan, Republic of China \bigskip \medskip
-
- 中~~華~~民~~國~~一~~百~~ㄧ~~十~~年~~一~~月 }
-\end{center}
-\pagebreak
-
-\label{abstract}
-
-%中文摘要
-\pagenumbering{roman}
-\begin{center}
-{  \LARGE
-有向圖譜半徑之簡易比較方法
-\bigskip\bigskip\bigskip
-
-研究生：陳科翰  ~~~~~~~~~~ 指導教授：翁志文~教授 \\
-國立交通大學  \\
-\bigskip
-應用數學系
-\bigskip\bigskip\bigskip\bigskip
-} \\~\\~\\~\\
-\addcontentsline{toc}{section}{Abstract (in Chinese)}
-{\large 摘~要}
-\end{center}
- \bigskip
-
- 矩陣的譜半徑為其特徵值絕對值的最大值，而一有向圖的譜半徑則定義為其鄰接矩陣之
- 譜半徑。本論文給出一個比較方陣譜半徑的方法，將此方法應用於有向圖的鄰接矩
- 陣， 我們可以簡易比較有向圖的譜半徑。
- \\
-\bigskip
-
-\noindent 關鍵詞：譜半徑、鄰接矩陣
-\pagebreak
-
-%英文摘要
-\begin{center}{\LARGE
-A simple method on comparison between spectral radii of two directed graphs
-\bigskip\bigskip\bigskip}
-
-{ \large
-Student: Ko-Han Chen  ~~~~~ Advisor: Chih-Wen Weng \\
-\Large
-
-Department ~of~ Applied ~Mathematics
-\bigskip
-
-National~ Chiao ~Tung~ University
-\bigskip\bigskip\bigskip\bigskip}\\
-{\large Abstract}
-\end{center}
-
-%\begin{abstract}
-\addcontentsline{toc}{section}{Abstract (in English)}
-The spectral radius of a square matrix is the largest magnitude of its eigenvalues. And the
- spectral radius of a directed graph is defined as the spectral radius of the corresponding
- adjacency matrix. In this paper, we give an approach to compare the spectral radii of two
- nonnegative matrices. By applying this method on the adjacency matrix of a
- directed graph, we can compare the spectral radii of two directed graphs simply.
-
-\bigskip
-
-\noindent {\bf Keywords}: spectral radius, adjacency matrix
-%\end{abstract}
-\pagebreak
-
-\renewcommand{\baselinestretch}{1.2}
-% 目錄
-\large
-\tableofcontents
-
-\clearpage
-\pagenumbering{arabic}
-\linespread{1.5}
-
-\setcounter{page}{1}
-%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-%%%%%%%%%%%%%%%%%%%%%%
-
+\begin{frame}
+\frametitle{Introduction}
 Let $\mathbb{R}$ and $\mathbb{C}$ denote the
@@
 associated with a simple directed graph.
+\end{frame}
 
-\begin{defn}
+\begin{frame}
+    \begin{definition}
         Given a directed graph $G$, the $\textit{adjacency matrix}$ of $G$ is the square
@@
          \]
-\end{defn}
-
+    \end{definition}
     Given a directed graph $G$, the spectral radius of $G$ is the
@@
 
-Conversely, we can also define a directed graph $G$ from a given
- nonnegative $n\times n$ matrix $C=(c_{ij})$  by setting the vertex
- set $\{1, 2, \ldots, n\}$ and edge set $\{ij~\colon~c_{ij}>0\}$.
- The matrix $C$ is {\it irreducible} if the defined graph $G$ from
- $C$ is strongly connected.
+\end{frame}
 
-The spectral radius is an important indicator to specify the relation
- of connected vertices in a graph, so it is meaningful to find a simple
- method to estimate the spectral radius. A simple and excellent
- executable method to estimate the spectral radius has some features,
- first, the bios is minimized, and second, there must be a way to prove
- it sensible. Enumerate these factors and prove it correctly would make this method reliable.
+\begin{frame}
+    In \cite{chang}, Cheng and Weng give many bounds of the spectral radius
+     of a nonnegative square matrix. And based on their theory and Perron-Frobenius
+      theorem, we give another approach to obtain an upper bound of the spectral
+       radius and apply it on the adjacency matrix of a directed graph.
 
-In \cite{chang}, Cheng and Weng give many bounds of the spectral radius of a nonnegative square matrix.
-And based on their theory and Perron-Frobenius theorem, we give another approach to obtain an upper bound of the spectral radius and apply it on the adjacency matrix of a directed graph.
-All theorems come from continuous discussions between C.W. Weng and K.H. Chen. These were all documented.\cite{src_files}
+    All theorems come from continuous discussions between C.W. Weng and K.H. Chen.
+     These were all documented.\cite{src_files}
+\end{frame}
 
-%%%%%%%%%%%%%%%%%%%%%%%
-\section{Preliminaries}
-%%%%%%%%%%%%%%%%%%%%%%%
-
+\begin{frame}
+    \label{thm:Perron_Frobenius}
+    \frametitle{Preliminaries}
     The following is Perron–Frobenius theorem, which provides a feature of
@@
 
-\begin{thm} \cite{prn_fros2} \label{thm:Perron_Frobenius}
+\begin{theorem} \cite{prn_fros2} 
     If $C$ is a nonnegative square matrix, then the spectral radius $\rho(C)$ is an
@@
     Moreover if $C$ is irreducible the above eigenvectors can be chosen to be positive. 
-\end{thm}
+\end{theorem}
+\end{frame}
 
+\begin{frame}
     A well-known application of Theorem~\ref{thm:Perron_Frobenius}
@@
 Our theory is based on the following theorem, which is from \cite{chang}.
+\end{frame}
 
-\begin{thm}\label{pre_thm}
+\begin{frame}
+    \begin{theorem}
+        \label{pre_thm}
         Let $C=(c_{ij})$, $C'=(c'_{ij})$  be $n\times n$ real matrices
@@
          that there exist $n\times n$ matrices $P$ and $Q$   satisfying the following (i)-(iv).
-\begin{enumerate}[label=(\roman*)]
+    \begin{enumerate}[(i)]
         \item \label{pre_thm_em1}  $PCQ\leq PC'Q$;
@@
         \end{equation}
-\end{thm}
+    \end{theorem}
+\end{frame}
 
-\begin{proof}
+\begin{frame}
     Multiplying the nonnegative vector $u$ in assumption~\ref{pre_thm_em1}
@@
  where the above equality follows by $Qu$ being eigenvector of $C'$ for $\lambda'$.
+\end{frame}
+
+\begin{frame}
     Multiplying the nonnegative vector $v^T$ of $C$ in assumption
@@
         $\lambda\leq \lambda'$ and finish the proof of the first part.
+\end{frame}
+
+\begin{frame}
     Assume that $\lambda=\lambda'$, so the inequality in (\ref{pre2}) is an equality.
@@
          \end{align*} so $\lambda=\lambda'$ by (\ref{pre2}).
-\end{proof}
+\end{frame}
 
-%%%%%%%%%%%%%%%%%%%%
-\section{Our Method}
-%%%%%%%%%%%%%%%%%%%%
-
+\begin{frame}
+    \frametitle{Our Method}
     We will apply Theorem~\ref{pre_thm} by using two particular square matrices $P$ and $Q$ to obtain our main result. 
@@
 Throughout this thesis we fix $k\in [n-1]$, let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$
-appearing in the position $k,n$ of $E_{kn}$. Now we apply the previous Theorem \ref{pre_thm} with $P=I$ and
+appearing in the position $k,n$ of $E_{kn}$.
+\end{frame}
+
+\begin{frame}
+    Now we apply the previous Theorem \ref{pre_thm} with $P=I$ and
 
@@
     \end{equation}
+\end{frame}
+
+\begin{frame}
     so the matrix $PC'Q$ in assumption~\ref{pre_thm_em1} of Theorem~\ref{pre_thm} is
@@
 where $c'_{ij}$ denotes the $(i,j)$-entry of $C'$.
+\end{frame}
 
-\begin{defn}%[$k$-rooted vector]
+\begin{frame}
+    \begin{definition}%[$k$-rooted vector]
         A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted} if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n$.
-\end{defn}
+        \end{definition}
 
@@
 
-\begin{lem}\label{lem:rt_vec}
+        \begin{lemma}\label{lem:rt_vec}
         If $u=(u_1, u_2, \ldots, u_n)^T$, then
-\begin{enumerate}[label=(\roman*)]
+        \begin{enumerate}[(i)]
         \item \label{lem:rt_vec:en1} $Qu$ is $k$-rooted  if and only if $u$ is nonnegative;
@@
         % \qed
-\end{lem}
+        \end{lemma}
+\end{frame}
 
+\begin{frame}
     \begin{proof}
@@
           but with the same meaning in Theorem~\ref{pre_thm} 
+\end{frame}
 
+\begin{frame}
     We need a notation of submatrix, which is taken from some columns and some rows of a matrix.
 
-\begin{defn}
+\begin{definition}
     For a matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column
@@
     and $j\in\beta$. We use the notation $C[i|j]$ for short of $C[[i]|[j]].$
-\end{defn}
+\end{definition}
+\end{frame}
 
-\begin{thm}\label{thm_main}
+\begin{frame}
+    \begin{theorem}\label{thm_main}
         Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ real matrices with real eigenvalues $\lambda$ and $\lambda'$ respectively.
     Assume that
-\begin{enumerate}[label=(\roman*)]
+        \begin{enumerate}[(i)]
         \item \label{thm_main:condition_i} $C[n|n-1]\leq C'[n|n-1]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
@@
         \end{enumerate}
+
         Then $\lambda\leq \lambda'$.
@@
         if and only if
-\begin{enumerate}[label=(\alph*)]
+        \begin{enumerate}[(a)]
             \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i>0$ and $v'_n>0;$
@@
         \end{enumerate} 
-\end{thm}
+    \end{theorem}
+\end{frame}
 
+\begin{frame}
     \begin{proof}
@@
     \end{proof}
+\end{frame}
 
+\begin{frame}
     We are interested in the matrices $C'$ that have $k$-rooted eigenvectors.
@@
 The first is the definition of $(k,n)$-sum.
-\begin{defn}
+\begin{definition}
     For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum vector} of $C'$ is the vector
      obtained from the sum of the $k$-th and  $n$-th columns of $C'$.
-\end{defn}
-
+\end{definition}
 Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$.
 Below is the definition of $k$-rooted matrix.
-\begin{defn}\label{m_rooted}
+\begin{definition}\label{m_rooted}
     A  matrix $C'=(c'_{ij})$ is called {\it $k$-rooted}  if for
@@
      and the $(k,n)$-sum vector of $C'$ is $k$-rooted.
-\end{defn}
+\end{definition}
+\end{frame}
 
+\begin{frame}
     We need a simple lemma for later use.
 
-\begin{lem}
+\begin{lemma}
 $Q^{-1}=I-E_{kn}.$
-\end{lem}
+\end{lemma}
 
@@
 
+\end{frame}
+
+\begin{frame}
     The matrix $Q^{-1}$ is explicitly written as
@@
 \end{pmatrix},$$
+
+\end{frame}
+
+\begin{frame}
     and if $C'=(c'_{ij})$ then $Q^{-1}C'Q$ has the form 
@@
 
+\end{frame}
+
+\begin{frame}
     The following lemma shows that a $k$-rooted matrix has a $k$-rooted eigenvector.
 
-\begin{lem}\label{lma_m_rooted}
+\begin{lemma}\label{lma_m_rooted}
     Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(ii) hold.
-        \begin{enumerate}[label=(\roman*)]
+        \begin{enumerate}[(i)]
             \item \label{lma_m_rooted_cond1} $C'$ is a $k$-rooted matrix if and only if $Q^{-1}(C'+dI)Q$ is nonnegative for some $d\geq 0$, where $I$ is the $n\times n$ identity matrix. 
@@
         \end{enumerate}
-\end{lem}
+\end{lemma}
+\end{frame}
 
-\begin{proof}
-\begin{enumerate}
-  \item[(i)] The matrix $Q^{-1}C'Q$ has $ij$ entry
+\begin{frame}
+    \begin{proof}[Proof.(i)]
+        The matrix $Q^{-1}C'Q$ has $ij$ entry
         $$(Q^{-1}C'Q)_{ij}=\left\{
@@
         Hence $Q^{-1}(C'+dI)Q$ is nonnegative if and only if $C'$ is $k$-rooted by the definition of nonnegative matrix and $k$-rooted matrix.
-  \item[(ii)] Suppose $C'$ is $k$-rooted. Choose $d\geq 0$ such that $Q^{-1}(C'+dI)Q$ is nonnegative.  
+
+    \end{proof}
+\end{frame}
+
+\begin{frame}
+    \begin{proof}[Proof.(ii)]
+        Suppose $C'$ is $k$-rooted. Choose $d\geq 0$ such that $Q^{-1}(C'+dI)Q$ is nonnegative.  
     Let $u$ be a nonnegative eigenvector of $Q^{-1}(C'+dI)Q=Q^{-1}C'Q+I$ for $\rho(C'+dI)=\rho(C')+d.$
     Note that $Q^{-1}C'Qu=\rho(C')u,$ and $Qu$ is $k$-rooted by Lemma~\ref{lem:rt_vec}. Hence $v'=Qu$ is what we want. 
-\end{enumerate}
     \end{proof}
 
+\end{frame}
+
+\begin{frame}
     Note that Theorem~\ref{thm_main} depends on eigenvectors. The following is an eigenvector-free Theorem.
 
-\begin{thm}\label{thm:conclusion}
+\begin{theorem}\label{thm:conclusion}
     Let $C$ be an $n\times n$ nonnegative irreducible matrix and $C'$ be an $n\times n$ $k$-rooted matrix such that $C'Q$ majorizes $CQ$. 
  Then $\rho(C)\leq \rho(C')$. 
-\end{thm}
+\end{theorem}
 
@@
 \end{proof}
+\end{frame}
 
-% proof shortened
+\begin{frame}
+    \frametitle{Examples}
+    Let $G$ be the digraph depicted below. 
+    \begin{figure}
+        \includegraphics[scale = 0.5]{exam3_10.PNG}
+    \end{figure}
 
-\begin{exam}
+\end{frame}
 
-Let $G$ be the digraph depicted below. 
-\bigskip
-
-\begin{center}
-\begin{tikzpicture}
-
-\tikzset{vertex/.style = {shape=circle,draw,minimum size=0.5em}}
-\tikzset{edge/.style = {->,> = latex'}}
-% vertices
-\node[vertex] (1) at  (0,5) {$1$};
-\node[vertex] (2) at  (6,10) {$2$};
-\node[vertex] (3) at  (12,5) {$3$};
-\node[vertex] (4) at  (6,5) {$4$};
-
-%edges
-
-\draw[edge] (1) to[bend right] (3);
-\draw[edge] (1) to[bend right] (4);
-\draw[edge] (2) to (1);
-\draw[edge] (2) to[bend right] (4);
-\draw[edge] (3) to (2);
-\draw[edge] (3) to[bend right] (1);
-\draw[edge] (3) to[bend right] (4); 
-\draw[edge] (4)[bend right] to (1); 
-\draw[edge] (4)[bend right] to (2); 
-\draw[edge] (4)[bend right] to (3); 
-\end{tikzpicture}
-\end{center}
-
+\begin{frame}
     The following $4\times 4$ matrix is the adjacency matrix of $G$. 
@@
 which is the adjacency matrix of $G'$ depicted below. 
-\bigskip
+\end{frame}
 
-\begin{center}
-\begin{tikzpicture}
+\begin{frame}
+    \begin{figure}
+        \includegraphics[scale = 0.5]{exam3_11.PNG}
+    \end{figure}
 
-\tikzset{vertex/.style = {shape=circle,draw,minimum size=0.5em}}
-\tikzset{edge/.style = {->,> = latex'}}
-% vertices
-\node[vertex] (1) at  (0,5) {$1$};
-\node[vertex] (2) at  (6,10) {$2$};
-\node[vertex] (3) at  (12,5) {$3$};
-\node[vertex] (4) at  (6,5) {$4$};
+\end{frame}
 
-%edges
-
-\draw[edge] (1) to[bend right] (3);
-\draw[edge] (1) to[bend right] (4);
-\draw[edge] (2) to (1);
-\draw[edge] (2) to (3);
-\draw[edge] (3) to[bend right] (1);
-\draw[edge] (3) to (2);
-\draw[edge] (3) to[bend right] (4);
-\draw[edge] (4)[bend right] to (1);
-\draw[edge] (4) to (2);
-\draw[edge] (4)[bend right] to (3);
-\end{tikzpicture}
-\end{center}
-
+\begin{frame}
     Note that both $G$ and $G'$ have the same number of edges, 
@@
 Both of the values of $\rho(C)$ and $\rho(C')$ are close to $2.511547$ by  calculating on computer. \cite[sage]{sage}
-\end{exam}
+\end{frame}
 
+\begin{frame}
     To finish the thesis, we provide an example to show that the `$k$-rooted' assumption of $C'$ is necessary in Theorem~\ref{thm:conclusion}.
 
-\begin{exam}
     Consider the following two $4\times 4$ matrices
@@
     This is because $C'$ is not $k$-rooted as $c'_{33}+c'_{34}=0\not\geq 1=c'_{43}+c'_{44}$.
-
-All theorems come from continuous discussions between C.W. Weng and K.H. Chen. These were all documented.\cite{src_files}
-
-\end{exam}
-
-%\section*{References}
-\begin{thebibliography}{20}
-\normalsize
-\addcontentsline{toc}{section}{Bibliography}
-
-\bibitem{chang}
-Yen-Jen Cheng, {\it  A matrix realization of spectral bounds
-of the spectral radius of a nonnegative matrix}, Ph.D. Thesis, NCTU, 2018.
-
-\bibitem{spec_rad}
-A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012
-\bibitem{prn_fros2}
-R. A. Horn , C. R. Johnson, {\it Matrix analysis}, Cambrigde University Press, 1985.
-\bibitem{sage}
-[Sage] SageMath, the Sage Mathematics Software System (Version 9.2),
-       The Sage Developers, 2020, https://www.sagemath.org.  %sage tutorial
-\bibitem{src_files}
-[github] K. H. Chen, C. W. Weng, source files to the essay, A simple method on comparison between spectral radii of two directed graphs,
-     2021, https://reurl.cc/6yy32Z. % https://github.com/Urbaner3/NCTU_weng.
-
-\end{thebibliography}
+\end{frame}
 

### 2021-01-27 spectral radius of matrix new method/thesis/final_article0127.tex
publishing 0127

--- 2021-01-20 spectral radius of matrix new method/thesis/article012121.tex
@@
 \usepackage{graphicx}
+\usepackage{comment}
+%\usepackage{lipsum}
+\usepackage{background}
+\backgroundsetup{scale=1,angle=0,opacity=1,
+    contents = {\includegraphics[scale = 1]{logo.jpg}}
+}
+%\usepackage{watermark}
+%\watermark{\includegraphics[scale = 1]{logo.jpg}}
 
@@
 % \newtheorem{pof}[thm]{Proof.}
-
-\usepackage{comment}
 
@@
 
+%ij index orientation to your instinct, and do the definition
+
 Given a directed graph $G$, the spectral radius of $G$ is the
@@
  method to estimate the spectral radius. A simple and excellent
- executable method to estimate the spectral radius has some features,
- first, the bios is minimized, and second, there must be a way to prove
+ executable method to estimate the spectral radius has some features.
+ First, the bios is minimized, and second, there must be a way to prove
  it sensible. Enumerate these factors and prove it correctly would make this method reliable.
@@
 And based on their theory and Perron-Frobenius theorem, we give another approach to obtain an upper bound of the spectral radius and apply it on the adjacency matrix of a directed graph.
-All theorems come from continuous discussions between C.W. Weng and K.H. Chen. These were all documented.\cite{src_files}
+All theorems come from continuous discussions between C.W. Weng and K.H. Chen. These were all documented\cite{src_files}.
+
+%張耀祖：有沒有比較何者較好？
 
@@
  show that if matrix  $C'$ {\it majors} $C$ (in notation $C\leq C'$),
- i.e. $c_{ij}\leq c'_{ij}$ for all $ij,j$, then $\rho(C)\leq \rho(C')$.
+ i.e. $c_{ij}\leq c'_{ij}$ for all $i,j$, then $\rho(C)\leq \rho(C')$.
 Our main result shows that the assumption $C\leq C'$ can be a little loosen. 
@@
          \end{align*} so $\lambda=\lambda'$ by (\ref{pre2}).
+         %This paragraph is hard to see the fact of proof. The formula is too brief.
 \end{proof}
@@
 We use $[n-1]$ as notation of the set of integers from $1$ to $n-1$, which is $\{1,2,\cdots,n-1\}$.
-Throughout this thesis we fix $k\in [n-1]$, let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$
+Throughout this thesis we fix $k\in [n-1]$. Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$
 appearing in the position $k,n$ of $E_{kn}$. Now we apply the previous Theorem \ref{pre_thm} with $P=I$ and
 
+%張：在Q的符號中看不出與k有關
 \begin{equation} \label{Q_1}
@@
 \begin{proof}
-(i), (ii) follow immediate from the definition of $k$-rooted and
+(i), (ii) follow immediately from the definition of $k$-rooted and
  $Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$.
@@
  suggest that $C$ and $C'$ have nonnegative $k$-rooted eigenvectors. And the forth condition is simpler
-  but with the same meaning in Theorem~\ref{pre_thm}
+  but with the same meaning in Theorem~\ref{pre_thm}.
 
@@
         $\lambda = \lambda'$ if and only if (\ref{pre0}) holds, and this is equivalent to
-         conditions \ref{thm_main:equ_cond_a}, \ref{thm_main:equ_cond_b} and \ref{thm_main:equ_cond_c} of this theorem.
+         conditions \ref{thm_main:equ_cond_a}, \ref{thm_main:equ_cond_b}, and \ref{thm_main:equ_cond_c} of this theorem.
 \end{proof}
@@
 \begin{proof}
-Since $$Q(I-E_{kn}=(I+E_{kn})(I-E_{kn})=I-E_{kn}+E_{kn}-E_{kn}E_{kn}=I,$$ we have
+Since $$Q(I-E_{kn})=(I+E_{kn})(I-E_{kn})=I-E_{kn}+E_{kn}-E_{kn}E_{kn}=I,$$ we have
 $Q^{-1}=I-E_{kn}$.
@@
 \begin{thm}\label{thm:conclusion}
-    Let $C$ be an $n\times n$ nonnegative irreducible matrix and $C'$ be an $n\times n$ $k$-rooted matrix such that $C'Q$ majorizes $CQ$. 
+    Let $C$ be an $n\times n$ nonnegative irreducible matrix and $C'$ be an $n\times n$ $k$-rooted matrix such that $C'Q$ majors $CQ$. 
  Then $\rho(C)\leq \rho(C')$. 
@@
 
-\draw[edge] (1) to[bend right] (3);
-\draw[edge] (1) to[bend right] (4);
-\draw[edge] (2) to (1);
-\draw[edge] (2) to[bend right] (4);
-\draw[edge] (3) to (2);
-\draw[edge] (3) to[bend right] (1);
-\draw[edge] (3) to[bend right] (4); 
-\draw[edge] (4)[bend right] to (1); 
-\draw[edge] (4)[bend right] to (2); 
-\draw[edge] (4)[bend right] to (3); 
+\draw[edge] (1) to (2);
+\draw[edge] (1) to[bend left] (3);
+\draw[edge] (1) to[bend left] (4);
+\draw[edge] (2) to (3);
+\draw[edge] (2) to[bend left] (4);
+\draw[edge] (3) to[bend left] (1);
+\draw[edge] (3) to[bend left] (4); 
+\draw[edge] (4)[bend left] to (1); 
+\draw[edge] (4)[bend left] to (2); 
+\draw[edge] (4)[bend left] to (3); 
 \end{tikzpicture}
@@
 
-\draw[edge] (1) to[bend right] (3);
-\draw[edge] (1) to[bend right] (4);
-\draw[edge] (2) to (1);
+\draw[edge] (1) to (2);
+\draw[edge] (1) to[bend left] (3);
+\draw[edge] (1) to[bend left] (4);
 \draw[edge] (2) to (3);
-\draw[edge] (3) to[bend right] (1);
+\draw[edge] (2) to (4);
+\draw[edge] (3) to[bend left] (1);
 \draw[edge] (3) to (2);
-\draw[edge] (3) to[bend right] (4);
-\draw[edge] (4)[bend right] to (1);
-\draw[edge] (4) to (2);
-\draw[edge] (4)[bend right] to (3);
+\draw[edge] (3) to[bend left] (4);
+\draw[edge] (4)[bend left] to (1);
+\draw[edge] (4)[bend left] to (3);
 \end{tikzpicture}
@@
 Note that both $G$ and $G'$ have the same number of edges, 
-neither $A$ majories $A'$ nor $A'$ majories $A$. Our main result still can do comparison between 
+neither $A$ majors $A'$ nor $A'$ majors $A$. Our main result still can do comparison between 
 $\rho(A)$ and $\rho(A')$. 
@@
     \end{pmatrix}=AQ$. 
-Hence Hence $\rho(A)\leq\rho(A')$ by Theorem~\ref{thm:conclusion} with $C=A$ and $C'=A'$. 
-Both of the values of $\rho(C)$ and $\rho(C')$ are close to $2.511547$ by  calculating on computer. \cite[sage]{sage}
+Hence $\rho(A)\leq\rho(A')$ by Theorem~\ref{thm:conclusion} with $C=A$ and $C'=A'$. 
+Both of the values of $\rho(C)$ and $\rho(C')$ are close to $2.511547$ by  calculating on computer \cite[sage]{sage}.
 \end{exam}
@@
 
-All theorems come from continuous discussions between C.W. Weng and K.H. Chen. These were all documented.\cite{src_files}
+All theorems come from continuous discussions between C.W. Weng and K.H. Chen. These were all documented \cite{src_files}.
 
 \end{exam}
+
+% 傅：tournaments graph, choosing the vertex with the maximum out-degree, does the theory implies the spectual radii are in an indecreasing sequence?  我：The irreducible in preserved.
 
@@
 \bibitem{src_files}
-[github] K. H. Chen, C. W. Weng, source files to the essay, A simple method on comparison between spectral radii of two directed graphs,
+[github] K. H. Chen, source files to the essay, A simple method on comparison between spectral radii of two directed graphs,
      2021, https://reurl.cc/6yy32Z.  % https://github.com/Urbaner3/NCTU_weng.
+
+     \newblock the link: $https://github.com/Urbaner3/NCTU\_weng$
 
